---
title: "Causal Impact Analysis"
<<<<<<< HEAD
editor: visual
execute:
  echo: false
  message: false
  warning: false
  cache: false
lang: en-GB
author: Sarah Lucas
date: last-modified
date-format: "YYYY-MM-DD"
title-block-banner: "#f9bf07"
title-block-banner-color: "#333739"
format:
  html:
    embed-resources: true
    smooth-scroll: true
    theme: cosmo
    fontcolor: black
    toc: true
    toc-location: left
    toc-title: Summary
    toc-depth: 3
css: styles.css
=======
format: html
editor: visual
>>>>>>> 19611e9 (extra data wrangling for CIA and trial CIA)
---

REMRQ - Royal Liverpool

REM21 - Aintree University

RBN01 - Whiston

REMBG - Warrington

RVY01 - Southport & Formby

RVY02 - Ormskirk & District

RJR05 - Countess of Chester

<<<<<<< HEAD
tar_make()

```{r, include=FALSE}
=======
# Extra data wrangling


```{r}
>>>>>>> 19611e9 (extra data wrangling for CIA and trial CIA)
library(tidyverse)
library(MarketMatching)
library(tsibble)
library(targets)
library(janitor)
library(readxl)
library(zoo)
library(lubridate)

<<<<<<< HEAD
library(StrategyUnitTheme)
library(extrafont)


source("R/data_wrangling_functions.R")
source("R/CIA_additional_data_wrangling_functions.R")
source("_targets.R")

# Extra data wrangling

beddays<-tar_read(beddays)

beddays_by_prov<-beddays|>
=======
 


#Functions 
merge_sites<-function(data){
 data|>
  mutate(site_code=ifelse((site_code=="REMRQ"|site_code=="RQ617"), "REMRQ", site_code))|> #merge historical Royal Liverpool codes
    mutate(site_code=ifelse((site_code=="RGM22"|site_code=="RGM21"), "RGM22", site_code))|> #merge Papworth site codes
     mutate(site_code=ifelse((site_code=="RVJ01"|site_code=="RVJ20"), "RVJ01", site_code))|> #merge Southmead site codes
   mutate(site_code=ifelse((site_code=="RGN80"|site_code=="RGN42"), "RGN80", site_code))|> #merge Peterborough site codes
    mutate(site_code=ifelse((site_code=="RWFTW"|site_code=="RWF01"|site_code=="RWF02"), "RWFTW", site_code)) #merge Tunbridge site codes
}

beddays_by_site<-fun_load_beddays("Data/nhp_hospsite_beddays_mth.csv")

beddays_by_prov<-fun_load_beddays("Data/nhp_hospsite_beddays_mth.csv")|>
>>>>>>> 19611e9 (extra data wrangling for CIA and trial CIA)
  mutate(organisation_code=substr(der_provider_site_code, start = 1, stop = 3))|>#get organisation code
    group_by(yearmon, organisation_code)|>
    summarise(beddays=sum(beddays))

<<<<<<< HEAD

## Friends & Family
friends_and_family_cia_format<-tar_read(formatted_friends_and_family_data)|>
friends_and_family_cia_formatting()
  #filter(site_code=="REMRQ"|site_code=="REM21"|site_code=="RBN01"|site_code=="REMBG"|
  #       site_code=="RVY01"|site_code=="RVY02"|site_code=="RJR05")


## Staff turnover
turnover_cia_format<-tar_read(formatted_turnover)|>
staff_turnover_cia_formatting()


 # filter(organisation_code=="RGM")|>
#ggplot(aes(x = month, y =leaving_rate) ) + 
#geom_line(linewidth=1)+
 # ylim(0,NA)
  

## Staff sickness
staff_sickness_cia_format<-tar_read(formatted_staff_sickness_absence)|>
  staff_sickness_cia_formatting()|>
  filter(organisation_code=="REM"|organisation_code=="RBN"|organisation_code=="RVY"| organisation_code=="RJR" )

## Healthcare acquired infections - Infection rate per 10,000 bed days
hcai_cia_format<-tar_read(formatted_HCAI_data)|>
  hcai_cia_formatting()


## In-hospital Falls and Fractures - Fall rate per 1000 bed days
falls_and_fractures_cia_format<- tar_read(sus_apcs)|>   
falls_and_fractures_cia_formatting()


## Deaths/Summary Hospital-Level Mortality Indicator
shmi_data<-tar_read(formatted_shmi)|>
=======
```


## Friends & Family
```{r}
friends_and_family_data<-read.csv("Data/formatted_friends_and_family_data.csv")|>
    mutate(month=as.Date(month))|>
 merge_sites()|>
  group_by(month, site_code)|>
 summarise(percent=mean(percent, na.rm=TRUE))|>
  filter(site_code=="REMRQ"|site_code=="REM21"|site_code=="RBN01"|site_code=="REMBG"|
         site_code=="RVY01"|site_code=="RVY02"|site_code=="RJR05")

```



## Staff turnover
```{r}
workforce_udal<-read.csv("Data/sql_workforce.csv")
workforce_links<-read_excel("Data/links_workforce.xlsx")
workforce_data<-combine_workforce(workforce_udal,workforce_links)
turnover<-wrangle_turnover("sql_turnover.csv")

```







## Staff sickness

```{r}


# staff_sickness
staff_sickness<-staff_sickness_absence_formatting("Data/staff_sickness_absence.csv")|>
  mutate(month=as.Date(month))|>
      mutate(organisation_code=ifelse((organisation_code=="REM"|organisation_code=="RQ6"), "REM", organisation_code))|> #merge historical Royal Liverpool codes
    group_by(month, organisation_code)|>
  summarise(fte_days_sick=sum(fte_days_sick), fte_days_available=sum(fte_days_available) )|> #regroup following merging the organisation codes
  mutate(percent=(fte_days_sick/fte_days_available)*100)|>
  filter(organisation_code=="REM"|organisation_code=="RBN"|organisation_code=="RVY"|
          organisation_code=="RJR" )
```

## Healthcare acquired infections

```{r}


hcai_data_combined<-hcai_formatting("Data/hai_cdiff_pre_2018.csv", 
                "Data/hai_cdiff.csv",
                "Data/hai_ecoli.csv",
                 "Data/hai_klebsiella.csv",
                 "Data/hai_mssa.csv",
                "Data/hai_mrsa.csv",
                "Data/hai_p_aeruginosa.csv")|>
  left_join(beddays_by_prov[,c("organisation_code", "yearmon", "beddays")], by=c("organisation_code", "month"="yearmon"))|>
  mutate(rate=(count_of_cases/beddays)*10000)|> #cases per 10,000 beddays
  group_by(month, organisation_code)|>
summarise(combined_rate=sum(rate))|>#calculate combined rate for all infectiond
  filter(month>="2018-03-01")|>
  filter(organisation_code=="REM")|> #for Royal Liverpool
    ggplot(aes(x = month, y =combined_rate) ) + 
   geom_line(linewidth=1) 




```
## In-hospital Falls and Fractures

```{r}

falls_and_fractures<- fun_load_sus_apcs("Data/nhp_hospsite_apcs_mth.csv", beddays)|>   rename(site_code=der_provider_site_code)|>
  rename(month=yearmon)|>
 merge_sites()|>
  group_by(site_code, month)|>
  summarise(fall_fracs=sum(fall_fracs), beddays=sum(beddays))|> #recalculate rate following merging sites
  mutate(ff_rate=(fall_fracs/beddays)*1000) #rate per 1000 beddays
 

```

## MISSING VALUES Summary Hospital-Level Mortality Indicator
```{r}
shmi_data<-wrangle_shmi("Data/sql_shmi.csv")|>
>>>>>>> 19611e9 (extra data wrangling for CIA and trial CIA)
  mutate(month=floor_date(effective_snapshot_date, "month"))|> #Format date to monthly
  filter(level=="Site")|> #Select only Site data (only available 2019 onwards)
  merge_sites()|>
  group_by(month, site_code)|>
  summarise(observed=sum(observed), expected=sum(expected))|>
<<<<<<< HEAD
  mutate(shmi=observed/expected)|>
  filter(site_code=="RGM21"|site_code=="RGM22")
  

shmi_data<-tar_read(formatted_shmi)|>
  mutate(month=floor_date(effective_snapshot_date, "month"))|> #Format date to monthly
  filter(level=="Trust")|> #Select only Site data (only available 2019 onwards)
  mutate(organisation_code=ifelse((organisation_code=="REM"|organisation_code=="RQ6"), "REM", organisation_code))|> #merge historical Royal Liverpool codes
  group_by(month, organisation_code)|>
  summarise(observed=sum(observed), expected=sum(expected))|>
  mutate(shmi=observed/expected)|>
  filter(organisation_code=="RGM")

# No deaths data for papworth

# SUS death rate (deaths/1000 admissions)
sus_death_data_cia_format<- tar_read(sus_apcs)|>   
sus_deaths_cia_formatting()

## filter(site_code=="RGM22")|>
  #filter(month>"2017-04-01")|>
# ggplot(aes(x = month, y =death_rate) ) + 
 #  geom_line(linewidth=1)
=======
  mutate(shmi=observed/expected)
>>>>>>> 19611e9 (extra data wrangling for CIA and trial CIA)
 # filter(site_code=="REMRQ"|site_code=="REM21"|site_code=="RBN01"|site_code=="REMBG"|
  #       site_code=="RVY01"|site_code=="RVY02"|site_code=="RJR05"|site_code=="RQ617")


<<<<<<< HEAD
## RTT waiting time
rtt_waiting_time_cia_format<-tar_read(formatted_rtt_data) |>
rtt_waiting_time_cia_formatting()|>
 filter(organisation_code=="REM"|organisation_code=="RJR"|organisation_code=="RVY"|
          organisation_code==  "RBN")

## Bed occupancy
bed_occupancy_cia_format<-tar_read(formatted_bed_occupancy)|>
bed_occupancy_cia_formatting()

## Length of Stay
length_of_stay_cia_format<- tar_read(sus_apcs)|>
    length_of_stay_cia_formatting()
#  filter(site_code=="RGM22")|> 
#    ggplot(aes(x = month, y =avg_los) ) + 
#   geom_line(linewidth=1) 


## TO DO Emergency readmissions

```

```{r, include= FALSE}

# Plots for information

## Cleaning staff


cleaning_staff<-tar_read(eric_udal)|>
  filter(measure=="Cleaning staff (WTE)")|>
  filter(level=="Site")|>
  mutate(month=floor_date(effective_snapshot_date, "month"))|> #Format date to monthly
  left_join(beddays[,c("der_provider_site_code", "beddays", "yearmon")], 
=======


shmi_data|>
  filter(organisation_code=="RGM")|>
    ggplot(aes(x = month, y =expected) ) + 
   geom_line(size=1) +
   labs( title = "",y = "No. of cases", x="")+
   theme( legend.position= c(0.25, 0.8))+
   scale_y_continuous(limits=c(0, NA)) 


friends_and_family_data|>
  filter(site_code=="RVJ01")|>
    ggplot(aes(x = month, y =percent) ) + 
   geom_line(size=1) +
   labs( title = "",y = "No. of cases", x="")+
   theme( legend.position= c(0.25, 0.8))+
   scale_y_continuous(limits=c(0, NA)) 

#RGM21 no shmi
#+RGM22 no f&f /shmi

 #RGN42 - no f&f/shmi
# RGN80

 #RVJ01+
 #  RVJ20 no shmi
 



 
```



## RTT waiting time
```{r}
rtt_data<-read.csv("Data/formatted_rtt_data.csv") |>
    mutate(month=as.Date(month))|>
    mutate(organisation_code=ifelse((organisation_code=="REM"|organisation_code=="RQ6"), "REM", organisation_code))|> #merge historical Royal Liverpool codes
    group_by(month, organisation_code)|>
  summarise(median_by_prov = median(rep(weeks,number_of_incomplete_pathways)), number_incomplete=sum(number_of_incomplete_pathways))|> #Median by month and provider 
  mutate(median_by_prov=ifelse(is.na(median_by_prov),0,median_by_prov))|>
    filter(organisation_code=="REM"|organisation_code=="RJR"|organisation_code=="RVY"|
           organisation_code==  "RBN")


```



## Bed occupancy
```{r}
occupancy_data<-wrangle_bed_occupancy("Data/sql_bed_occupancy.csv")|>
     mutate(effective_snapshot_date=as.Date(effective_snapshot_date,"%Y-%m-%d"))|> #Format date 
  mutate(month=floor_date(effective_snapshot_date, "month"))|> #Format date to monthly
  filter(report_period_length=="Quarterly")|>
      mutate(organisation_code=ifelse((organisation_code=="REM"|organisation_code=="RQ6"), "REM", organisation_code))|> #merge historical Royal Liverpool codes
  group_by(month, organisation_code)|>
  summarise(available=sum(available), occupied=sum(occupied))|>
  mutate(bed_occupancy=occupied/available)

```

## Length of Stay
```{r}

length_of_stay<- fun_load_sus_apcs("Data/nhp_hospsite_apcs_mth.csv", beddays)|>
  rename(site_code=der_provider_site_code)|>
  rename(month=yearmon)|>
 merge_sites()|>
  group_by(site_code, month)|>
  summarise(los=sum(los), spells=sum(spells))|> #recalculate following merge of sites
  mutate(avg_los=los/spells) |>
  filter(site_code=="RGM22")|> 
    ggplot(aes(x = month, y =avg_los) ) + 
   geom_line(linewidth=1) 


```

## TO DO Emergency readmissions


# Other plots information

## Cleaning staff
```{r}
cleaning_staff<-wrangle_eric("Data/sql_eric_09_15.csv", "Data/sql_eric_16_23.csv")|>
  filter(measure=="Cleaning staff (WTE)")|>
  filter(level=="Site")|>
  mutate(month=floor_date(effective_snapshot_date, "month"))|> #Format date to monthly
  left_join(beddays_by_site[,c("der_provider_site_code", "beddays", "yearmon")], 
>>>>>>> 19611e9 (extra data wrangling for CIA and trial CIA)
                   by=c("site_code"= "der_provider_site_code", "month"="yearmon"))|>
 merge_sites()|>
  mutate(rate=(value/beddays)*1000) #WTE per 1000 beddays



<<<<<<< HEAD
## C. Difficile rate over time - hcai where recording goes back before 2017/2018
=======
```

## C. Difficile rate over time
```{r}

#c.diff only as this goes back before 2017/2018
>>>>>>> 19611e9 (extra data wrangling for CIA and trial CIA)
hcai_formatting("Data/hai_cdiff_pre_2018.csv", 
                "Data/hai_cdiff.csv",
                "Data/hai_ecoli.csv",
                 "Data/hai_klebsiella.csv",
                 "Data/hai_mssa.csv",
                "Data/hai_mrsa.csv",
                "Data/hai_p_aeruginosa.csv")|>
  left_join(beddays_by_prov[,c("organisation_code", "yearmon", "beddays")], by=c("organisation_code", "month"="yearmon"))|>
  mutate(rate=(count_of_cases/beddays)*10000)|> #cases per 10,000 beddays
filter(collection=="C.difficile")|>
  filter(organisation_code=="REM")|> #for Royal Liverpool
    ggplot(aes(x = month, y =rate) ) + 
   geom_line(linewidth=1) 

<<<<<<< HEAD
# C. Difficile numbers are too small to use in CIA as so much variability.

```

```{r, fig.height=4, fig.width=10}


  measure<-c("friends and family test", "staff turnover", "staff sickness", "healthcare acquired infections", "falls and fractures", "hospital deaths", "rtt waiting times", "bed occupancy", "length of stay" )
    start_date<-c(min(friends_and_family_cia_format$month), min(turnover_cia_format$month), min(staff_sickness_cia_format$month), min(hcai_cia_format$month), min(falls_and_fractures_cia_format$month), min(sus_death_data_cia_format$month), min(rtt_waiting_time_cia_format$month), min(bed_occupancy_cia_format$month), min(length_of_stay_cia_format$month))
      end_date<-c(max(friends_and_family_cia_format$month), max(turnover_cia_format$month), max(staff_sickness_cia_format$month), max(hcai_cia_format$month), max(falls_and_fractures_cia_format$month), max(sus_death_data_cia_format$month), max(rtt_waiting_time_cia_format$month), max(bed_occupancy_cia_format$month), max(length_of_stay_cia_format$month))
  
indicators<- data.frame(measure, start_date, end_date) |>
 # gather(key="start_end", value="month", -measure)

name<-c("Royal Liverpool", "Clatterbridge", "Papworth", "Peterborough", "Chase Farm", "Southmead", "Tunbridge Wells")
date<-c('2022-10-01', '2020-06-01', '2019-05-01', '2010-11-01', '2018-09-01', '2014-05-01', '2011-01-01' )

sites<-data.frame(name, date)|>
  mutate(date=as.Date(date))

ggplot() +
  geom_segment(data=indicators, aes(x=measure, y=start_date, yend=end_date),lineend = "round", color="#ABDDA4", linewidth=3)+
labs(y=NULL, x=NULL)+
  su_theme()+
  theme(axis.text.y = element_text(size=12),axis.text.x = element_text(size=11))+
  geom_vline(data=sites, aes(xintercept = date), linetype="dashed", color="#2c2825") +
  geom_text(data=sites, aes(x=date, label=name, y=12), colour="#2c2825", angle=45, text=element_text(size=11))+
  scale_x_date(date_breaks = "1 year",date_labels = "%Y")
=======
# C. difficile numbers are too small to use in CIA as so much variability.
>>>>>>> 19611e9 (extra data wrangling for CIA and trial CIA)

```

# Causal Impact analysis

## Staff sickness

```{r, include=TRUE}


# Find the best matches  
<<<<<<< HEAD
mm <- MarketMatching::best_matches(data=staff_sickness_cia_format,
=======
mm <- MarketMatching::best_matches(data=staff_sickness,
>>>>>>> 19611e9 (extra data wrangling for CIA and trial CIA)
                   id_variable="organisation_code",
                   date_variable="month",
                   matching_variable="percent",
                   parallel=FALSE,
                   warping_limit=1, # warping limit=1
                   dtw_emphasis=1, # rely only on dtw for pre-screening
<<<<<<< HEAD
                   matches=3, # request 3 matches
                   start_match_period="2016-08-01",
                   end_match_period="2022-09-01")
=======
                   matches=2, # request 2 matches
                   start_match_period="2017-04-01",
                   end_match_period="2022-10-01")
>>>>>>> 19611e9 (extra data wrangling for CIA and trial CIA)

#View the best matches
knitr::kable(head(mm$BestMatches))

results <- MarketMatching::inference(matched_markets = mm,
                                     analyze_betas=TRUE,
                                     test_market = "REM",
                                    end_post_period = "2023-10-01",
                                    alpha=0.05, 
<<<<<<< HEAD
                                    prior_level_sd=0.01,
                                    nseasons=12)

#Plot the actuals 
results$PlotActuals+
  su_theme()

# Plot out actual vs expected
results$PlotActualVersusExpected+
  su_theme()
=======
                                    prior_level_sd=0.02,
                                    nseasons=12)

# Plot out actual vs expected
results$PlotActualVersusExpected
>>>>>>> 19611e9 (extra data wrangling for CIA and trial CIA)

# Plot out cumulative effect
results$PlotCumulativeEffect

# Plot pointwise effect
results$PlotPointEffect

<<<<<<< HEAD
=======
#Plot the actuals 
results$PlotActuals
>>>>>>> 19611e9 (extra data wrangling for CIA and trial CIA)

# See which hospital receives the highest weight in determining the outcome
coeff <- results$Coefficients
knitr::kable(head(coeff))


```

```{r, include=FALSE}

#Store predicted values in dataframe
pred <- results$Predictions
knitr::kable(head(pred))

# Check out the DW and MAPE of the model
results$PlotPriorLevelSdAnalysis

#Prospective Pseudo Power Curves -will help you evaluate if your choice of test and control markets creates a sufficient model to measure a realistic lift from a future intervention. 

power <- MarketMatching::test_fake_lift(matched_markets = mm, 
                                      test_market = "REM", 
                                      end_fake_post_period = "2023-10-01", 
                                      prior_level_sd = 0.01, 
                                      steps=10,
                                      max_fake_lift=0.05)
#And plot the graph- Ideally, a curve that starts at high probability on the left side, reaches its minimum at zero lift, and then rises again symmetrically. If the curve does not reach its minimum at zero there may be systemic model bias in the post period. 
power$ResultsGraph


```

<<<<<<< HEAD
## RTT Waiting time data- Median waiting time (in weeks)
=======
## RTT Waiting time data- Number of incomplete pathways
>>>>>>> 19611e9 (extra data wrangling for CIA and trial CIA)

```{r}


# Find the best matches  
mm <- MarketMatching::best_matches(rtt_data,
                   id_variable="organisation_code",
                   date_variable="month",
<<<<<<< HEAD
                   matching_variable="median_by_prov",
                   parallel=FALSE,
                   warping_limit=1, # warping limit=1
                   dtw_emphasis=1, # rely only on dtw for pre-screening
                   matches=3, # request 3 matches
                   start_match_period="2016-08-01",
                   end_match_period="2022-09-01")
=======
                   matching_variable="number_incomplete",
                   parallel=FALSE,
                   warping_limit=1, # warping limit=1
                   dtw_emphasis=1, # rely only on dtw for pre-screening
                   matches=2, # request 5 matches
                   start_match_period="2017-04-01",
                   end_match_period="2022-10-01")
>>>>>>> 19611e9 (extra data wrangling for CIA and trial CIA)

#View the best matches
knitr::kable(head(mm$BestMatches))

results <- MarketMatching::inference(matched_markets = mm,
                                     analyze_betas=TRUE,
                                     test_market = "REM",
                                    end_post_period = "2023-10-01",
                                    alpha=0.05, 
                                    prior_level_sd=0.01,
                                    nseasons=12)

#Absolute Effect indicates an increase in the median of 0.94 relative to what we expected. The Relative Effect provides a standardized view, indicating a 0.94% increase in the median. Probability of a causal impact indicates that the likelihood of observing this effect by chance is high (e.g., 100 - 55.2). 

<<<<<<< HEAD
#Plot the actuals 
results$PlotActuals

=======
>>>>>>> 19611e9 (extra data wrangling for CIA and trial CIA)
# Plot out actual vs expected
results$PlotActualVersusExpected

# Plot out cumulative effect
results$PlotCumulativeEffect

# Plot pointwise effect
results$PlotPointEffect

<<<<<<< HEAD

=======
#Plot the actuals 
results$PlotActuals
>>>>>>> 19611e9 (extra data wrangling for CIA and trial CIA)


# See which hospital recieves the highest weight in determining the outcome
coeff <- results$Coefficients
knitr::kable(head(coeff))



```

```{r, include=FALSE}

#Store predicted values in dataframe
pred <- results$Predictions
knitr::kable(head(pred))

# Check out the DW and MAPE of the model
results$PlotPriorLevelSdAnalysis

#Prospective Pseudo Power Curves -will help you evaluate if your choice of test and control markets creates a sufficient model to measure a realistic lift from a future intervention. 

power <- MarketMatching::test_fake_lift(matched_markets = mm, 
                                      test_market = "REM", 
                                      end_fake_post_period = "2023-10-01", 
                                      prior_level_sd = 0.01, 
                                      steps=10,
                                      max_fake_lift=0.05)
#And plot the graph- Ideally, a curve that starts at high probability on the left side, reaches its minimum at zero lift, and then rises again symmetrically. If the curve does not reach its minimum at zero there may be systemic model bias in the post period. 
power$ResultsGraph



```
<<<<<<< HEAD
=======







>>>>>>> 19611e9 (extra data wrangling for CIA and trial CIA)
