---
title: "Causal Impact Analysis: Productivity and Efficiency indicators"
editor: visual
execute:
  echo: false
  message: false
  warning: false
  cache: false
lang: en-GB
author: Sarah Lucas
date: last-modified
date-format: "YYYY-MM-DD"
title-block-banner: "#f9bf07"
title-block-banner-color: "#333739"
format:
  html:
    embed-resources: true
    smooth-scroll: true
    theme: cosmo
    fontcolor: black
    toc: true
    toc-location: left
    toc-title: Summary
    toc-depth: 3
    grid:
      sidebar-width: 250px
      body-width: 1050px
      margin-width: 0px
      gutter-width: 1.5rem
css: styles.css
---

```{r, include=FALSE}

library(tidyverse)
library(MarketMatching)
library(tsibble)
library(targets)
library(janitor)
library(readxl)
library(zoo)
library(lubridate)
library(ggrepel)
library(flextable)
library(egg)
library(StrategyUnitTheme)
library(patchwork)
library(metafor)
library(bayesmeta)

## RTT waiting time
rtt_waiting_time<-tar_read(rtt_waiting_time_cia_format) 

## Bed occupancy
bed_occupancy<-tar_read(bed_occupancy_cia_format)

## Length of Stay
length_of_stay<- tar_read(length_of_stay_cia_format)

## Emergency readmissions
emergency_readmissions<-tar_read(emergency_readmissions_cia_format)

#Loading control data
single_bedroom_matches_final<-tar_read(single_bedroom_matches_final)

source("R/CIA_Functions.R")




```


```{r, include=FALSE, fig.height=6, fig.width=10}

LoS_output<-tar_read(LoS_output)|>
  mutate(RelEffect.var=RelEffect.sd^2)|>
filter(!is.na(site))

rma(RelEffect, RelEffect.var, data=LoS_output)

LOS <- bayesmeta(y= LoS_output[,"RelEffect"],
                               sigma = LoS_output[,"RelEffect.sd"],
                               label = LoS_output[,"site"])


```


# Availability of indicators by site

```{r, fig.height=6, fig.width=10}

tar_read(indicator_availability_plot)

```

```{r}

tar_read(indicator_availability_table)

```

# Productivity and Efficiency

## Waiting time- Median (in weeks)

::: panel-tabset
### Summary

```{r, fig.width=8, fig.height=4}

waiting_time_median_output<-tar_read(waiting_time_median_output)

forest_plot(waiting_time_median_output)

model_effects_table(waiting_time_median_output)

```

### Decrease

::: columns
::: {.column width="50%"}
#### Royal Liverpool

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_median_REM<-tar_read(waiting_time_median_REM)

#evaluating_model("REM", NA,  rtt_waiting_time, "2022-10-01", "median_by_prov", 0.05, waiting_time_median_REM, single_bedroom_matches_final)

```

```{r, include=TRUE, fig.width=5, fig.height=6}

cia_summary_plots(waiting_time_median_REM, "Median waiting time (wks)", "2022-10-01")


```
:::

::: {.column width="50%"}
#### Peterborough

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_median_RGN<-tar_read(waiting_time_median_RGN)

#evaluating_model("RGN", NA, rtt_waiting_time, "2010-11-01", "median_by_prov", 0.05, waiting_time_median_RGN, single_bedroom_matches_final)


```

```{r, include=TRUE, fig.width=5, fig.height=6}

cia_summary_plots(waiting_time_median_RGN, "Median waiting time (wks)", "2010-11-01")
```
:::
:::

### No change

::: columns
::: {.column width="50%"}
#### Clatterbridge

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_median_REN<-tar_read(waiting_time_median_REN)

#evaluating_model("REN", NA, rtt_waiting_time, "2020-06-01", "median_by_prov", 0.05, waiting_time_median_REN, single_bedroom_matches_final)

```

```{r, include=TRUE, fig.width=5, fig.height=6}

cia_summary_plots(waiting_time_median_REN, "Median waiting time (wks)", "2020-06-01")

```

#### Papworth

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_median_RGM<-tar_read(waiting_time_median_RGM)

#evaluating_model("RGM", NA, rtt_waiting_time, "2019-05-01", "median_by_prov", 0.05, waiting_time_median_RGM, single_bedroom_matches_final)

```

```{r, include=TRUE, fig.width=5, fig.height=6}

cia_summary_plots(waiting_time_median_RGM, "Median waiting time (wks)", "2019-05-01")
```
:::

```{r, include=FALSE, fig.width=8, fig.height=8}
#### Chase Farm
#waiting_time_median_RAL<-tar_read(waiting_time_median_RAL)

#evaluating_model("RAL", NA, rtt_waiting_time, "2018-09-01", "median_by_prov", 0.05, waiting_time_median_RAL, single_bedroom_matches_final)

```

```{r, include=TRUE, fig.width=5, fig.height=6}

#cia_summary_plots(waiting_time_median_RAL, "Study site: Chase Farm, RAL","Median waiting time (wks)", "2018-09-01")
```

::: {.column width="50%"}
#### Southmead

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_median_RVJ<-tar_read(waiting_time_median_RVJ)

#evaluating_model("RVJ",NA,  rtt_waiting_time, "2014-05-01", "median_by_prov", 0.05, waiting_time_median_RVJ, single_bedroom_matches_final)

```

```{r, include=TRUE, fig.width=5, fig.height=6}

cia_summary_plots(waiting_time_median_RVJ, "Median waiting time (wks)", "2014-05-01")
```

#### Tunbridge Wells

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_median_RWF<-tar_read(waiting_time_median_RWF)

#evaluating_model("RWF", NA, rtt_waiting_time, "2011-01-01", "median_by_prov", 0.01, waiting_time_median_RWF, single_bedroom_matches_final)


```

```{r, include=TRUE, fig.width=5, fig.height=6}

cia_summary_plots(waiting_time_median_RWF, "Median waiting time (wks)", "2011-01-01")
```
:::
:::
:::

## Waiting time - Total number waiting

::: panel-tabset
### Summary

```{r, fig.width=8, fig.height=4}

waiting_time_number_output<-tar_read(waiting_time_number_output)

forest_plot(waiting_time_number_output)

model_effects_table(waiting_time_number_output)


```

### Decrease

#### Royal Liverpool

```{r, include=FALSE, fig.width=5, fig.height=8}

waiting_time_number_REM<-tar_read(waiting_time_number_REM)

#evaluating_model("REM", NA, rtt_waiting_time, "2022-10-01", "number_incomplete", 0.05, waiting_time_number_REM, single_bedroom_matches_final)


```

```{r, include=TRUE, fig.width=5, fig.height=6}

cia_summary_plots(waiting_time_number_REM, "Number waiting", "2022-10-01")
```

### No change

::: columns
::: {.column width="50%"}
#### Papworth

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_number_RGM<-tar_read(waiting_time_number_RGM)

#evaluating_model("RGM", NA, rtt_waiting_time, "2019-05-01", "number_incomplete", 0.05, waiting_time_number_RGM, single_bedroom_matches_final)


```

```{r, include=TRUE, fig.width=5, fig.height=6}

cia_summary_plots(waiting_time_number_RGM, "Number waiting", "2019-05-01")
```

#### Peterborough

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_number_RGN<-tar_read(waiting_time_number_RGN)

#evaluating_model("RGN", NA, rtt_waiting_time, "2010-11-01","number_incomplete", 0.05, waiting_time_number_RGN, single_bedroom_matches_final)


```

```{r, include=TRUE, fig.width=5, fig.height=6}

cia_summary_plots(waiting_time_number_RGN, "Number waiting", "2010-11-01")
```
:::

```{r, include=FALSE, fig.width=8, fig.height=8}
#### Chase Farm

#waiting_time_number_RAL<-tar_read(waiting_time_number_RAL)

#evaluating_model("RAL", NA, rtt_waiting_time, "2018-09-01", "number_incomplete", 0.05, waiting_time_number_RAL, single_bedroom_matches_final)

```

```{r, include=TRUE, fig.width=5, fig.height=6}

#cia_summary_plots(waiting_time_number_RAL, "Study site: Chase Farm, RAL","Number waiting", "2018-09-01")
```

::: {.column width="50%"}
#### Southmead

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_number_RVJ<-tar_read(waiting_time_number_RVJ) 

#evaluating_model("RVJ", NA, rtt_waiting_time, "2014-05-01", "number_incomplete", 0.05, waiting_time_number_RVJ, single_bedroom_matches_final)

```

```{r, include=TRUE, fig.width=5, fig.height=6}

cia_summary_plots(waiting_time_number_RVJ, "Number waiting", "2014-05-01")
```
:::
:::

### Increase

::: columns
::: {.column width="50%"}
#### Clatterbridge

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_number_REN<-tar_read(waiting_time_number_REN)

evaluating_model("REN", NA, rtt_waiting_time, "2020-06-01", "number_incomplete", 0.05, waiting_time_number_REN, single_bedroom_matches_final)

```

```{r, include=TRUE, fig.width=5, fig.height=6}

cia_summary_plots(waiting_time_number_REN, "Number waiting", "2020-06-01")
```
:::

::: {.column width="50%"}
#### Tunbridge Wells

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_number_RWF<-tar_read(waiting_time_number_RWF)

#evaluating_model("RWF", NA, rtt_waiting_time, "2011-01-01", "number_incomplete", 0.01, waiting_time_number_RWF, single_bedroom_matches_final)

```

```{r, include=TRUE, fig.width=5, fig.height=6}

cia_summary_plots(waiting_time_number_RWF, "Number waiting", "2011-01-01")
```
:::
:::
:::

## Length of stay

::: panel-tabset
### Summary

```{r, fig.width=8, fig.height=4}

LoS_output<-tar_read(LoS_output)

forest_plot(LoS_output)

model_effects_table(LoS_output)


```

### Decrease

```{r, include=FALSE, fig.width=8, fig.height=8}
#### Papworth

#COVID-19 spikes in the post switch period are impacting LoS and these are not seen in the controls

#LoS_RGM<-tar_read(LoS_RGM)

#evaluating_model("RGM", "RGM22", length_of_stay, "2019-05-01", "avg_los", 0.05, LoS_RGM, single_bedroom_matches_final)

```

```{r, include=TRUE, fig.width=5, fig.height=6}

#cia_summary_plots(LoS_RGM, "Study site: Papworth, RGM","Average LoS (days)", "2019-05-01")
```

::: columns
::: {.column width="50%"}
#### Peterborough

```{r, include=FALSE, fig.width=8, fig.height=8}

LoS_RGN<-tar_read(LoS_RGN)

#evaluating_model("RGN",  "RGN80", length_of_stay, "2010-11-01","avg_los", 0.05, LoS_RGN, single_bedroom_matches_final)


```

```{r, include=TRUE, fig.width=5, fig.height=6}

cia_summary_plots(LoS_RGN, "Average LoS (days)", "2010-11-01")
```

#### Chase Farm

```{r, include=FALSE, fig.width=8, fig.height=8}

LoS_RAL<-tar_read(LoS_RAL)

#evaluating_model("RAL", "RALC7", length_of_stay, "2018-09-01", "avg_los", 0.05, LoS_RAL, single_bedroom_matches_final)

```

```{r, include=TRUE, fig.width=5, fig.height=6}

cia_summary_plots(LoS_RAL,"Average LoS (days)", "2018-09-01")
```
:::

::: {.column width="50%"}
#### Southmead

```{r, include=FALSE, fig.width=8, fig.height=8}

LoS_RVJ<-tar_read(LoS_RVJ)

#evaluating_model("RVJ","RVJ01",  length_of_stay, "2014-05-01", "avg_los", 0.05, LoS_RVJ, single_bedroom_matches_final)

```

```{r, include=TRUE, fig.width=5, fig.height=6}

cia_summary_plots(LoS_RVJ,"Average LoS (days)", "2014-05-01")
```
:::
:::

### No change

#### Royal Liverpool

```{r, include=FALSE, fig.width=8, fig.height=8}

LoS_REM<-tar_read(LoS_REM)

#evaluating_model("REM", "REMRQ",  length_of_stay, "2022-10-01", "avg_los", 0.05, LoS_REM, single_bedroom_matches_final)


```

```{r, include=TRUE, fig.width=5, fig.height=6}

cia_summary_plots(LoS_REM, "Average LoS (days)", "2022-10-01")
```

### Increase

::: columns
::: {.column width="50%"}
#### Clatterbridge

```{r, include=FALSE, fig.width=8, fig.height=8}

LoS_REN<-tar_read(LoS_REN)

evaluating_model("REN", "REN22", length_of_stay, "2020-06-01", "avg_los", 0.05, LoS_REN, single_bedroom_matches_final)

```

```{r, include=TRUE, fig.width=5, fig.height=6}

cia_summary_plots(LoS_REN,"Average LoS (days)", "2020-06-01")


```
:::

::: {.column width="50%"}
#### Tunbridge Wells

```{r, include=FALSE, fig.width=8, fig.height=8}

LoS_RWF<-tar_read(LoS_RWF)

#evaluating_model("RWF",  "RWFTW", length_of_stay, "2011-01-01", "avg_los", 0.05, LoS_RWF, single_bedroom_matches_final)


```

```{r, include=TRUE, fig.width=5, fig.height=6}

cia_summary_plots(LoS_RWF,"Average LoS (days)", "2011-01-01")
```
:::
:::
:::

## Emergency Readmissions

::: panel-tabset
### Summary

```{r, fig.width=8, fig.height=4}

emergency_readmissions_output<-tar_read(emergency_readmissions_output)

forest_plot(emergency_readmissions_output)

model_effects_table(emergency_readmissions_output)


```

### Decrease

::: columns
::: {.column width="50%"}
#### Clatterbridge

```{r, include=FALSE, fig.width=8, fig.height=8}

emergency_readmissions_REN<-tar_read(emergency_readmissions_REN)

#evaluating_model("REN", "REN22", emergency_readmissions, "2020-06-01","perc", 0.05, emergency_readmissions_REN, single_bedroom_matches_final)

```

```{r, include=TRUE, fig.width=5, fig.height=6}

cia_summary_plots(emergency_readmissions_REN, "% readmissions", "2020-06-01")

```

#### Peterborough

```{r, include=FALSE, fig.width=8, fig.height=8}

emergency_readmissions_RGN<-tar_read(emergency_readmissions_RGN)

#evaluating_model("RGN",  "RGN80", emergency_readmissions, "2010-11-01","perc", 0.05, emergency_readmissions_RGN, single_bedroom_matches_final)


```

```{r, include=TRUE, fig.width=5, fig.height=6}

cia_summary_plots(emergency_readmissions_RGN,"% readmissions", "2010-11-01")
```
:::

::: {.column width="50%"}
#### Tunbridge Wells

```{r, include=FALSE, fig.width=8, fig.height=8}

emergency_readmissions_RWF<-tar_read(emergency_readmissions_RWF)

#evaluating_model("RWF",  "RWFTW", emergency_readmissions, "2011-01-01", "perc", 0.05, emergency_readmissions_RWF, single_bedroom_matches_final)


```

```{r, include=TRUE, fig.width=5, fig.height=6}

cia_summary_plots(emergency_readmissions_RWF, "% readmissions", "2011-01-01")
```
:::
:::

### No change

::: columns
::: {.column width="50%"}
#### Royal Liverpool

```{r, include=FALSE, fig.width=8, fig.height=8}

emergency_readmissions_REM<-tar_read(emergency_readmissions_REM)

#evaluating_model("REM", "REMRQ",  emergency_readmissions, "2022-10-01", "perc", 0.05, emergency_readmissions_REM, single_bedroom_matches_final)


```

```{r, include=TRUE, fig.width=5, fig.height=6}

cia_summary_plots(emergency_readmissions_REM, "% readmissions", "2022-10-01")
```

#### Papworth

```{r, include=FALSE, fig.width=8, fig.height=8}

emergency_readmissions_RGM<-tar_read(emergency_readmissions_RGM)

#evaluating_model("RGM", "RGM22", emergency_readmissions, "2019-05-01", "perc", 0.05, emergency_readmissions_RGM, single_bedroom_matches_final)


```

```{r, include=TRUE, fig.width=5, fig.height=6}

cia_summary_plots(emergency_readmissions_RGM, "% readmissions", "2019-05-01")
```
:::

::: {.column width="50%"}
#### Chase Farm

```{r, include=FALSE, fig.width=8, fig.height=8}

emergency_readmissions_RAL<-tar_read(emergency_readmissions_RAL)

#evaluating_model("RAL", "RALC7", emergency_readmissions, "2018-09-01", "perc", 0.05, emergency_readmissions_RAL, single_bedroom_matches_final)

```

```{r, include=TRUE, fig.width=5, fig.height=6}

cia_summary_plots(emergency_readmissions_RAL,"% readmissions", "2018-09-01")

pred <- emergency_readmissions_RAL$Predictions

```

#### Southmead

```{r, include=FALSE, fig.width=8, fig.height=8}

emergency_readmissions_RVJ<-tar_read(emergency_readmissions_RVJ)

#evaluating_model("RVJ","RVJ01",  emergency_readmissions, "2014-05-01","perc", 0.05, emergency_readmissions_RVJ, single_bedroom_matches_final)

```

```{r, include=TRUE, fig.width=5, fig.height=6}

cia_summary_plots(emergency_readmissions_RVJ, "% readmissions", "2014-05-01")
```
:::
:::
:::

## Bed Occupancy

::: panel-tabset
### Summary

```{r, fig.width=8, fig.height=4}

bed_occupancy_output<-tar_read(bed_occupancy_output)

forest_plot(bed_occupancy_output)

model_effects_table(bed_occupancy_output)


```

```{r, include=FALSE, fig.width=8, fig.height=8}

#### Papworth - Only 4 points post switch and last one might be impacted by COVID

#Post switch period is impacted by COVID-19

#bed_occupancy_RGM<-tar_read(bed_occupancy_RGM)

#evaluating_model("RGM",NA, bed_occupancy, "2019-05-01", "bed_occupancy", 0.05, bed_occupancy_RGM, single_bedroom_matches_final)

```

```{r, include=TRUE, fig.width=5, fig.height=6}

#cia_summary_plots(bed_occupancy_RGM,"Percentage", "2019-05-01")
```

### No change

::: columns
::: {.column width="50%"}
#### Royal Liverpool

```{r, include=FALSE, fig.width=8, fig.height=8}

bed_occupancy_REM<-tar_read(bed_occupancy_REM)

#evaluating_model("REM", NA, bed_occupancy, "2022-10-01", "bed_occupancy", 0.05, bed_occupancy_REM, single_bedroom_matches_final)

```

```{r, include=TRUE, fig.width=5, fig.height=6}

cia_summary_plots(bed_occupancy_REM, "Percentage", "2022-10-01")
```
:::

::: {.column width="50%"}
#### Chase Farm

```{r, include=FALSE, fig.width=8, fig.height=8}

bed_occupancy_RAL<-tar_read(bed_occupancy_RAL)

evaluating_model("RAL",NA,  bed_occupancy, "2018-09-01", "bed_occupancy", 0.05, bed_occupancy_RAL, single_bedroom_matches_final)

```

```{r, include=TRUE, fig.width=5, fig.height=6}

cia_summary_plots(bed_occupancy_RAL, "Percentage", "2018-09-01")
```
:::
:::

### Increase

::: columns
::: {.column width="50%"}
#### Clatterbridge

```{r, include=FALSE, fig.width=8, fig.height=8}

bed_occupancy_REN<-tar_read(bed_occupancy_REN)

#evaluating_model("REN", NA, bed_occupancy, "2020-06-01", "bed_occupancy", 0.05, bed_occupancy_REN, single_bedroom_matches_final)


```

```{r, include=TRUE, fig.width=5, fig.height=6}

cia_summary_plots(bed_occupancy_REN,"Percentage", "2020-06-01")
```
:::

::: {.column width="50%"}
#### Southmead

```{r, include=FALSE, fig.width=8, fig.height=8}

bed_occupancy_RVJ<-tar_read(bed_occupancy_RVJ)

#evaluating_model("RVJ", NA, bed_occupancy, "2014-05-01", "bed_occupancy", 0.05, bed_occupancy_RVJ, single_bedroom_matches_final)


```

```{r, include=TRUE, fig.width=5, fig.height=6}

cia_summary_plots(bed_occupancy_RVJ, "Percentage", "2014-05-01")
```
:::
:::
:::

## Summary of effects across sites

```{r}


  hcai_output  <-tar_read(hcai_output)
  falls_and_fractures_output  <-tar_read(falls_and_fractures_output)
  sus_deaths_output  <-tar_read(sus_deaths_output)
  friends_and_family_output  <-tar_read(friends_and_family_output)
  staff_sickness_output  <-tar_read(staff_sickness_output)

summary_table_indicators_and_sites(waiting_time_median_output,
                                             waiting_time_number_output,
                                             LoS_output,
                                             emergency_readmissions_output,
                                             bed_occupancy_output,
                                             hcai_output,
                                             falls_and_fractures_output,
                                             sus_deaths_output,
                                             friends_and_family_output,
                                             staff_sickness_output) 

```
