---
title: "Causal Impact Analysis: Health and Safety and Patient and Staff experience"
editor: visual
execute:
  echo: false
  message: false
  warning: false
  cache: false
lang: en-GB
author: Sarah Lucas
date: last-modified
date-format: "YYYY-MM-DD"
title-block-banner: "#f9bf07"
title-block-banner-color: "#333739"
format:
  html:
    embed-resources: true
    smooth-scroll: true
    theme: cosmo
    fontcolor: black
    toc: true
    toc-location: left
    toc-title: Summary
    toc-depth: 3
    grid:
      sidebar-width: 250px
      body-width: 1050px
      margin-width: 0px
      gutter-width: 1.5rem
css: styles.css
---

```{r, include=FALSE}

library(tidyverse)
library(MarketMatching)
library(tsibble)
library(targets)
library(janitor)
library(readxl)
library(zoo)
library(lubridate)
library(ggrepel)
library(flextable)
library(egg)
library(StrategyUnitTheme)

## Friends & Family
friends_and_family<-tar_read(friends_and_family_cia_format)

## Staff turnover
staff_turnover<-tar_read(staff_turnover_cia_format)

## Staff sickness
staff_sickness<-tar_read(staff_sickness_cia_format)

## Healthcare acquired infections - Infection rate per 10,000 bed days
hcai<-tar_read(hcai_cia_format)

## In-hospital Falls and Fractures - Fall rate per 1000 bed days
falls_and_fractures<- tar_read(falls_and_fractures_cia_format)

# SUS death rate (deaths/1000 admissions)
sus_deaths<- tar_read(sus_deaths_cia_format)

#survey<-read_csv("Z:/Strategic Analytics/Projects 2024/1220 - NHP Single Bed Rooms/Data/staff_survey.csv")

#test<-survey|>
#  clean_names()|>
#      mutate(effective_snapshot_date = as.Date(effective_snapshot_date, "%Y-%m-%d")) |> #Format date
#    mutate(month = floor_date(effective_snapshot_date, "month"))|>  #Format date to monthly
#  filter( str_detect(breakdown_category,"Registered Nurses & Midwives:")|
 #       breakdown_category=="Nursing auxiliary / Nursing assistant / Healthcare assistant") |>
 #   

 # filter(question=="q21c - I would recommend my organisation as a place to work.")|>

matches<-tar_read(single_bedroom_matches)

source("R/CIA_Functions.R")

```

# Availability of indicators by site

```{r, fig.height=6, fig.width=10}

tar_read(indicator_availability_plot)

```

```{r}

tar_read(indicator_availability_table)


```

# Health and Safety

## Healthcare acquired infections

Combined rate per 10,000 beddays

#### Royal Liverpool

```{r, include=FALSE, fig.width=8, fig.height=8}

hcai_REM<-tar_read(hcai_REM)

#evaluating_model("REM", NA, hcai, "2022-10-01", "combined_rate", 0.05, hcai_REM)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(hcai_REM, "Study site: Royal Liverpool, REM","Rate/10,000 beddays", "2022-10-01")
```

#### Clatterbridge

```{r, include=FALSE, fig.width=8, fig.height=8}

hcai_REN<-tar_read(hcai_REN)

#evaluating_model("REN",NA,  hcai, "2020-06-01", "combined_rate", 0.05, hcai_REN)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(hcai_REN, "Study site: Clatterbridge, REN","Rate/10,000 beddays", "2020-06-01")
```

## Falls and Fractures in hospital

#### Royal Liverpool

```{r, include=FALSE, fig.width=8, fig.height=8}

falls_and_fractures_REM<-tar_read(falls_and_fractures_REM)

#evaluating_model("REM", "REMRQ",  falls_and_fractures, "2022-10-01", "ff_rate", 0.05, falls_and_fractures_REM)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(falls_and_fractures_REM, "Study site: Royal Liverpool, REM","% of spells", "2022-10-01")
```

#### Clatterbridge

```{r, include=FALSE, fig.width=8, fig.height=8}

falls_and_fractures_REN<-tar_read(falls_and_fractures_REN)

#evaluating_model("REN", "REN22", falls_and_fractures, "2020-06-01","ff_rate", 0.05, falls_and_fractures_REN)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(falls_and_fractures_REN, "Study site: Clatterbridge, REN","% of spells", "2020-06-01")


```

#### Papworth

```{r, include=FALSE, fig.width=8, fig.height=8}

falls_and_fractures_RGM<-tar_read(falls_and_fractures_RGM)

#evaluating_model("RGM", "RGM22", falls_and_fractures, "2019-05-01", "ff_rate", 0.05, falls_and_fractures_RGM)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(falls_and_fractures_RGM, "Study site: Papworth, RGM","% of spells", "2019-05-01")
```

#### Peterborough

```{r, include=FALSE, fig.width=8, fig.height=8}

falls_and_fractures_RGN<-tar_read(falls_and_fractures_RGN)

#evaluating_model("RGN",  "RGN80",falls_and_fractures, "2010-11-01","ff_rate", 0.05, falls_and_fractures_RGN)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(falls_and_fractures_RGN, "Study site: Peterborough, RGN","% of spells", "2010-11-01")
```

#### Chase Farm

```{r, include=FALSE, fig.width=8, fig.height=8}

#falls_and_fractures_RAL<-tar_read(falls_and_fractures_RAL)

#evaluating_model("RAL", "RALC7", falls_and_fractures, "2018-09-01", "ff_rate", 0.05, falls_and_fractures_RAL)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

#cia_summary_plots(falls_and_fractures_RAL, "Study site: Chase Farm, RAL","% of spells", "2018-09-01")
```

#### Southmead

```{r, include=FALSE, fig.width=8, fig.height=8}

falls_and_fractures_RVJ<-tar_read(falls_and_fractures_RVJ)

#evaluating_model("RVJ","RVJ01",  falls_and_fractures, "2014-05-01","ff_rate", 0.05, falls_and_fractures_RVJ)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(falls_and_fractures_RVJ, "Study site: Southmead, RVJ","% of spells", "2014-05-01")
```

#### Tunbridge Wells

```{r, include=FALSE, fig.width=8, fig.height=8}

falls_and_fractures_RWF<-tar_read(falls_and_fractures_RWF)

#evaluating_model("RWF",  "RWFTW", falls_and_fractures, "2011-01-01", "ff_rate", 0.05, falls_and_fractures_RWF)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(falls_and_fractures_RWF, "Study site: Tunbridge Wells, RWF","% of spells", "2011-01-01")
```

## Deaths in hospital

#### Royal Liverpool

```{r, include=FALSE, fig.width=8, fig.height=8}

sus_deaths_REM<-tar_read(sus_deaths_REM)

#evaluating_model("REM", "REMRQ",  sus_deaths, "2022-10-01", "hosp_rate_1000", 0.05, sus_deaths_REM)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(sus_deaths_REM, "Study site: Royal Liverpool, REM","No./per 1,000 discharges", "2022-10-01")
```

#### Clatterbridge

```{r, include=FALSE, fig.width=8, fig.height=8}

sus_deaths_REN<-tar_read(sus_deaths_REN)

evaluating_model("REN", "REN22", sus_deaths, "2020-06-01","hosp_rate_1000", 0.05, sus_deaths_REN)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(sus_deaths_REN, "Study site: Clatterbridge, REN","No./per 1,000 discharges", "2020-06-01")

```

```{r, include=FALSE}

sus_deaths|>
  filter(site_code=="REN22"|
         site_code=="REN20"| 
         site_code=="REN01"| 
         site_code=="REN21" )|>
  ggplot()+
  geom_line(aes(x=month, y=discharges, group=site_code, colour=site_code))+
  scale_y_continuous(limits=c(0,NA))

sus_deaths|>
  filter(site_code=="REN22"|
         site_code=="REN20"| 
         site_code=="REN01"| 
         site_code=="REN21")|>
  ggplot()+
  geom_line(aes(x=month, y=death_hosp, group=site_code, colour=site_code))+
  scale_y_continuous(limits=c(0,NA))

sus_deaths|>
  filter(site_code=="REN22"|
         site_code=="REN20"| 
         site_code=="REN01"| 
         site_code=="REN21")|>
  ggplot()+
  geom_line(aes(x=month, y=hosp_rate_1000, group=site_code, colour=site_code))+
  scale_y_continuous(limits=c(0,NA))

```

#### Papworth

```{r, include=FALSE, fig.width=8, fig.height=8}

sus_deaths_RGM<-tar_read(sus_deaths_RGM)

#evaluating_model("RGM", "RGM22", sus_deaths, "2019-05-01", "hosp_rate_1000", 0.05, sus_deaths_RGM)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(sus_deaths_RGM, "Study site: Papworth, RGM","No./per 1,000 discharges", "2019-05-01")
```

#### Peterborough

```{r, include=FALSE, fig.width=8, fig.height=8}

sus_deaths_RGN<-tar_read(sus_deaths_RGN)

#evaluating_model("RGN",  "RGN80", sus_deaths, "2010-11-01","hosp_rate_1000", 0.05, sus_deaths_RGN)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(sus_deaths_RGN, "Study site: Peterborough, RGN","No./per 1,000 discharges", "2010-11-01")
```

#### Chase Farm

Missing data in 2019 and 2020

```{r, include=FALSE, fig.width=8, fig.height=8}

sus_deaths_RAL<-tar_read(sus_deaths_RAL)

#evaluating_model("RAL", "RALC7", sus_deaths, "2018-09-01","hosp_rate_1000", 0.05, sus_deaths_RAL)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(sus_deaths_RAL, "Study site: Chase Farm, RAL","No./per 1,000 discharges", "2018-09-01")
```

#### Southmead

```{r, include=FALSE, fig.width=8, fig.height=8}

sus_deaths_RVJ<-tar_read(sus_deaths_RVJ)

#evaluating_model("RVJ","RVJ01",  sus_deaths, "2014-05-01","hosp_rate_1000", 0.05, sus_deaths_RVJ)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(sus_deaths_RVJ, "Study site: Southmead, RVJ","No./per 1,000 discharges", "2014-05-01")
```

#### Tunbridge Wells

```{r, include=FALSE, fig.width=8, fig.height=8}

sus_deaths_RWF<-tar_read(sus_deaths_RWF)

#evaluating_model("RWF",  "RWFTW", sus_deaths, "2011-01-01", "hosp_rate_1000", 0.05, sus_deaths_RWF)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(sus_deaths_RWF, "Study site: Tunbridge Wells, RWF","No./per 1,000 discharges", "2011-01-01")
```

# Patient and Staff Experience

## Patient experience - Friends and Family scores

#### Royal Liverpool (REMRQ)

```{r, include=FALSE, fig.height=8, fig.width=8}

friends_and_family_REMRQ<-tar_read(friends_and_family_REMRQ)

#evaluating_model("REM","REMRQ", friends_and_family,"2022-10-01", "friends_and_family_percent", 0.05, friends_and_family_REMRQ)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(friends_and_family_REMRQ, "Study site: Royal Liverpool, REMRQ","Positive responses (%)", "2022-10-01")


# Large amount of data missing in the two years prior due to gap over covid. One of the control sites doesn't go back far enough for it is causing the data to be cut off. Think I need to have less matches for this one. But would still have a disturbed pre switch period due to COVID

```

#### Clatterbridge (REN)

```{r, include=FALSE, fig.width=8, fig.height=8}


friends_and_family_REN22<-tar_read(friends_and_family_REN22)

#evaluating_model("REN","REN22", friends_and_family,"2020-06-01", "friends_and_family_percent", 0.05,friends_and_family_REN22 )

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(friends_and_family_REN22, "Study site: Clatterbridge, REN22","Positive responses (%)", "2020-06-01")

#Last data point prior to switch was about 4 months prior then no data for 8 months after, as switch came during COVID

```

#### Papworth (RGM)

```{r, include=FALSE, fig.width=8, fig.height=8}

friends_and_family_RGM22<-tar_read(friends_and_family_RGM22)

#evaluating_model("RGM", "RGM22", friends_and_family,"2019-05-01", "friends_and_family_percent", 0.05, friends_and_family_RGM22)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(friends_and_family_RGM22, "Study site: Papworth, RGM22","Positive responses (%)", "2019-05-01")
```

#### Chase Farm Hospital (RAL)

```{r, include=FALSE, fig.width=8, fig.height=8}

friends_and_family_RALC7<-tar_read(friends_and_family_RALC7)


#evaluating_model("RAL","RALC7",  friends_and_family,"2018-09-01", "friends_and_family_percent", 0.05, friends_and_family_RALC7)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(friends_and_family_RALC7, "Study site: Chase Farm Hospital, RALC7","Positive responses (%)", "2018-09-01")
```

## Staff sickness

#### Royal Liverpool (REM)

```{r, include=FALSE, fig.height=8, fig.width=8}

staff_sickness_REM<-tar_read(staff_sickness_REM)


#evaluating_model("REM",NA, staff_sickness,"2022-10-01", "staff_sickness_percent", 0.05, staff_sickness_REM)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(staff_sickness_REM, "Study site: Royal Liverpool, REM","Sickness Rate (%)", "2022-10-01")

```

#### Clatterbridge (REN)

```{r, include=FALSE, fig.width=8, fig.height=8}

staff_sickness_REN<-tar_read(staff_sickness_REN)

#evaluating_model("REN", NA,staff_sickness,"2020-06-01", "staff_sickness_percent", 0.05,staff_sickness_REN )

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(staff_sickness_REN, "Study site: Clatterbridge, REN","Sickness Rate (%)", "2020-06-01")

```

#### Papworth (RGM)

```{r, include=FALSE, fig.width=8, fig.height=8}

staff_sickness_RGM<-tar_read(staff_sickness_RGM)

#evaluating_model("RGM", NA,staff_sickness,"2019-05-01", "staff_sickness_percent", 0.05, staff_sickness_RGM)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(staff_sickness_RGM, "Study site: Papworth, RGM","Sickness Rate (%)", "2019-05-01")
```

#### Chase Farm Hospital (RAL)

```{r, include=FALSE, fig.width=8, fig.height=8}

staff_sickness_RAL<-tar_read(staff_sickness_RAL)


#evaluating_model("RAL", staff_sickness,"2018-09-01", "staff_sickness_percent", 0.05, staff_sickness_RAL)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(staff_sickness_RAL,NA, "Study site: Chase Farm Hospital, RAL","Sickness Rate (%)", "2018-09-01")
```

#### Southmead (RVJ)

```{r, include=FALSE, fig.width=8, fig.height=8}

staff_sickness_RVJ<-tar_read(staff_sickness_RVJ)

#evaluating_model("RVJ", NA,staff_sickness,"2014-05-01", "staff_sickness_percent", 0.05, staff_sickness_RVJ)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(staff_sickness_RVJ, "Study site: Southmead, RVJ","Sickness Rate (%)", "2014-05-01")
```

```{r, include= FALSE, fig.height=8, fig.width=8}

## Staff turnover

#### Royal Liverpool (REM)

#staff_turnover_REM<-cia_analysis("REM", NA, staff_turnover,"2022-10-01", "leaving_rate", 0.05)


#evaluating_model("REM", NA,staff_turnover,"2022-10-01", "leaving_rate", 0.05, staff_turnover_REM)


# denominator appears to remain constant but for 12 months between Sept 2019 to Aug 2020, the numbers of leavers and joiners recorded is approx. 6 times higher than usual.

cia_summary_plots(staff_turnover_REM, "Study site: Royal Liverpool, REM","Leaving Rate (%)", "2022-10-01")


```

```{r, include=FALSE}
# Other plots information

## Cleaning staff



#cleaning_staff<-tar_read(eric_udal)|>
#  filter(measure=="Cleaning staff (WTE)")|>
#  filter(level=="Site")|>
#  mutate(month=floor_date(effective_snapshot_date, "month"))|> #Format date to monthly
#  left_join(beddays[,c("der_provider_site_code", "beddays", "yearmon")], #by=c("site_code"="der_provider_site_code", "month"="yearmon")) |>
#  merge_sites()|>
#  group_by(month, site_code)|>
#  summarise(value=sum(value), beddays=sum(beddays))|>
#  mutate(rate=(value/beddays)*1000) #WTE per 1000 beddays

```

```{r, include=FALSE}
## C. Difficile rate over time

#c.diff only as this goes back before 2017/2018
#tar_read(formatted_HCAI_data)|>
#  left_join(beddays_by_prov[,c("organisation_code", "yearmon", "beddays")], by=c("organisation_code", "month"="yearmon"))|>
#  mutate(rate=(count_of_cases/beddays)*10000)|> #cases per 10,000 beddays
#filter(collection=="C.difficile")|>
#  filter(organisation_code=="REM")|> #for Royal Liverpool
#    ggplot(aes(x = month, y =rate) ) + 
#   geom_line(linewidth=1) 


# C. Difficile numbers are too small to use in CIA as so much variability.

```
