---
title: "Causal Impact Analysis"
editor: visual
execute:
  echo: false
  message: false
  warning: false
  cache: false
lang: en-GB
author: Sarah Lucas
date: last-modified
date-format: "YYYY-MM-DD"
title-block-banner: "#f9bf07"
title-block-banner-color: "#333739"
format:
  html:
    embed-resources: true
    smooth-scroll: true
    theme: cosmo
    fontcolor: black
    toc: true
    toc-location: left
    toc-title: Summary
    toc-depth: 3
css: styles.css
---

```{r, include=FALSE}


# Extra data wrangling

library(tidyverse)
library(MarketMatching)
library(tsibble)
library(targets)
library(janitor)
library(readxl)
library(zoo)
library(lubridate)
library(ggrepel)
library(flextable)
library(egg)

library(StrategyUnitTheme)

## Friends & Family
friends_and_family<-tar_read(friends_and_family_cia_format)
  #filter(site_code=="REMRQ"|site_code=="REM21"|site_code=="RBN01"|site_code=="REMBG"|
  #       site_code=="RVY01"|site_code=="RVY02"|site_code=="RJR05")

## Staff turnover
staff_turnover<-tar_read(staff_turnover_cia_format)


## Staff sickness
staff_sickness<-tar_read(staff_sickness_cia_format)

## Healthcare acquired infections - Infection rate per 10,000 bed days
hcai<-tar_read(hcai_cia_format)

## In-hospital Falls and Fractures - Fall rate per 1000 bed days
falls_and_fractures<- tar_read(falls_and_fractures_cia_format)

# SUS death rate (deaths/1000 admissions)
sus_deaths<- tar_read(sus_deaths_cia_format)

## RTT waiting time
rtt_waiting_time<-tar_read(rtt_waiting_time_cia_format) |>
 filter(organisation_code=="REM"|organisation_code=="RJR"|organisation_code=="RVY"|
          organisation_code==  "RBN")

## Bed occupancy
bed_occupancy<-tar_read(bed_occupancy_cia_format)

## Length of Stay
length_of_stay<- tar_read(length_of_stay_cia_format)
#  filter(site_code=="RGM22")|> 
#    ggplot(aes(x = month, y =avg_los) ) + 
#   geom_line(linewidth=1) 

## TO DO Emergency readmissions
```

#Functions
```{r}

# Function to find the best matches
select_matches<-function(organisation, data, switch_month, variable){
  
matches<-tar_read(single_bedroom_matches)|>
   filter(organisation_code==organisation)
 
 dataset<-data|>
   filter(organisation_code==organisation | organisation_code %in% matches$matching_organisation_code)|>
   left_join(matches[,c("matching_organisation_code", "trust_name")],    by=c("organisation_code"="matching_organisation_code"))|> # Add name of matched sites
      distinct()|>
   filter(month!=switch_month |organisation_code!=organisation) #remove month of switch
 
 # Find best matches
 mm <- MarketMatching::best_matches(data=dataset,
                   id_variable="organisation_code",
                   date_variable="month",
                   matching_variable={{variable}},
                   parallel=FALSE,
                   warping_limit=1, 
                   dtw_emphasis=1, 
                   matches=5, 
                   start_match_period=(as.Date(switch_month) %m-% months(72)),
                   end_match_period=(as.Date(switch_month)))

 return(mm)

}

# Function to run the CIA   
cia_analysis<-function(organisation,data, switch_month, variable, prior_sd){

  mm<-select_matches(organisation, data, switch_month, variable)

 #View the best matches
  value<-mm$BestMatches|>
  filter(organisation_code==organisation)

  # Run the causal impact analysis
results <- MarketMatching::inference(matched_markets = mm,
                                     analyze_betas=TRUE,
                                     test_market = organisation,
                                    end_post_period =(as.Date(switch_month) %m+% months(24)),
                                    alpha=0.05, 
                                    prior_level_sd= prior_sd)

# See which hospital receives the highest weight in determining the outcome
coeff <- results$Coefficients

#Store predicted values in dataframe
pred <- results$Predictions

return(results)

}


evaluating_model<-function(organisation, data, switch_month, variable, prior_sd, model){
  
mm<-  select_matches(organisation, data, switch_month, variable)
  
#Prospective Pseudo Power Curves -will help you evaluate if your choice of test and control markets creates a sufficient model to measure a realistic lift from a future intervention. 
power <- MarketMatching::test_fake_lift(matched_markets = mm, 
                                      test_market = organisation, 
                                      end_fake_post_period = (as.Date(switch_month) %m+% months(24)), 
                                      prior_level_sd = prior_sd, 
                                      steps=10,
                                      max_fake_lift=0.1)

#Plot the actuals 
a<-model$PlotActuals+
  su_theme()

# Check out the DW and MAPE of the model
b<-model$PlotPriorLevelSdAnalysis+
  su_theme()

#And plot the graph- Ideally, a curve that starts at high probability on the left side, reaches its minimum at zero lift, and then rises again symmetrically. If the curve does not reach its minimum at zero there may be systemic model bias in the post period. 
c<-power$ResultsGraph+
  su_theme()

figure<-ggarrange(a,b,c,
                  ncol=1)

}

cia_summary_plots<-function(results, title, ylab, switch_date){

# Plot out actual vs expected
a<-results$PlotActualVersusExpected+
  su_theme()+
  labs(title=title, y=ylab)+
  theme(axis.text = element_text(size=12), 
        axis.title = element_text(size=14), 
        legend.title =element_blank(),
        legend.text=element_text(size=12))+
 annotate(geom="text", x=as.Date(switch_date),  y=0.1, hjust=1.05, label="SBR switch", color="#ec6555")+
   geom_vline(aes(xintercept =as.Date(switch_date)), y=0,  linetype="dashed", linewidth=0.6, color="#ec6555")+
  scale_color_manual(values=c("#f9bf07","#2c2825" ))+
scale_x_date(date_breaks = "1 year",date_labels = "%Y")+
  scale_y_continuous(limits=c(0,NA))+ 
  guides(colour = guide_legend(reverse=T))

# Plot pointwise effect
b<-results$PlotPointEffect+
  su_theme()+
  theme(axis.text = element_text(size=12), axis.title = element_text(size=14))+
  geom_hline(aes(yintercept =0), linetype="dotted", color="#686f73", linewidth=0.4)+
  geom_vline(aes(xintercept =as.Date(switch_date)), y=0,  linetype="dashed", linewidth=0.6, color="#ec6555")+
scale_x_date(date_breaks = "1 year",date_labels = "%Y")

# Plot out cumulative effect
c<-results$PlotCumulativeEffect+
  su_theme()+
    theme(axis.text = element_text(size=12), axis.title = element_text(size=14))+
  geom_hline(aes(yintercept =0), linetype="dotted", color="#686f73", linewidth=0.4)+
  geom_vline(aes(xintercept =as.Date(switch_date)), y=0,  linetype="dashed", linewidth=0.6, color="#ec6555")+
scale_x_date(date_breaks = "1 year",date_labels = "%Y")

figure<-ggarrange(a,b,c, ncol=1)
}



```



# Availability of indicators by site

```{r, fig.height=5, fig.width=10}


  measure<-c("friends and family test", "staff turnover", "staff sickness", "healthcare acquired infections", "falls and fractures", "hospital deaths", "rtt waiting times", "bed occupancy", "length of stay" )
    start_date<-c(min(friends_and_family$month), min(staff_turnover$month), min(staff_sickness$month), min(hcai$month), min(falls_and_fractures$month), min(sus_deaths$month), min(rtt_waiting_time$month), min(bed_occupancy$month), min(length_of_stay$month))
      end_date<-c(max(friends_and_family$month), max(staff_turnover$month), max(staff_sickness$month), max(hcai$month), max(falls_and_fractures$month), max(sus_deaths$month), max(rtt_waiting_time$month), max(bed_occupancy$month), max(length_of_stay$month))


indicators<- data.frame(measure, start_date, end_date)|>
 gather(key=type, value=range, -measure)|>
    mutate(range=as.Date(range))


name<-c("Royal Liverpool", "Clatterbridge", "Papworth", "Peterborough", "Chase Farm", "Southmead", "Tunbridge Wells")
date<-c('2022-10-01', '2020-06-01', '2019-05-01', '2010-11-01', '2018-09-01', '2014-05-01', '2011-01-01' )

sites<-data.frame(name, date)|>
  mutate(date=as.Date(date))



ggplot(data=indicators,aes(y=measure, x=range))+
 geom_path(lineend = "round", color="#f9bf07", linewidth=5)+
labs(y=NULL, x=NULL)+
 su_theme()+
  theme(axis.text.y = element_text(size=12.5),axis.text.x = element_text(size=11),
        plot.margin = unit(c(4.5,1,1,1), "lines"))+
 geom_vline(data=sites, aes(xintercept =date), linetype="dashed", color="#2c2825", linewidth=0.8)+
 geom_text(data=sites|>filter(name!= "Peterborough" & name!="Tunbridge Wells"), aes(x=date, y=Inf, label=name), colour="#2c2825", angle=40, hjust=0, vjust=-0.2, text=element_text(size=11.5))+
  geom_text(data=sites|>filter(name== "Peterborough"), aes(x=date, y=Inf, label=name), colour="#2c2825", angle=40, hjust=0.1, vjust=-0.4, text=element_text(size=11))+
  geom_text(data=sites|>filter(name=="Tunbridge Wells"), aes(x=date, y=Inf, label=name), colour="#2c2825", angle=40, hjust=0, vjust=0.6, text=element_text(size=11))+
scale_x_date(date_breaks = "1 year",date_labels = "%Y")+
  coord_cartesian(clip = 'off') 




```

```{r}


indicator_availability_by_site<-indicators|>
  cross_join(sites)|>
  filter(type=="start_date")|>
   mutate(difference=as.numeric(date-range))|> #difference in days
  mutate(sufficient_baseline=ifelse(difference>=730, "yes", "no"))|>
  select(-difference, -date, -range, -type)|>
  pivot_wider( names_from = name, values_from=sufficient_baseline)

 colormatrix<-ifelse(indicator_availability_by_site=="no","#FBE0DC", 
                     ifelse(indicator_availability_by_site=="yes", "#d5eed1", "#FFFFFF"  ))
    
  
indicator_availability_by_site|>
  flextable() |>
  align(part = "header", align = "center")|>
    align(part = "body", align = "center")|>
  bg(bg = "#f9bf07", part = "header") |>
  bg(j=1:8, bg=colormatrix)|>
  bold(bold = TRUE, part="header")|>
   fontsize(size = 12, part = "all")|>
   padding(padding = 2, part = "all", padding.top=NULL) |>
 autofit()|>
      htmltools_value(ft.align = "left") 





```

# Patient and Staff Experience

## Patient experience - Friends and Family scores

Liverpool 
Clatterbridge 
Papworth 
Chase Farm

## Staff turnover

Liverpool

## Staff sickness

#### Royal Liverpool (REM)

```{r, fig.height=8, fig.width=8}

staff_sickness_REM<-cia_analysis("REM",  staff_sickness,"2022-10-01", "staff_sickness_percent", 0.05)


evaluating_model("REM", staff_sickness,"2022-10-01", "staff_sickness_percent", 0.05, staff_sickness_REM)



```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(staff_sickness_REM, "Study site: Royal Liverpool, REM","Sickness Rate (%)", "2022-10-01")

```

#### Clatterbridge (REN)

```{r, include=TRUE, fig.width=8, fig.height=8}

staff_sickness_REN<-cia_analysis("REN", staff_sickness,"2020-06-01", "staff_sickness_percent", 0.05)

evaluating_model("REN", staff_sickness,"2020-06-01", "staff_sickness_percent", 0.05,staff_sickness_REN )


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(staff_sickness_REN, "Study site: Clatterbridge, REN","Sickness Rate (%)", "2020-06-01")

```

#### Papworth (RGM)

```{r, include=TRUE, fig.width=8, fig.height=8}

staff_sickness_RGM<-cia_analysis("RGM", staff_sickness,"2019-05-01", "staff_sickness_percent", 0.05)

evaluating_model("RGM", staff_sickness,"2019-05-01", "staff_sickness_percent", 0.05, staff_sickness_RGM)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(staff_sickness_RGM, "Study site: Papworth, RGM","Sickness Rate (%)", "2019-05-01")
```

#### Chase Farm Hospital (RAL)

```{r, include=TRUE, fig.width=8, fig.height=8}

staff_sickness_RAL<-cia_analysis("RAL", staff_sickness,"2018-09-01", "staff_sickness_percent", 0.05)


evaluating_model("RAL", staff_sickness,"2018-09-01", "staff_sickness_percent", 0.05, staff_sickness_RAL)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(staff_sickness_RAL, "Study site: Chase Farm Hospital, RAL","Sickness Rate (%)", "2018-09-01")
```

#### Southmead (RVJ)

```{r, include=FALSE, fig.width=8, fig.height=8}

staff_sickness_RVJ<-cia_analysis("RVJ", staff_sickness,"2014-05-01", "staff_sickness_percent", 0.05)

evaluating_model("RVJ", staff_sickness,"2014-05-01", "staff_sickness_percent", 0.05, staff_sickness_RVJ)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(staff_sickness_RVJ, "Study site: Southmead, RVJ","Sickness Rate (%)", "2014-05-01")
```

# Productivity and Efficiency

## RTT Waiting time data- Median waiting time (in weeks)

```{r}

```

```{r, include=FALSE}



```

```{r, include=FALSE}
# Other plots information

## Cleaning staff



cleaning_staff<-tar_read(eric_udal)|>
  filter(measure=="Cleaning staff (WTE)")|>
  filter(level=="Site")|>
  mutate(month=floor_date(effective_snapshot_date, "month"))|> #Format date to monthly
  left_join(beddays[,c("der_provider_site_code", "beddays", "yearmon")], by=c("site_code"="der_provider_site_code", "month"="yearmon")) |>
  merge_sites()|>
  group_by(month, site_code)|>
  summarise(value=sum(value), beddays=sum(beddays))|>
  mutate(rate=(value/beddays)*1000) #WTE per 1000 beddays

```

```{r, include=FALSE}
## C. Difficile rate over time

#c.diff only as this goes back before 2017/2018
tar_read(formatted_HCAI_data)|>
  left_join(beddays_by_prov[,c("organisation_code", "yearmon", "beddays")], by=c("organisation_code", "month"="yearmon"))|>
  mutate(rate=(count_of_cases/beddays)*10000)|> #cases per 10,000 beddays
filter(collection=="C.difficile")|>
  filter(organisation_code=="REM")|> #for Royal Liverpool
    ggplot(aes(x = month, y =rate) ) + 
   geom_line(linewidth=1) 


# C. Difficile numbers are too small to use in CIA as so much variability.

```
