---
title: "Causal Impact Analysis"
editor: visual
execute:
  echo: false
  message: false
  warning: false
  cache: false
lang: en-GB
author: Sarah Lucas
date: last-modified
date-format: "YYYY-MM-DD"
title-block-banner: "#f9bf07"
title-block-banner-color: "#333739"
format:
  html:
    embed-resources: true
    smooth-scroll: true
    theme: cosmo
    fontcolor: black
    toc: true
    toc-location: left
    toc-title: Summary
    toc-depth: 3
    grid:
      sidebar-width: 250px
      body-width: 1050px
      margin-width: 0px
      gutter-width: 1.5rem
css: styles.css
---

```{r, include=FALSE}

library(tidyverse)
library(MarketMatching)
library(tsibble)
library(targets)
library(janitor)
library(readxl)
library(zoo)
library(lubridate)
library(ggrepel)
library(flextable)
library(egg)
library(StrategyUnitTheme)



## Friends & Family
friends_and_family<-tar_read(friends_and_family_cia_format)|>
  filter(!is.na(friends_and_family_percent))|>
  filter(site_code!="N6J7V" &
         site_code!="E0A3H")

## Staff turnover
staff_turnover<-tar_read(staff_turnover_cia_format)|>
  mutate(leaving_rate=ifelse(is.na(leaving_rate), 0, leaving_rate))|>
  filter(month>"2020-08-01" | organisation_code!="REM") |># Liverpool data issues before this point
  filter(organisation_code!="RVY")

## Staff sickness
staff_sickness<-tar_read(staff_sickness_cia_format)

## Healthcare acquired infections - Infection rate per 10,000 bed days
hcai<-tar_read(hcai_cia_format)

## In-hospital Falls and Fractures - Fall rate per 1000 bed days
falls_and_fractures<- tar_read(falls_and_fractures_cia_format)|>
  mutate(ff_rate=ifelse(is.nan(ff_rate), 0, ff_rate))|>
  filter(site_code!="RALC7"|month>'2014-03-01')

# SUS death rate (deaths/1000 admissions)
sus_deaths<- tar_read(sus_deaths_cia_format)

## RTT waiting time
rtt_waiting_time<-tar_read(rtt_waiting_time_cia_format) |>
  filter( organisation_code!="RF4" &  
        organisation_code!="R1H" &
         organisation_code!= "RJ2") #Removing poss control due to data issues

## Bed occupancy
bed_occupancy<-tar_read(bed_occupancy_cia_format)|>
  mutate(bed_occupancy=bed_occupancy*100)|>
  filter(organisation_code!="R0A" & organisation_code!="RNL") #remove controls for Chase Farm

## Length of Stay
length_of_stay<- tar_read(length_of_stay_cia_format)

## Emergency readmissions
emergency_readmissions<-tar_read(emergency_readmissions_cia_format)|>
  filter(site_code!="RXPCP" &
         site_code!="RVY01" &
         site_code!="RDEEB"&
         site_code!="RPA02")

#survey<-read_csv("Z:/Strategic Analytics/Projects 2024/1220 - NHP Single Bed Rooms/Data/staff_survey.csv")

#test<-survey|>
#  clean_names()|>
#      mutate(effective_snapshot_date = as.Date(effective_snapshot_date, "%Y-%m-%d")) |> #Format date
#    mutate(month = floor_date(effective_snapshot_date, "month"))|>  #Format date to monthly
#  filter( str_detect(breakdown_category,"Registered Nurses & Midwives:")|
 #       breakdown_category=="Nursing auxiliary / Nursing assistant / Healthcare assistant") |>
 #   

 # filter(question=="q21c - I would recommend my organisation as a place to work.")|>

matches<-tar_read(single_bedroom_matches)


rtt_test<-tar_read(rtt_waiting_time_cia_format)|>
  filter(organisation_code=="REM")


```

```{r}

# Function to find the best matches
select_matches<-function(organisation, data, switch_month, variable){
  
matches<-tar_read(single_bedroom_matches)|>
   filter(organisation_code==organisation)
 
 dataset<-data|>
   filter(organisation_code==organisation | organisation_code %in% matches$matching_organisation_code)|>
   left_join(matches[,c("matching_organisation_code", "trust_name")],    by=c("organisation_code"="matching_organisation_code"))|> # Add name of matched sites
      distinct()
  # filter(month!=switch_month |organisation_code!=organisation) #remove month of switch
 
 # Find best matches
 mm <- MarketMatching::best_matches(data=dataset,
                   id_variable="organisation_code",
                   date_variable="month",
                   matching_variable={{variable}},
                   parallel=FALSE,
                   warping_limit=1, 
                   dtw_emphasis=1, 
                   matches=5, 
                   start_match_period=(as.Date(switch_month) %m-% months(120)),
                   end_match_period=(as.Date(switch_month)))
 
  # start_match_period=(as.Date(min(data$month))),

 return(mm)

}



# Function to run the CIA   
cia_analysis<-function(organisation, data, switch_month, variable, prior_sd){

  mm<-select_matches(organisation, data, switch_month, variable)

 #View the best matches
  value<-mm$BestMatches|>
  filter(organisation_code==organisation)
  

  # Run the causal impact analysis
results <- MarketMatching::inference(matched_markets = mm,
                                     analyze_betas=TRUE,
                                     test_market = organisation,
                                    end_post_period =(as.Date(switch_month) %m+% months(24)),
                                    alpha=0.05, 
                                    prior_level_sd= prior_sd)

# See which hospital receives the highest weight in determining the outcome
coeff <- results$Coefficients

#Store predicted values in dataframe
pred <- results$Predictions

return(results)

}


evaluating_model<-function(organisation, data, switch_month, variable, prior_sd, model){
  
mm<-  select_matches(organisation, data, switch_month, variable)
  
#Prospective Pseudo Power Curves -will help you evaluate if your choice of test and control markets creates a sufficient model to measure a realistic lift from a future intervention. 
power <- MarketMatching::test_fake_lift(matched_markets = mm, 
                                      test_market = organisation, 
                                      end_fake_post_period = (as.Date(switch_month) %m+% months(24)), 
                                      prior_level_sd = prior_sd, 
                                      steps=10,
                                      max_fake_lift=0.1)

#Plot the actuals 
a<-model$PlotActuals+
  su_theme()

# Check out the DW and MAPE of the model
b<-model$PlotPriorLevelSdAnalysis+
  su_theme()

#And plot the graph- Ideally, a curve that starts at high probability on the left side, reaches its minimum at zero lift, and then rises again symmetrically. If the curve does not reach its minimum at zero there may be systemic model bias in the post period. 
c<-power$ResultsGraph+
  su_theme()

figure<-ggarrange(a,b,c,
                  ncol=1)

}

# Function to find the best matches FOR SITES
select_matches_sites<-function(organisation, site, data, switch_month, variable){
  
matches<-tar_read(single_bedroom_matches)|>
   filter(organisation_code==organisation)
 
 dataset<-data|>
   filter(site_code==site | site_code %in% matches$site_code)|>
   left_join(matches[,c("site_code", "trust_name")], by=c("site_code"))|> # Add name of matched sites
      distinct()
 #  filter(month!=switch_month |site_code!=site) #remove month of switch
 
 # Find best matches
 mm <- MarketMatching::best_matches(data=dataset,
                   id_variable="site_code",
                   date_variable="month",
                   matching_variable={{variable}},
                   parallel=FALSE,
                   warping_limit=1, 
                   dtw_emphasis=1, 
                   matches=5, 
                     start_match_period=(as.Date(switch_month) %m-% months(120)),
                   end_match_period=(as.Date(switch_month)))
 
    # start_match_period=(as.Date(min(data$month))),

 return(mm)

}



# Function to run the CIA FOR SITES   
cia_analysis_sites<-function(organisation, site, data, switch_month, variable, prior_sd){

  mm<-select_matches_sites(organisation, site, data, switch_month, variable)

 #View the best matches
  value<-mm$BestMatches|>
  filter(site_code==site)

  # Run the causal impact analysis
results <- MarketMatching::inference(matched_markets = mm,
                                     analyze_betas=TRUE,
                                     test_market = site,
                                    end_post_period =(as.Date(switch_month) %m+% months(24)),
                                    alpha=0.05, 
                                    prior_level_sd= prior_sd)

# See which hospital receives the highest weight in determining the outcome
coeff <- results$Coefficients

#Store predicted values in dataframe
pred <- results$Predictions

return(results)

}

# Evaluating the model FOR SITES
evaluating_model_sites<-function(organisation, site, data, switch_month, variable, prior_sd, model){
  
mm<-  select_matches_sites(organisation, site, data, switch_month, variable)
  
#Prospective Pseudo Power Curves -will help you evaluate if your choice of test and control markets creates a sufficient model to measure a realistic lift from a future intervention. 
power <- MarketMatching::test_fake_lift(matched_markets = mm, 
                                      test_market = site, 
                                      end_fake_post_period = (as.Date(switch_month) %m+% months(24)), 
                                      prior_level_sd = prior_sd, 
                                      steps=10,
                                      max_fake_lift=0.1)

#Plot the actuals 
a<-model$PlotActuals+
  su_theme()

# Check out the DW and MAPE of the model
b<-model$PlotPriorLevelSdAnalysis+
  su_theme()

#And plot the graph- Ideally, a curve that starts at high probability on the left side, reaches its minimum at zero lift, and then rises again symmetrically. If the curve does not reach its minimum at zero there may be systemic model bias in the post period. 
c<-power$ResultsGraph+
  su_theme()

figure<-ggarrange(a,b,c,
                  ncol=1)

}



cia_summary_plots<-function(results, title, ylab, switch_date){

# Plot out actual vs expected
a<-results$PlotActualVersusExpected+
  su_theme()+
  labs(title=title, y=ylab)+
  theme(axis.text = element_text(size=12), 
        axis.title = element_text(size=14), 
        legend.title =element_blank(),
        legend.text=element_text(size=12))+
 annotate(geom="text", x=as.Date(switch_date),  y=-Inf, vjust=-0.3, hjust=1.04, label="SBR switch", color="#ec6555")+
   geom_vline(aes(xintercept =as.Date(switch_date)),  linetype="solid", linewidth=0.6, color="#ec6555")+
  scale_color_manual(values=c("#f9bf07","#2c2825" ))+
scale_x_date(date_breaks = "1 year",date_labels = "%Y")+
  guides(colour = guide_legend(reverse=T))

# Plot pointwise effect
b<-results$PlotPointEffect+
  su_theme()+
  theme(axis.text = element_text(size=12), axis.title = element_text(size=14))+
  geom_hline(aes(yintercept =0), linetype="dotted", color="#686f73", linewidth=0.4)+
  geom_vline(aes(xintercept =as.Date(switch_date)), linetype="solid", linewidth=0.6, color="#ec6555")+
scale_x_date(date_breaks = "1 year",date_labels = "%Y")

# Plot out cumulative effect
c<-results$PlotCumulativeEffect+
  su_theme()+
    theme(axis.text = element_text(size=12), axis.title = element_text(size=14))+
  geom_hline(aes(yintercept =0), linetype="dotted", color="#686f73", linewidth=0.4)+
  geom_vline(aes(xintercept =as.Date(switch_date)), linetype="solid", linewidth=0.6, color="#ec6555")+
scale_x_date(date_breaks = "1 year",date_labels = "%Y")

figure<-ggarrange(a,b,c, ncol=1)
}



```

# Availability of indicators by site

```{r, fig.height=6, fig.width=10}


  measure<-c("Patient experience-\nfriends and family test", "Staff turnover", "Staff sickness", "Healthcare acquired infections", "Falls and fractures", "Hospital deaths", "RTT waiting times", "Bed occupancy", "Length of stay", "Emergency readmissions" )
level<-c("site", "trust", "trust", "trust", "site", "site", "trust", "trust", "site", "site")
group<-c("Patient & Staff Experience", "Patient & Staff Experience", "Patient & Staff Experience", "Health & Safety", "Health & Safety", "Health & Safety", "Productivity & Efficiency", "Productivity & Efficiency", "Productivity & Efficiency", "Productivity & Efficiency")
    start_date<-c(min(friends_and_family$month), min(staff_turnover$month), min(staff_sickness$month), min(hcai$month), min(falls_and_fractures$month), min(sus_deaths$month), min(rtt_waiting_time$month), min(bed_occupancy$month), min(length_of_stay$month), min(emergency_readmissions$month))
      end_date<-c(max(friends_and_family$month), max(staff_turnover$month), max(staff_sickness$month), max(hcai$month), max(falls_and_fractures$month), max(sus_deaths$month), max(rtt_waiting_time$month), max(bed_occupancy$month), max(length_of_stay$month), max(emergency_readmissions$month))
      

indicators<- data.frame(group, measure, level, start_date, end_date)|>
 gather(key=type, value=range, -group, -measure, -level)|>
    mutate(range=as.Date(range))|>
  mutate(measure=factor(measure, levels=c( "Staff turnover", "Staff sickness","Patient experience-\nfriends and family test", "Healthcare acquired infections", "Falls and fractures", "Hospital deaths", "Emergency readmissions","Bed occupancy",  "RTT waiting times","Length of stay")))

name<-c("Royal Liverpool", "Clatterbridge", "Papworth", "Peterborough", "Chase Farm", "Southmead", "Tunbridge Wells")
date<-c('2022-10-01', '2020-06-01', '2019-05-01', '2010-11-01', '2018-09-01', '2014-05-01', '2011-01-01' )

sites<-data.frame(name, date)|>
  mutate(date=as.Date(date))


a<-ggplot(data=(indicators|>filter(group=="Productivity & Efficiency")),aes(y=measure, x=range))+
 geom_path(lineend = "round", color="#f9bf07", linewidth=5)+
labs(title="Productivity & Efficiency", y=NULL, x=NULL)+
 su_theme()+
  theme(axis.text.y = element_text(size=12.5),
        plot.margin = unit(c(4.5,1,0,1), "lines"),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.line.x=element_blank(),
        plot.title = element_text(hjust = -0.45, colour="#5881c1"))+
 geom_vline(data=sites, aes(xintercept =date), linetype="dashed", color="#2c2825", linewidth=0.8)+
 geom_text(data=sites|>filter(name!= "Peterborough" & name!="Tunbridge Wells"), aes(x=date, y=Inf, label=name), colour="#2c2825", angle=40, hjust=0, vjust=-0.2, text=element_text(size=11.5))+
  geom_text(data=sites|>filter(name== "Peterborough"), aes(x=date, y=Inf, label=name), colour="#2c2825", angle=40, hjust=0.1, vjust=-0.4, text=element_text(size=11))+
  geom_text(data=sites|>filter(name=="Tunbridge Wells"), aes(x=date, y=Inf, label=name), colour="#2c2825", angle=40, hjust=0, vjust=0.6, text=element_text(size=11))+
scale_x_date(date_breaks = "1 year",date_labels = "%Y")+
  coord_cartesian(clip = 'off') 

b<-ggplot(data=(indicators|>filter(group=="Health & Safety")),aes(y=measure, x=range))+
 geom_path(lineend = "round", color="#f9bf07", linewidth=5)+
labs(title="Health & Safety", y=NULL, x=NULL)+
 su_theme()+
  theme(axis.text.y = element_text(size=12.5),
        plot.margin = unit(c(0,1,0,1), "lines"),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.line.x=element_blank(),
        plot.title = element_text(hjust = -0.4, colour="#5881c1"))+
 geom_vline(data=sites, aes(xintercept =date), linetype="dashed", color="#2c2825", linewidth=0.8)+
scale_x_date(date_breaks = "1 year",date_labels = "%Y")+
  coord_cartesian(clip = 'off') 

c<-ggplot(data=(indicators|>filter(group=="Patient & Staff Experience")),aes(y=measure, x=range))+
 geom_path(lineend = "round", color="#f9bf07", linewidth=5)+
labs(title="Patient & Staff Experience", y=NULL, x=NULL)+
 su_theme()+
  theme(axis.text.y = element_text(size=12.5),axis.text.x = element_text(size=11),
        plot.margin = unit(c(0,1,1,1), "lines"),
        plot.title = element_text(hjust = -0.45, colour="#5881c1"))+
 geom_vline(data=sites, aes(xintercept =date), linetype="dashed", color="#2c2825", linewidth=0.8)+
scale_x_date(date_breaks = "1 year",date_labels = "%Y",
             limits = as.Date(c('2008-04-01','2023-11-01')))+
  coord_cartesian(clip = 'off') 

figure<-ggarrange(a, b,c, ncol=1)


```

```{r}


indicator_availability_by_site<-indicators|>
  cross_join(sites)|>
  filter(type=="start_date")|>
   mutate(difference=as.numeric(date-range))|> #difference in days
  mutate(sufficient_baseline=ifelse(difference>=730, "yes", "no"))|>
  select(-difference, -date, -range, -type)|>
  pivot_wider( names_from = name, values_from=sufficient_baseline)|>
  mutate(measure=factor(measure, levels=c( "Patient experience-\nfriends and family test", "Staff sickness","Staff turnover", "Hospital deaths", "Falls and fractures", "Healthcare acquired infections","Length of stay" ,"RTT waiting times","Bed occupancy",  "Emergency readmissions"))) |>
  arrange(measure)|>
  mutate(group=factor(group, levels=c("Productivity & Efficiency", "Health & Safety","Patient & Staff Experience")))|>
  arrange(group)

 colormatrix1<-ifelse(indicator_availability_by_site=="no","#FBE0DC", 
                     ifelse(indicator_availability_by_site=="yes", "#d5eed1", "#FFFFFF"  )) |>
   as.data.frame()|>
   slice(1:4)|>
   select(-group)|>
   as.matrix()
   
    colormatrix2<-ifelse(indicator_availability_by_site=="no","#FBE0DC", 
                     ifelse(indicator_availability_by_site=="yes", "#d5eed1", "#FFFFFF"  )) |>
   as.data.frame()|>
   slice(5:7)|>
   select(-group)|>
   as.matrix()
   
   
   
    colormatrix3<-ifelse(indicator_availability_by_site=="no","#FBE0DC", 
                     ifelse(indicator_availability_by_site=="yes", "#d5eed1", "#FFFFFF"  )) |>
   as.data.frame()|>
   slice(8:10)|>
   select(-group)|>
   as.matrix()
   
#, level=c("Productivity & Efficiency","Health & Safety",  "Patient & Staff Experience")
 #    
   
  as_grouped_data(indicator_availability_by_site, groups = "group")|>
  as_flextable( hide_grouplabel = TRUE) |>
  set_header_labels(measure= "Variable",
                    level="Level")|>
  align(part = "header", align = "center")|>
    align(part = "body", align = "center")|>
      align(j=1:2,  align = "left")|>
  bg(bg = "#f9bf07", part = "header") |>
  bg(i=2:5, part="body", bg=colormatrix1)|>
      bg(i=7:9, bg=colormatrix2)|>
      bg(i=11:13, bg=colormatrix3)|>
      align(j = 1, i = ~ !is.na(group), part = "body", align="left" )|>
  bold(j = 1, i = ~ !is.na(group), part = "body" )|>
  bold(bold = TRUE, part="header")|>
   fontsize(size = 12, part = "all")|>
   padding(padding = 2, part = "all", padding.top=NULL) |>
 autofit()|>
      htmltools_value(ft.align = "left") 





```

# Productivity and Efficiency

## Waiting time data- Median waiting time (in weeks)

Seems to be some change in data reporting around 2011. Also have numbers predicted to be negative, so need to look at transforming the data first.

#### Royal Liverpool

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_median_REM<-cia_analysis("REM",  rtt_waiting_time,"2022-10-01", "median_by_prov", 0.05)

evaluating_model("REM",   rtt_waiting_time, "2022-10-01", "median_by_prov", 0.05, waiting_time_median_REM)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(waiting_time_median_REM, "Study site: Royal Liverpool, REM","Median waiting time (wks)", "2022-10-01")
```

#### Clatterbridge

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_median_REN<-cia_analysis("REN", rtt_waiting_time,"2020-06-01", "median_by_prov", 0.05)

evaluating_model("REN",  rtt_waiting_time, "2020-06-01", "median_by_prov", 0.05, waiting_time_median_REN)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(waiting_time_median_REN, "Study site: Clatterbridge, REN","Median waiting time (wks)", "2020-06-01")

test<-rtt_waiting_time|>
  filter(organisation_code=="REN")
```

#### Papworth

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_median_RGM<-cia_analysis("RGM", rtt_waiting_time,"2019-05-01", "median_by_prov", 0.05)

evaluating_model("RGM",  rtt_waiting_time, "2019-05-01", "median_by_prov", 0.05, waiting_time_median_RGM)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(waiting_time_median_RGM, "Study site: Papworth, RGM","Median waiting time (wks)", "2019-05-01")
```

#### Peterborough

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_median_RGN<-cia_analysis("RGN", rtt_waiting_time,"2010-11-01", "median_by_prov", 0.05)

evaluating_model("RGN",  rtt_waiting_time, "2010-11-01", "median_by_prov", 0.05, waiting_time_median_RGN)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(waiting_time_median_RGN, "Study site: Peterborough, RGN","Median waiting time (wks)", "2010-11-01")
```

#### Chase Farm

Missing data in 2019 and 2020

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_median_RAL<-cia_analysis("RAL", rtt_waiting_time,"2018-09-01", "median_by_prov", 0.05)

evaluating_model("RAL",  rtt_waiting_time, "2018-09-01", "median_by_prov", 0.05, waiting_time_median_RAL)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(waiting_time_median_RAL, "Study site: Chase Farm, RAL","Median waiting time (wks)", "2018-09-01")
```

#### Southmead

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_median_RVJ<-cia_analysis("RVJ", rtt_waiting_time,"2014-05-01", "median_by_prov", 0.05)

evaluating_model("RVJ",  rtt_waiting_time, "2014-05-01", "median_by_prov", 0.05, waiting_time_median_RVJ)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(waiting_time_median_RVJ, "Study site: Southmead, RVJ","Median waiting time (wks)", "2014-05-01")
```

#### Tunbridge Wells

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_median_RWF<-cia_analysis("RWF", rtt_waiting_time,"2011-01-01", "median_by_prov", 0.01)

evaluating_model("RWF",  rtt_waiting_time, "2011-01-01", "median_by_prov", 0.01, waiting_time_median_RWF)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(waiting_time_median_RWF, "Study site: Tunbridge Wells, RWF","Median waiting time (wks)", "2011-01-01")
```

## Waiting time data- Total numbers waiting

#### Royal Liverpool

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_number_REM<-cia_analysis("REM", rtt_waiting_time,"2022-10-01", "number_incomplete", 0.05)

evaluating_model("REM",  rtt_waiting_time, "2022-10-01", "number_incomplete", 0.05, waiting_time_number_REM)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(waiting_time_number_REM, "Study site: Royal Liverpool, REM","Number waiting", "2022-10-01")
```

#### Clatterbridge

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_number_REN<-cia_analysis("REN", rtt_waiting_time,"2020-06-01","number_incomplete", 0.05)

evaluating_model("REN",  rtt_waiting_time, "2020-06-01", "number_incomplete", 0.05, waiting_time_number_REN)

test<-rtt_waiting_time|>
  filter(organisation_code=="REN")

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(waiting_time_number_REN, "Study site: Clatterbridge, REN","Number waiting", "2020-06-01")
```

#### Papworth

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_number_RGM<-cia_analysis("RGM", rtt_waiting_time,"2019-05-01", "number_incomplete", 0.05)

evaluating_model("RGM",  rtt_waiting_time, "2019-05-01", "number_incomplete", 0.05, waiting_time_number_RGM)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(waiting_time_number_RGM, "Study site: Papworth, RGM","Number waiting", "2019-05-01")
```

#### Peterborough

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_number_RGN<-cia_analysis("RGN", rtt_waiting_time,"2010-11-01", "number_incomplete", 0.05)

evaluating_model("RGN",  rtt_waiting_time, "2010-11-01","number_incomplete", 0.05, waiting_time_number_RGN)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(waiting_time_number_RGN, "Study site: Peterborough, RGN","Number waiting", "2010-11-01")
```

#### Chase Farm

Missing data in 2019 and 2020

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_number_RAL<-cia_analysis("RAL", rtt_waiting_time,"2018-09-01", "number_incomplete", 0.05)

evaluating_model("RAL",  rtt_waiting_time, "2018-09-01", "number_incomplete", 0.05, waiting_time_number_RAL)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(waiting_time_number_RAL, "Study site: Chase Farm, RAL","Number waiting", "2018-09-01")
```

#### Southmead

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_number_RVJ<-cia_analysis("RVJ", rtt_waiting_time,"2014-05-01", "number_incomplete", 0.05)

evaluating_model("RVJ",  rtt_waiting_time, "2014-05-01", "number_incomplete", 0.05, waiting_time_number_RVJ)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(waiting_time_number_RVJ, "Study site: Southmead, RVJ","Number waiting", "2014-05-01")
```

#### Tunbridge Wells

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_number_RWF<-cia_analysis("RWF", rtt_waiting_time,"2011-01-01","number_incomplete", 0.01)

evaluating_model("RWF",  rtt_waiting_time, "2011-01-01", "number_incomplete", 0.01, waiting_time_number_RWF)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(waiting_time_number_RWF, "Study site: Tunbridge Wells, RWF","Number waiting", "2011-01-01")
```

## Length of stay

#### Royal Liverpool

```{r, include=FALSE, fig.width=8, fig.height=8}

LoS_REM<-cia_analysis_sites("REM", "REMRQ", length_of_stay,"2022-10-01", "avg_los", 0.05)

evaluating_model_sites("REM", "REMRQ",  length_of_stay, "2022-10-01", "avg_los", 0.05, LoS_REM)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(LoS_REM, "Study site: Royal Liverpool, REM","Average LoS (days)", "2022-10-01")
```

#### Clatterbridge

Missing data from the end of 2020

```{r, include=FALSE, fig.width=8, fig.height=8}

LoS_REN<-cia_analysis_sites("REN", "REN22",length_of_stay,"2020-06-01","avg_los", 0.05)

evaluating_model_sites("REN", "REN22", length_of_stay, "2020-06-01", "avg_los", 0.05, LoS_REN)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(LoS_REN, "Study site: Clatterbridge, REN","Average LoS (days)", "2020-06-01")


```

```{r, include=FALSE}

#Believe REN22- the Liverpool site of interest is currently the only one with inpatient facilities, but still have records REN20

length_of_stay|>
  filter(site_code=="REN22"|
         site_code=="REN20"| 
         site_code=="REN01"| 
         site_code=="REN21" )|>
  ggplot()+
  geom_line(aes(x=month, y=los, group=site_code, colour=site_code))+
  scale_y_continuous(limits=c(0,NA))

length_of_stay|>
  filter(site_code=="REN22"|
         site_code=="REN20"| 
         site_code=="REN01"| 
         site_code=="REN21")|>
  ggplot()+
  geom_line(aes(x=month, y=spells, group=site_code, colour=site_code))+
  scale_y_continuous(limits=c(0,NA))

length_of_stay|>
  filter(site_code=="REN22"|
         site_code=="REN20"| 
         site_code=="REN01"| 
         site_code=="REN21")|>
  ggplot()+
  geom_line(aes(x=month, y=avg_los, group=site_code, colour=site_code))+
  scale_y_continuous(limits=c(0,NA))


```

#### Papworth

COVID-19 spikes in the post switch period are impacting LoS.

```{r, include=FALSE, fig.width=8, fig.height=8}

LoS_RGM<-cia_analysis_sites("RGM", "RGM22",length_of_stay,"2019-05-01", "avg_los", 0.05)

evaluating_model_sites("RGM", "RGM22", length_of_stay, "2019-05-01", "avg_los", 0.05, LoS_RGM)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(LoS_RGM, "Study site: Papworth, RGM","Average LoS (days)", "2019-05-01")
```

#### Peterborough

```{r, include=FALSE, fig.width=8, fig.height=8}

LoS_RGN<-cia_analysis_sites("RGN", "RGN80",length_of_stay,"2010-11-01", "avg_los", 0.05)

evaluating_model_sites("RGN",  "RGN80", length_of_stay, "2010-11-01","avg_los", 0.05, LoS_RGN)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(LoS_RGN, "Study site: Peterborough, RGN","Average LoS (days)", "2010-11-01")
```

#### Chase Farm

Missing data in 2019 and 2020

```{r, include=FALSE, fig.width=8, fig.height=8}

LoS_RAL<-cia_analysis_sites("RAL", "RALC7", length_of_stay,"2018-09-01", "avg_los", 0.05)

evaluating_model_sites("RAL", "RALC7", length_of_stay, "2018-09-01", "avg_los", 0.05, LoS_RAL)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(LoS_RAL, "Study site: Chase Farm, RAL","Average LoS (days)", "2018-09-01")
```



```{r}
length_of_stay|>
  filter(site_code=="RALC7"|
         site_code=="RAPCF"| 
         site_code=="RVLC7"| 
         site_code=="RRP16" )|>
  ggplot()+
  geom_line(aes(x=month, y=los, group=site_code, colour=site_code))+
  scale_y_continuous(limits=c(0,NA))

length_of_stay|>
  filter(site_code=="RALC7"|
         site_code=="RAPCF"| 
         site_code=="RVLC7"| 
         site_code=="RRP16" )|>
  ggplot()+
  geom_line(aes(x=month, y=spells, group=site_code, colour=site_code))+
  scale_y_continuous(limits=c(0,NA))

length_of_stay|>
  filter(site_code=="RALC7"|
         site_code=="RAPCF"| 
         site_code=="RVLC7"| 
         site_code=="RRP16" )|>
  ggplot()+
  geom_line(aes(x=month, y=avg_los, group=site_code, colour=site_code))+
  scale_y_continuous(limits=c(0,NA))



```

<<<<<<< HEAD
>>>>>>> fb90aa3 (Add some plots)
=======
>>>>>>> 6f5ec5b (Add some plots)
#### Southmead

```{r, include=FALSE, fig.width=8, fig.height=8}

LoS_RVJ<-cia_analysis_sites("RVJ", "RVJ01",length_of_stay,"2014-05-01", "avg_los", 0.05)

evaluating_model_sites("RVJ","RVJ01",  length_of_stay, "2014-05-01", "avg_los", 0.05, LoS_RVJ)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(LoS_RVJ, "Study site: Southmead, RVJ","Average LoS (days)", "2014-05-01")
```

#### Tunbridge Wells

```{r, include=FALSE, fig.width=8, fig.height=8}

LoS_RWF<-cia_analysis_sites("RWF", "RWFTW", length_of_stay,"2011-01-01","avg_los", 0.05)

evaluating_model_sites("RWF",  "RWFTW", length_of_stay, "2011-01-01", "avg_los", 0.05, LoS_RWF)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(LoS_RWF, "Study site: Tunbridge Wells, RWF","Average LoS (days)", "2011-01-01")
```

## Emergency Readmissions

#### Royal Liverpool

```{r, include=FALSE, fig.width=8, fig.height=8}

emergency_readmissions_REM<-cia_analysis_sites("REM", "REMRQ", emergency_readmissions,"2022-10-01", "perc", 0.05)

evaluating_model_sites("REM", "REMRQ",  emergency_readmissions, "2022-10-01", "perc", 0.05, emergency_readmissions_REM)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(emergency_readmissions_REM, "Study site: Royal Liverpool, REM","% readmissions", "2022-10-01")
```

#### Clatterbridge

```{r, include=FALSE, fig.width=8, fig.height=8}

emergency_readmissions_REN<-cia_analysis_sites("REN", "REN22",emergency_readmissions, "2020-06-01","perc", 0.05)

evaluating_model_sites("REN", "REN22", emergency_readmissions, "2020-06-01","perc", 0.05, emergency_readmissions_REN)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(emergency_readmissions_REN, "Study site: Clatterbridge, REN","% readmissions", "2020-06-01")

```

```{r, include=FALSE}

emergency_readmissions|>
  filter(site_code=="REN22"|
         site_code=="REN20"| 
         site_code=="REN01"| 
         site_code=="REN21" )|>
  ggplot()+
  geom_line(aes(x=month, y=admits, group=site_code, colour=site_code))+
  scale_y_continuous(limits=c(0,NA))

emergency_readmissions|>
  filter(site_code=="REN22"|
         site_code=="REN20"| 
         site_code=="REN01"| 
         site_code=="REN21")|>
  ggplot()+
  geom_line(aes(x=month, y=readmits, group=site_code, colour=site_code))+
  scale_y_continuous(limits=c(0,NA))

emergency_readmissions|>
  filter(site_code=="REN22"|
         site_code=="REN20"| 
         site_code=="REN01"| 
         site_code=="REN21")|>
  ggplot()+
  geom_line(aes(x=month, y=perc, group=site_code, colour=site_code))+
  scale_y_continuous(limits=c(0,NA))

```

#### Papworth

```{r, include=FALSE, fig.width=8, fig.height=8}

emergency_readmissions_RGM<-cia_analysis_sites("RGM", "RGM22",emergency_readmissions,"2019-05-01", "perc", 0.05)

evaluating_model_sites("RGM", "RGM22", emergency_readmissions, "2019-05-01", "perc", 0.05, emergency_readmissions_RGM)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(emergency_readmissions_RGM, "Study site: Papworth, RGM","% readmissions", "2019-05-01")
```

#### Peterborough

```{r, include=FALSE, fig.width=8, fig.height=8}

emergency_readmissions_RGN<-cia_analysis_sites("RGN", "RGN80",emergency_readmissions,"2010-11-01", "perc", 0.05)

evaluating_model_sites("RGN",  "RGN80", emergency_readmissions, "2010-11-01","perc", 0.05, emergency_readmissions_RGN)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(emergency_readmissions_RGN, "Study site: Peterborough, RGN","% readmissions", "2010-11-01")
```

#### Chase Farm

Missing data in 2019 and 2020

```{r, include=FALSE, fig.width=8, fig.height=8}

emergency_readmissions_RAL<-cia_analysis_sites("RAL", "RALC7", emergency_readmissions,"2018-09-01", "perc", 0.05)

evaluating_model_sites("RAL", "RALC7", emergency_readmissions, "2018-09-01", "perc", 0.05, emergency_readmissions_RAL)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(emergency_readmissions_RAL, "Study site: Chase Farm, RAL","% readmissions", "2018-09-01")

pred <- emergency_readmissions_RAL$Predictions

```

#### Southmead

```{r, include=FALSE, fig.width=8, fig.height=8}

emergency_readmissions_RVJ<-cia_analysis_sites("RVJ", "RVJ01",emergency_readmissions,"2014-05-01", "perc", 0.05)

evaluating_model_sites("RVJ","RVJ01",  emergency_readmissions, "2014-05-01","perc", 0.05, emergency_readmissions_RVJ)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(emergency_readmissions_RVJ, "Study site: Southmead, RVJ","% readmissions", "2014-05-01")
```

#### Tunbridge Wells

```{r, include=FALSE, fig.width=8, fig.height=8}

emergency_readmissions_RWF<-cia_analysis_sites("RWF", "RWFTW", emergency_readmissions,"2011-01-01","perc", 0.05)

evaluating_model_sites("RWF",  "RWFTW", emergency_readmissions, "2011-01-01", "perc", 0.05, emergency_readmissions_RWF)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(emergency_readmissions_RWF, "Study site: Tunbridge Wells, RWF","% readmissions", "2011-01-01")
```

## Bed Occupancy

#### Royal Liverpool

```{r, include=FALSE, fig.width=8, fig.height=8}

bed_occupancy_REM<-cia_analysis("REM", bed_occupancy,"2022-10-01", "bed_occupancy", 0.05)

evaluating_model("REM",  bed_occupancy, "2022-10-01", "bed_occupancy", 0.05, bed_occupancy_REM)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(bed_occupancy_REM, "Study site: Royal Liverpool, REM","Percentage", "2022-10-01")
```

#### Clatterbridge

```{r, include=FALSE, fig.width=8, fig.height=8}

bed_occupancy_REN<-cia_analysis("REN", bed_occupancy,"2020-06-01", "bed_occupancy", 0.05)

evaluating_model("REN",  bed_occupancy, "2020-06-01", "bed_occupancy", 0.05, bed_occupancy_REN)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(bed_occupancy_REN, "Study site: Clatterbridge, REN","Percentage", "2020-06-01")
```

#### Papworth

Post switch period is impacted by COVID-19

```{r, include=FALSE, fig.width=8, fig.height=8}

bed_occupancy_RGM<-cia_analysis("RGM", bed_occupancy,"2019-05-01", "bed_occupancy", 0.05)

evaluating_model("RGM", bed_occupancy, "2019-05-01", "bed_occupancy", 0.05, bed_occupancy_RGM)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(bed_occupancy_RGM, "Study site: Papworth, RGM","Percentage", "2019-05-01")
```

#### Chase Farm

```{r, include=FALSE, fig.width=8, fig.height=8}

bed_occupancy_RAL<-cia_analysis("RAL", bed_occupancy,"2018-09-01", "bed_occupancy", 0.05)

evaluating_model("RAL",  bed_occupancy, "2018-09-01", "bed_occupancy", 0.05, bed_occupancy_RAL)

<<<<<<< HEAD
=======
test<-bed_occupancy|>
  filter(organisation_code)

>>>>>>> 144b813 (Updated Chase farm models)
```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(bed_occupancy_RAL, "Study site: Chase Farm, RAL","Percentage", "2018-09-01")
```

#### Southmead

```{r, include=FALSE, fig.width=8, fig.height=8}

bed_occupancy_RVJ<-cia_analysis("RVJ", bed_occupancy,"2014-05-01", "bed_occupancy", 0.05)

evaluating_model("RVJ",  bed_occupancy, "2014-05-01", "bed_occupancy", 0.05, bed_occupancy_RVJ)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(bed_occupancy_RVJ, "Study site: Southmead, RVJ","Percentage", "2014-05-01")
```

# Health and Safety

## Healthcare acquired infections

Combined rate per 10,000 beddays

#### Royal Liverpool

```{r, include=FALSE, fig.width=8, fig.height=8}

hcai_REM<-cia_analysis("REM", hcai,"2022-10-01", "combined_rate", 0.05)

evaluating_model("REM",  hcai, "2022-10-01", "combined_rate", 0.05, hcai_REM)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(hcai_REM, "Study site: Royal Liverpool, REM","Rate/10,000 beddays", "2022-10-01")
```

#### Clatterbridge

```{r, include=FALSE, fig.width=8, fig.height=8}

hcai_REN<-cia_analysis("REN",hcai,"2020-06-01", "combined_rate", 0.05)

evaluating_model("REN",  hcai, "2020-06-01", "combined_rate", 0.05, hcai_REN)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(hcai_REN, "Study site: Clatterbridge, REN","Rate/10,000 beddays", "2020-06-01")
```

## Falls and Fractures in hospital

#### Royal Liverpool

```{r, include=FALSE, fig.width=8, fig.height=8}

falls_and_fractures_REM<-cia_analysis_sites("REM", "REMRQ", falls_and_fractures,"2022-10-01", "ff_rate", 0.05)

evaluating_model_sites("REM", "REMRQ",  falls_and_fractures, "2022-10-01", "ff_rate", 0.05, falls_and_fractures_REM)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(falls_and_fractures_REM, "Study site: Royal Liverpool, REM","% of spells", "2022-10-01")
```

#### Clatterbridge

```{r, include=FALSE, fig.width=8, fig.height=8}

falls_and_fractures_REN<-cia_analysis_sites("REN", "REN22",falls_and_fractures, "2020-06-01","ff_rate", 0.05)

evaluating_model_sites("REN", "REN22", falls_and_fractures, "2020-06-01","ff_rate", 0.05, falls_and_fractures_REN)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(falls_and_fractures_REN, "Study site: Clatterbridge, REN","% of spells", "2020-06-01")

test<-falls_and_fractures|>
  filter(site_code=="REN22")
```

#### Papworth

```{r, include=FALSE, fig.width=8, fig.height=8}

falls_and_fractures_RGM<-cia_analysis_sites("RGM", "RGM22",falls_and_fractures,"2019-05-01", "ff_rate", 0.05)

evaluating_model_sites("RGM", "RGM22", falls_and_fractures, "2019-05-01", "ff_rate", 0.05, falls_and_fractures_RGM)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(falls_and_fractures_RGM, "Study site: Papworth, RGM","% of spells", "2019-05-01")
```

#### Peterborough

```{r, include=FALSE, fig.width=8, fig.height=8}

falls_and_fractures_RGN<-cia_analysis_sites("RGN", "RGN80",falls_and_fractures,"2010-11-01", "ff_rate", 0.05)

evaluating_model_sites("RGN",  "RGN80",falls_and_fractures, "2010-11-01","ff_rate", 0.05, falls_and_fractures_RGN)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(falls_and_fractures_RGN, "Study site: Peterborough, RGN","% of spells", "2010-11-01")
```

#### Chase Farm

```{r, include=FALSE, fig.width=8, fig.height=8}

falls_and_fractures_RAL<-cia_analysis_sites("RAL", "RALC7", falls_and_fractures,"2018-09-01", "ff_rate", 0.05)

evaluating_model_sites("RAL", "RALC7", falls_and_fractures, "2018-09-01", "ff_rate", 0.05, falls_and_fractures_RAL)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(falls_and_fractures_RAL, "Study site: Chase Farm, RAL","% of spells", "2018-09-01")
```

#### Southmead

```{r, include=FALSE, fig.width=8, fig.height=8}

falls_and_fractures_RVJ<-cia_analysis_sites("RVJ", "RVJ01",falls_and_fractures,"2014-05-01", "ff_rate", 0.05)

evaluating_model_sites("RVJ","RVJ01",  falls_and_fractures, "2014-05-01","ff_rate", 0.05, falls_and_fractures_RVJ)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(falls_and_fractures_RVJ, "Study site: Southmead, RVJ","% of spells", "2014-05-01")
```

#### Tunbridge Wells

```{r, include=FALSE, fig.width=8, fig.height=8}

falls_and_fractures_RWF<-cia_analysis_sites("RWF", "RWFTW", falls_and_fractures,"2011-01-01","ff_rate", 0.05)

evaluating_model_sites("RWF",  "RWFTW", falls_and_fractures, "2011-01-01", "ff_rate", 0.05, falls_and_fractures_RWF)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(falls_and_fractures_RWF, "Study site: Tunbridge Wells, RWF","% of spells", "2011-01-01")
```

## Deaths in hospital

#### Royal Liverpool

```{r, include=FALSE, fig.width=8, fig.height=8}

sus_deaths_REM<-cia_analysis_sites("REM", "REMRQ", sus_deaths,"2022-10-01", "hosp_rate_1000", 0.05)

evaluating_model_sites("REM", "REMRQ",  sus_deaths, "2022-10-01", "hosp_rate_1000", 0.05, sus_deaths_REM)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(sus_deaths_REM, "Study site: Royal Liverpool, REM","No./per 1,000 discharges", "2022-10-01")
```

#### Clatterbridge

```{r, include=FALSE, fig.width=8, fig.height=8}

sus_deaths_REN<-cia_analysis_sites("REN", "REN22",sus_deaths, "2020-06-01","hosp_rate_1000", 0.05)

evaluating_model_sites("REN", "REN22", sus_deaths, "2020-06-01","hosp_rate_1000", 0.05, sus_deaths_REN)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(sus_deaths_REN, "Study site: Clatterbridge, REN","No./per 1,000 discharges", "2020-06-01")

```

```{r, include=FALSE}

sus_deaths|>
  filter(site_code=="REN22"|
         site_code=="REN20"| 
         site_code=="REN01"| 
         site_code=="REN21" )|>
  ggplot()+
  geom_line(aes(x=month, y=discharges, group=site_code, colour=site_code))+
  scale_y_continuous(limits=c(0,NA))

sus_deaths|>
  filter(site_code=="REN22"|
         site_code=="REN20"| 
         site_code=="REN01"| 
         site_code=="REN21")|>
  ggplot()+
  geom_line(aes(x=month, y=death_hosp, group=site_code, colour=site_code))+
  scale_y_continuous(limits=c(0,NA))

sus_deaths|>
  filter(site_code=="REN22"|
         site_code=="REN20"| 
         site_code=="REN01"| 
         site_code=="REN21")|>
  ggplot()+
  geom_line(aes(x=month, y=hosp_rate_1000, group=site_code, colour=site_code))+
  scale_y_continuous(limits=c(0,NA))

```

#### Papworth

```{r, include=FALSE, fig.width=8, fig.height=8}

sus_deaths_RGM<-cia_analysis_sites("RGM", "RGM22",sus_deaths,"2019-05-01", "hosp_rate_1000", 0.05)

evaluating_model_sites("RGM", "RGM22", sus_deaths, "2019-05-01", "hosp_rate_1000", 0.05, sus_deaths_RGM)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(sus_deaths_RGM, "Study site: Papworth, RGM","No./per 1,000 discharges", "2019-05-01")
```

#### Peterborough

```{r, include=FALSE, fig.width=8, fig.height=8}

sus_deaths_RGN<-cia_analysis_sites("RGN", "RGN80",sus_deaths,"2010-11-01", "hosp_rate_1000", 0.05)

evaluating_model_sites("RGN",  "RGN80", sus_deaths, "2010-11-01","hosp_rate_1000", 0.05, sus_deaths_RGN)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(sus_deaths_RGN, "Study site: Peterborough, RGN","No./per 1,000 discharges", "2010-11-01")
```

#### Chase Farm

Missing data in 2019 and 2020

```{r, include=FALSE, fig.width=8, fig.height=8}

sus_deaths_RAL<-cia_analysis_sites("RAL", "RALC7", sus_deaths,"2018-09-01", "hosp_rate_1000", 0.05)

evaluating_model_sites("RAL", "RALC7", sus_deaths, "2018-09-01","hosp_rate_1000", 0.05, sus_deaths_RAL)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(sus_deaths_RAL, "Study site: Chase Farm, RAL","No./per 1,000 discharges", "2018-09-01")
```

```{r}

sus_deaths|>
  filter(site_code=="RALC7"|
         site_code=="RAPCF"| 
         site_code=="RVLC7"| 
         site_code=="RRP16" )|>
  ggplot()+
  geom_line(aes(x=month, y=discharges, group=site_code, colour=site_code))+
  scale_y_continuous(limits=c(0,NA))

sus_deaths|>
  filter(site_code=="RALC7"|
         site_code=="RAPCF"| 
         site_code=="RVLC7"| 
         site_code=="RRP16" )|>
  ggplot()+
  geom_line(aes(x=month, y=death_hosp, group=site_code, colour=site_code))+
  scale_y_continuous(limits=c(0,NA))

sus_deaths|>
  filter(site_code=="RALC7"|
         site_code=="RAPCF"| 
         site_code=="RVLC7"| 
         site_code=="RRP16" )|>
  ggplot()+
  geom_line(aes(x=month, y=hosp_rate_1000, group=site_code, colour=site_code))+
  scale_y_continuous(limits=c(0,NA))

```

#### Southmead

```{r, include=FALSE, fig.width=8, fig.height=8}

sus_deaths_RVJ<-cia_analysis_sites("RVJ", "RVJ01",sus_deaths,"2014-05-01", "hosp_rate_1000", 0.05)

evaluating_model_sites("RVJ","RVJ01",  sus_deaths, "2014-05-01","hosp_rate_1000", 0.05, sus_deaths_RVJ)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(sus_deaths_RVJ, "Study site: Southmead, RVJ","No./per 1,000 discharges", "2014-05-01")
```

#### Tunbridge Wells

```{r, include=FALSE, fig.width=8, fig.height=8}

sus_deaths_RWF<-cia_analysis_sites("RWF", "RWFTW", sus_deaths,"2011-01-01","hosp_rate_1000", 0.05)

evaluating_model_sites("RWF",  "RWFTW", sus_deaths, "2011-01-01", "hosp_rate_1000", 0.05, sus_deaths_RWF)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(sus_deaths_RWF, "Study site: Tunbridge Wells, RWF","No./per 1,000 discharges", "2011-01-01")
```

# Patient and Staff Experience

## Patient experience - Friends and Family scores

#### Royal Liverpool (REMRQ)

```{r, include=FALSE, fig.height=8, fig.width=8}

friends_and_family_REMRQ<-cia_analysis_sites("REM","REMRQ",  friends_and_family,"2022-10-01", "friends_and_family_percent", 0.05)

evaluating_model_sites("REM","REMRQ", friends_and_family,"2022-10-01", "friends_and_family_percent", 0.05, friends_and_family_REMRQ)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(friends_and_family_REMRQ, "Study site: Royal Liverpool, REMRQ","Positive responses (%)", "2022-10-01")

test<-friends_and_family|>
  filter(site_code=="REMRQ")

pred<-friends_and_family_REMRQ$Predictions

# Large amount of data missing in the two years prior due to gap over covid. One of the control sites doesn't go back far enough for it is causing the data to be cut off. Think I need to have less matches for this one. But would still have a disturbed pre switch period due to COVID

```

#### Clatterbridge (REN)

```{r, include=FALSE, fig.width=8, fig.height=8}


friends_and_family_REN22<-cia_analysis_sites("REN", "REN22",friends_and_family,"2020-06-01", "friends_and_family_percent", 0.05)

evaluating_model_sites("REN","REN22", friends_and_family,"2020-06-01", "friends_and_family_percent", 0.05,friends_and_family_REN22 )

test<-friends_and_family|>
  filter(site_code=="REN22")

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(friends_and_family_REN22, "Study site: Clatterbridge, REN22","Positive responses (%)", "2020-06-01")

test<-friends_and_family|>
  filter(site_code=="REN22")

#Last data point prior to switch was about 4 months prior then no data for 8 months after, as switch came during COVID

```

#### Papworth (RGM)

```{r, include=TRUE, fig.width=8, fig.height=8}

friends_and_family_RGM22<-cia_analysis_sites("RGM", "RGM22", friends_and_family,"2019-05-01", "friends_and_family_percent", 0.05)

evaluating_model_sites("RGM", "RGM22", friends_and_family,"2019-05-01", "friends_and_family_percent", 0.05, friends_and_family_RGM22)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(friends_and_family_RGM22, "Study site: Papworth, RGM22","Positive responses (%)", "2019-05-01")
```

#### Chase Farm Hospital (RAL)

```{r, include=FALSE, fig.width=8, fig.height=8}

friends_and_family_RALC7<-cia_analysis_sites("RAL", "RALC7", friends_and_family,"2018-09-01", "friends_and_family_percent", 0.05)


evaluating_model_sites("RAL","RALC7",  friends_and_family,"2018-09-01", "friends_and_family_percent", 0.05, friends_and_family_RALC7)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(friends_and_family_RALC7, "Study site: Chase Farm Hospital, RALC7","Positive responses (%)", "2018-09-01")
```

## Staff sickness

#### Royal Liverpool (REM)

```{r, include=FALSE, fig.height=8, fig.width=8}

staff_sickness_REM<-cia_analysis("REM",  staff_sickness,"2022-10-01", "staff_sickness_percent", 0.05)


evaluating_model("REM", staff_sickness,"2022-10-01", "staff_sickness_percent", 0.05, staff_sickness_REM)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(staff_sickness_REM, "Study site: Royal Liverpool, REM","Sickness Rate (%)", "2022-10-01")

```

#### Clatterbridge (REN)

```{r, include=FALSE, fig.width=8, fig.height=8}

staff_sickness_REN<-cia_analysis("REN", staff_sickness,"2020-06-01", "staff_sickness_percent", 0.05)

evaluating_model("REN", staff_sickness,"2020-06-01", "staff_sickness_percent", 0.05,staff_sickness_REN )

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(staff_sickness_REN, "Study site: Clatterbridge, REN","Sickness Rate (%)", "2020-06-01")

```

#### Papworth (RGM)

```{r, include=FALSE, fig.width=8, fig.height=8}

staff_sickness_RGM<-cia_analysis("RGM", staff_sickness,"2019-05-01", "staff_sickness_percent", 0.05)

evaluating_model("RGM", staff_sickness,"2019-05-01", "staff_sickness_percent", 0.05, staff_sickness_RGM)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(staff_sickness_RGM, "Study site: Papworth, RGM","Sickness Rate (%)", "2019-05-01")
```

#### Chase Farm Hospital (RAL)

```{r, include=FALSE, fig.width=8, fig.height=8}

staff_sickness_RAL<-cia_analysis("RAL", staff_sickness,"2018-09-01", "staff_sickness_percent", 0.05)


evaluating_model("RAL", staff_sickness,"2018-09-01", "staff_sickness_percent", 0.05, staff_sickness_RAL)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(staff_sickness_RAL, "Study site: Chase Farm Hospital, RAL","Sickness Rate (%)", "2018-09-01")
```

#### Southmead (RVJ)

```{r, include=FALSE, fig.width=8, fig.height=8}

staff_sickness_RVJ<-cia_analysis("RVJ", staff_sickness,"2014-05-01", "staff_sickness_percent", 0.05)

evaluating_model("RVJ", staff_sickness,"2014-05-01", "staff_sickness_percent", 0.05, staff_sickness_RVJ)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(staff_sickness_RVJ, "Study site: Southmead, RVJ","Sickness Rate (%)", "2014-05-01")
```

```{r, fig.height=8, fig.width=8}

## Staff turnover

#### Royal Liverpool (REM)

staff_turnover_REM<-cia_analysis("REM",  staff_turnover,"2022-10-01", "leaving_rate", 0.05)


evaluating_model("REM", staff_turnover,"2022-10-01", "leaving_rate", 0.05, staff_turnover_REM)

test<-staff_turnover|>
  filter(organisation_code=="REM")
# denominator appears to remain constant but for 12 months between Sept 2019 to Aug 2020, the numbers of leavers and joiners recorded is approx. 6 times higher than usual.

cia_summary_plots(staff_turnover_REM, "Study site: Royal Liverpool, REM","Leaving Rate (%)", "2022-10-01")


```



```{r, include=FALSE}
# Other plots information

## Cleaning staff



#cleaning_staff<-tar_read(eric_udal)|>
#  filter(measure=="Cleaning staff (WTE)")|>
#  filter(level=="Site")|>
#  mutate(month=floor_date(effective_snapshot_date, "month"))|> #Format date to monthly
#  left_join(beddays[,c("der_provider_site_code", "beddays", "yearmon")], #by=c("site_code"="der_provider_site_code", "month"="yearmon")) |>
#  merge_sites()|>
#  group_by(month, site_code)|>
#  summarise(value=sum(value), beddays=sum(beddays))|>
#  mutate(rate=(value/beddays)*1000) #WTE per 1000 beddays

```

```{r, include=FALSE}
## C. Difficile rate over time

#c.diff only as this goes back before 2017/2018
#tar_read(formatted_HCAI_data)|>
#  left_join(beddays_by_prov[,c("organisation_code", "yearmon", "beddays")], by=c("organisation_code", "month"="yearmon"))|>
#  mutate(rate=(count_of_cases/beddays)*10000)|> #cases per 10,000 beddays
#filter(collection=="C.difficile")|>
#  filter(organisation_code=="REM")|> #for Royal Liverpool
#    ggplot(aes(x = month, y =rate) ) + 
#   geom_line(linewidth=1) 


# C. Difficile numbers are too small to use in CIA as so much variability.

```
