---
title: "Causal Impact Analysis: Productivity and Efficiency indicators"
editor: visual
execute:
  echo: false
  message: false
  warning: false
  cache: false
lang: en-GB
author: Sarah Lucas
date: last-modified
date-format: "YYYY-MM-DD"
title-block-banner: "#f9bf07"
title-block-banner-color: "#333739"
format:
  html:
    embed-resources: true
    smooth-scroll: true
    theme: cosmo
    fontcolor: black
    toc: true
    toc-location: left
    toc-title: Summary
    toc-depth: 3
    grid:
      sidebar-width: 250px
      body-width: 1050px
      margin-width: 0px
      gutter-width: 1.5rem
css: styles.css
---

```{r, include=FALSE}

library(tidyverse)
library(MarketMatching)
library(tsibble)
library(targets)
library(janitor)
library(readxl)
library(zoo)
library(lubridate)
library(ggrepel)
library(flextable)
library(egg)
library(StrategyUnitTheme)


## RTT waiting time
rtt_waiting_time<-tar_read(rtt_waiting_time_cia_format) |>
  filter( organisation_code!="RF4" &  
        organisation_code!="R1H" &
         organisation_code!= "RJ2") #Removing poss control due to data issues

## Bed occupancy
bed_occupancy<-tar_read(bed_occupancy_cia_format)|>
  mutate(bed_occupancy=bed_occupancy*100)|>
  filter(organisation_code!="R0A" & organisation_code!="RNL") #remove controls for Chase Farm

## Length of Stay
length_of_stay<- tar_read(length_of_stay_cia_format)

## Emergency readmissions
emergency_readmissions<-tar_read(emergency_readmissions_cia_format)|>
  filter(site_code!="RXPCP" &
         site_code!="RVY01" &
         site_code!="RDEEB"&
         site_code!="RPA02")


#Loading control data
single_bedroom_matches<-tar_read(single_bedroom_matches)

source("R/CIA_Functions.R")


```

# Availability of indicators by site

```{r, fig.height=6, fig.width=10}

tar_read(indicator_availability_plot)

```

```{r}

tar_read(indicator_availability_table)

```

# Productivity and Efficiency

## Waiting time data- Median waiting time (in weeks)

Seems to be some change in data reporting around 2011. Also have numbers predicted to be negative, so need to look at transforming the data first.

#### Royal Liverpool

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_median_REM<-cia_analysis("REM", NA, rtt_waiting_time,"2022-10-01", "median_by_prov", 0.05)

#evaluating_model("REM", NA,  rtt_waiting_time, "2022-10-01", "median_by_prov", 0.05)

```

```{r, include=TRUE, fig.width=6, fig.height=6}

cia_summary_plots(waiting_time_median_REM, "Study site: Royal Liverpool, REM","Median waiting time (wks)", "2022-10-01")
```

#### Clatterbridge

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_median_REN<-cia_analysis("REN",NA, rtt_waiting_time,"2020-06-01", "median_by_prov", 0.05)

evaluating_model("REN", NA, rtt_waiting_time, "2020-06-01", "median_by_prov", 0.05, waiting_time_median_REN)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(waiting_time_median_REN, "Study site: Clatterbridge, REN","Median waiting time (wks)", "2020-06-01")

```

#### Papworth

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_median_RGM<-cia_analysis("RGM", NA, rtt_waiting_time,"2019-05-01", "median_by_prov", 0.05)

#evaluating_model("RGM", NA, rtt_waiting_time, "2019-05-01", "median_by_prov", 0.05, waiting_time_median_RGM)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(waiting_time_median_RGM, "Study site: Papworth, RGM","Median waiting time (wks)", "2019-05-01")
```

#### Peterborough

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_median_RGN<-cia_analysis("RGN", NA,rtt_waiting_time,"2010-11-01", "median_by_prov", 0.05)

#evaluating_model("RGN", NA, rtt_waiting_time, "2010-11-01", "median_by_prov", 0.05, waiting_time_median_RGN)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(waiting_time_median_RGN, "Study site: Peterborough, RGN","Median waiting time (wks)", "2010-11-01")
```

#### Chase Farm

Missing data in 2019 and 2020

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_median_RAL<-cia_analysis("RAL", NA,rtt_waiting_time,"2018-09-01", "median_by_prov", 0.05)

#evaluating_model("RAL", NA, rtt_waiting_time, "2018-09-01", "median_by_prov", 0.05, waiting_time_median_RAL)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(waiting_time_median_RAL, "Study site: Chase Farm, RAL","Median waiting time (wks)", "2018-09-01")
```

#### Southmead

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_median_RVJ<-cia_analysis("RVJ",NA, rtt_waiting_time,"2014-05-01", "median_by_prov", 0.05)

#evaluating_model("RVJ",NA,  rtt_waiting_time, "2014-05-01", "median_by_prov", 0.05, waiting_time_median_RVJ)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(waiting_time_median_RVJ, "Study site: Southmead, RVJ","Median waiting time (wks)", "2014-05-01")
```

#### Tunbridge Wells

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_median_RWF<-cia_analysis("RWF", NA,rtt_waiting_time,"2011-01-01", "median_by_prov", 0.01)

#evaluating_model("RWF", NA, rtt_waiting_time, "2011-01-01", "median_by_prov", 0.01, waiting_time_median_RWF)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(waiting_time_median_RWF, "Study site: Tunbridge Wells, RWF","Median waiting time (wks)", "2011-01-01")
```

## Waiting time data- Total numbers waiting

#### Royal Liverpool

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_number_REM<-cia_analysis("REM", NA,rtt_waiting_time,"2022-10-01", "number_incomplete", 0.05)

#evaluating_model("REM", NA, rtt_waiting_time, "2022-10-01", "number_incomplete", 0.05, waiting_time_number_REM)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(waiting_time_number_REM, "Study site: Royal Liverpool, REM","Number waiting", "2022-10-01")
```

#### Clatterbridge

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_number_REN<-cia_analysis("REN", NA,rtt_waiting_time,"2020-06-01","number_incomplete", 0.05)

#evaluating_model("REN", NA, rtt_waiting_time, "2020-06-01", "number_incomplete", 0.05, waiting_time_number_REN)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(waiting_time_number_REN, "Study site: Clatterbridge, REN","Number waiting", "2020-06-01")
```

#### Papworth

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_number_RGM<-cia_analysis("RGM",NA, rtt_waiting_time,"2019-05-01", "number_incomplete", 0.05)

#evaluating_model("RGM", NA, rtt_waiting_time, "2019-05-01", "number_incomplete", 0.05, waiting_time_number_RGM)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(waiting_time_number_RGM, "Study site: Papworth, RGM","Number waiting", "2019-05-01")
```

#### Peterborough

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_number_RGN<-cia_analysis("RGN",NA, rtt_waiting_time,"2010-11-01", "number_incomplete", 0.05)

#evaluating_model("RGN", NA, rtt_waiting_time, "2010-11-01","number_incomplete", 0.05, waiting_time_number_RGN)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(waiting_time_number_RGN, "Study site: Peterborough, RGN","Number waiting", "2010-11-01")
```

#### Chase Farm

Missing data in 2019 and 2020

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_number_RAL<-cia_analysis("RAL", NA,rtt_waiting_time,"2018-09-01", "number_incomplete", 0.05)

#evaluating_model("RAL", NA, rtt_waiting_time, "2018-09-01", "number_incomplete", 0.05, waiting_time_number_RAL)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(waiting_time_number_RAL, "Study site: Chase Farm, RAL","Number waiting", "2018-09-01")
```

#### Southmead

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_number_RVJ<-cia_analysis("RVJ", NA,rtt_waiting_time,"2014-05-01", "number_incomplete", 0.05)

#evaluating_model("RVJ", NA, rtt_waiting_time, "2014-05-01", "number_incomplete", 0.05, waiting_time_number_RVJ)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(waiting_time_number_RVJ, "Study site: Southmead, RVJ","Number waiting", "2014-05-01")
```

#### Tunbridge Wells

```{r, include=FALSE, fig.width=8, fig.height=8}

waiting_time_number_RWF<-cia_analysis("RWF",NA, rtt_waiting_time,"2011-01-01","number_incomplete", 0.01)

#evaluating_model("RWF", NA, rtt_waiting_time, "2011-01-01", "number_incomplete", 0.01, waiting_time_number_RWF)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(waiting_time_number_RWF, "Study site: Tunbridge Wells, RWF","Number waiting", "2011-01-01")
```

## Length of stay

#### Royal Liverpool

```{r, include=FALSE, fig.width=8, fig.height=8}

LoS_REM<-cia_analysis("REM", "REMRQ", length_of_stay,"2022-10-01", "avg_los", 0.05,single_bedroom_matches )

#evaluating_model_sites("REM", "REMRQ",  length_of_stay, "2022-10-01", "avg_los", 0.05, LoS_REM)
test<-select_matches("REM","REMRQ", length_of_stay,"2022-10-01", "avg_los", single_bedroom_matches)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(LoS_REM, "Study site: Royal Liverpool, REM","Average LoS (days)", "2022-10-01")
```

#### Clatterbridge

```{r, include=FALSE, fig.width=8, fig.height=8}

LoS_REN<-cia_analysis("REN", "REN22",length_of_stay,"2020-06-01","avg_los", 0.05)

#evaluating_model_sites("REN", "REN22", length_of_stay, "2020-06-01", "avg_los", 0.05, LoS_REN)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(LoS_REN, "Study site: Clatterbridge, REN","Average LoS (days)", "2020-06-01")


```

#### Papworth

COVID-19 spikes in the post switch period are impacting LoS.

```{r, include=FALSE, fig.width=8, fig.height=8}

LoS_RGM<-cia_analysis("RGM", "RGM22",length_of_stay,"2019-05-01", "avg_los", 0.05)

#evaluating_model_sites("RGM", "RGM22", length_of_stay, "2019-05-01", "avg_los", 0.05, LoS_RGM)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(LoS_RGM, "Study site: Papworth, RGM","Average LoS (days)", "2019-05-01")
```

#### Peterborough

```{r, include=FALSE, fig.width=8, fig.height=8}

LoS_RGN<-cia_analysis("RGN", "RGN80",length_of_stay,"2010-11-01", "avg_los", 0.05)

#evaluating_model_sites("RGN",  "RGN80", length_of_stay, "2010-11-01","avg_los", 0.05, LoS_RGN)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(LoS_RGN, "Study site: Peterborough, RGN","Average LoS (days)", "2010-11-01")
```

#### Chase Farm

Missing data in 2019 and 2020

```{r, include=FALSE, fig.width=8, fig.height=8}

LoS_RAL<-cia_analysis("RAL", "RALC7", length_of_stay,"2018-09-01", "avg_los", 0.05)

#evaluating_model_sites("RAL", "RALC7", length_of_stay, "2018-09-01", "avg_los", 0.05, LoS_RAL)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(LoS_RAL, "Study site: Chase Farm, RAL","Average LoS (days)", "2018-09-01")
```

#### Southmead

```{r, include=FALSE, fig.width=8, fig.height=8}

LoS_RVJ<-cia_analysis("RVJ", "RVJ01",length_of_stay,"2014-05-01", "avg_los", 0.05)

#evaluating_model_sites("RVJ","RVJ01",  length_of_stay, "2014-05-01", "avg_los", 0.05, LoS_RVJ)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(LoS_RVJ, "Study site: Southmead, RVJ","Average LoS (days)", "2014-05-01")
```

#### Tunbridge Wells

```{r, include=FALSE, fig.width=8, fig.height=8}

LoS_RWF<-cia_analysis("RWF", "RWFTW", length_of_stay,"2011-01-01","avg_los", 0.05)

#evaluating_model_sites("RWF",  "RWFTW", length_of_stay, "2011-01-01", "avg_los", 0.05, LoS_RWF)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(LoS_RWF, "Study site: Tunbridge Wells, RWF","Average LoS (days)", "2011-01-01")
```

## Emergency Readmissions

#### Royal Liverpool

```{r, include=FALSE, fig.width=8, fig.height=8}

emergency_readmissions_REM<-cia_analysis("REM", "REMRQ", emergency_readmissions,"2022-10-01", "perc", 0.05)

#evaluating_model_sites("REM", "REMRQ",  emergency_readmissions, "2022-10-01", "perc", 0.05, emergency_readmissions_REM)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(emergency_readmissions_REM, "Study site: Royal Liverpool, REM","% readmissions", "2022-10-01")
```

#### Clatterbridge

```{r, include=FALSE, fig.width=8, fig.height=8}

emergency_readmissions_REN<-cia_analysis("REN", "REN22",emergency_readmissions, "2020-06-01","perc", 0.05)

#evaluating_model_sites("REN", "REN22", emergency_readmissions, "2020-06-01","perc", 0.05, emergency_readmissions_REN)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(emergency_readmissions_REN, "Study site: Clatterbridge, REN","% readmissions", "2020-06-01")

```

#### Papworth

```{r, include=FALSE, fig.width=8, fig.height=8}

emergency_readmissions_RGM<-cia_analysis("RGM", "RGM22",emergency_readmissions,"2019-05-01", "perc", 0.05)

#evaluating_model_sites("RGM", "RGM22", emergency_readmissions, "2019-05-01", "perc", 0.05, emergency_readmissions_RGM)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(emergency_readmissions_RGM, "Study site: Papworth, RGM","% readmissions", "2019-05-01")
```

#### Peterborough

```{r, include=FALSE, fig.width=8, fig.height=8}

emergency_readmissions_RGN<-cia_analysis("RGN", "RGN80",emergency_readmissions,"2010-11-01", "perc", 0.05)

#evaluating_model_sites("RGN",  "RGN80", emergency_readmissions, "2010-11-01","perc", 0.05, emergency_readmissions_RGN)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(emergency_readmissions_RGN, "Study site: Peterborough, RGN","% readmissions", "2010-11-01")
```

#### Chase Farm

Missing data in 2019 and 2020

```{r, include=FALSE, fig.width=8, fig.height=8}

emergency_readmissions_RAL<-cia_analysis("RAL", "RALC7", emergency_readmissions,"2018-09-01", "perc", 0.05)

#evaluating_model_sites("RAL", "RALC7", emergency_readmissions, "2018-09-01", "perc", 0.05, emergency_readmissions_RAL)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(emergency_readmissions_RAL, "Study site: Chase Farm, RAL","% readmissions", "2018-09-01")

pred <- emergency_readmissions_RAL$Predictions

```

#### Southmead

```{r, include=FALSE, fig.width=8, fig.height=8}

emergency_readmissions_RVJ<-cia_analysis("RVJ", "RVJ01",emergency_readmissions,"2014-05-01", "perc", 0.05)

#evaluating_model_sites("RVJ","RVJ01",  emergency_readmissions, "2014-05-01","perc", 0.05, emergency_readmissions_RVJ)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(emergency_readmissions_RVJ, "Study site: Southmead, RVJ","% readmissions", "2014-05-01")
```

#### Tunbridge Wells

```{r, include=FALSE, fig.width=8, fig.height=8}

emergency_readmissions_RWF<-cia_analysis("RWF", "RWFTW", emergency_readmissions,"2011-01-01","perc", 0.05)

#evaluating_model_sites("RWF",  "RWFTW", emergency_readmissions, "2011-01-01", "perc", 0.05, emergency_readmissions_RWF)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(emergency_readmissions_RWF, "Study site: Tunbridge Wells, RWF","% readmissions", "2011-01-01")
```

## Bed Occupancy

#### Royal Liverpool

```{r, include=FALSE, fig.width=8, fig.height=8}

bed_occupancy_REM<-cia_analysis("REM", NA,bed_occupancy,"2022-10-01", "bed_occupancy", 0.05)

#evaluating_model("REM", NA, bed_occupancy, "2022-10-01", "bed_occupancy", 0.05, bed_occupancy_REM)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(bed_occupancy_REM, "Study site: Royal Liverpool, REM","Percentage", "2022-10-01")
```

#### Clatterbridge

```{r, include=FALSE, fig.width=8, fig.height=8}

bed_occupancy_REN<-cia_analysis("REN",NA, bed_occupancy,"2020-06-01", "bed_occupancy", 0.05)

#evaluating_model("REN", NA, bed_occupancy, "2020-06-01", "bed_occupancy", 0.05, bed_occupancy_REN)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(bed_occupancy_REN, "Study site: Clatterbridge, REN","Percentage", "2020-06-01")
```

#### Papworth

Post switch period is impacted by COVID-19

```{r, include=FALSE, fig.width=8, fig.height=8}

bed_occupancy_RGM<-cia_analysis("RGM",NA, bed_occupancy,"2019-05-01", "bed_occupancy", 0.05)

#evaluating_model("RGM",NA, bed_occupancy, "2019-05-01", "bed_occupancy", 0.05, bed_occupancy_RGM)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(bed_occupancy_RGM, "Study site: Papworth, RGM","Percentage", "2019-05-01")
```

#### Chase Farm

```{r, include=FALSE, fig.width=8, fig.height=8}

bed_occupancy_RAL<-cia_analysis("RAL",NA, bed_occupancy,"2018-09-01", "bed_occupancy", 0.05)

#evaluating_model("RAL",NA,  bed_occupancy, "2018-09-01", "bed_occupancy", 0.05, bed_occupancy_RAL)

```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(bed_occupancy_RAL, "Study site: Chase Farm, RAL","Percentage", "2018-09-01")
```

#### Southmead

```{r, include=FALSE, fig.width=8, fig.height=8}

bed_occupancy_RVJ<-cia_analysis("RVJ",NA, bed_occupancy,"2014-05-01", "bed_occupancy", 0.05)

#evaluating_model("RVJ", NA, bed_occupancy, "2014-05-01", "bed_occupancy", 0.05, bed_occupancy_RVJ)


```

```{r, include=TRUE, fig.width=8, fig.height=8}

cia_summary_plots(bed_occupancy_RVJ, "Study site: Southmead, RVJ","Percentage", "2014-05-01")
```
