---
title: "Causal Impact Analysis"
format: html
editor: visual
---

REMRQ - Royal Liverpool

REM21 - Aintree University

RBN01 - Whiston

REMBG - Warrington

RVY01 - Southport & Formby

RVY02 - Ormskirk & District

RJR05 - Countess of Chester

# Extra data wrangling


```{r}
library(tidyverse)
library(MarketMatching)
library(tsibble)
library(targets)
library(janitor)
library(readxl)
library(zoo)
library(lubridate)

 


#Functions 
merge_sites<-function(data){
 data|>
  mutate(site_code=ifelse((site_code=="REMRQ"|site_code=="RQ617"), "REMRQ", site_code))|> #merge historical Royal Liverpool codes
    mutate(site_code=ifelse((site_code=="RGM22"|site_code=="RGM21"), "RGM22", site_code))|> #merge Papworth site codes
     mutate(site_code=ifelse((site_code=="RVJ01"|site_code=="RVJ20"), "RVJ01", site_code))|> #merge Southmead site codes
   mutate(site_code=ifelse((site_code=="RGN80"|site_code=="RGN42"), "RGN80", site_code))|> #merge Peterborough site codes
    mutate(site_code=ifelse((site_code=="RWFTW"|site_code=="RWF01"|site_code=="RWF02"), "RWFTW", site_code)) #merge Tunbridge site codes
}

beddays_by_site<-fun_load_beddays("Data/nhp_hospsite_beddays_mth.csv")

beddays_by_prov<-fun_load_beddays("Data/nhp_hospsite_beddays_mth.csv")|>
  mutate(organisation_code=substr(der_provider_site_code, start = 1, stop = 3))|>#get organisation code
    group_by(yearmon, organisation_code)|>
    summarise(beddays=sum(beddays))

```


## Friends & Family
```{r}
friends_and_family_data<-read.csv("Data/formatted_friends_and_family_data.csv")|>
    mutate(month=as.Date(month))|>
 merge_sites()|>
  group_by(month, site_code)|>
 summarise(percent=mean(percent, na.rm=TRUE))|>
  filter(site_code=="REMRQ"|site_code=="REM21"|site_code=="RBN01"|site_code=="REMBG"|
         site_code=="RVY01"|site_code=="RVY02"|site_code=="RJR05")

```



## Staff turnover
```{r}
workforce_udal<-read.csv("Data/sql_workforce.csv")
workforce_links<-read_excel("Data/links_workforce.xlsx")
workforce_data<-combine_workforce(workforce_udal,workforce_links)
turnover<-wrangle_turnover("sql_turnover.csv")

```







## Staff sickness

```{r}


# staff_sickness
staff_sickness<-staff_sickness_absence_formatting("Data/staff_sickness_absence.csv")|>
  mutate(month=as.Date(month))|>
      mutate(organisation_code=ifelse((organisation_code=="REM"|organisation_code=="RQ6"), "REM", organisation_code))|> #merge historical Royal Liverpool codes
    group_by(month, organisation_code)|>
  summarise(fte_days_sick=sum(fte_days_sick), fte_days_available=sum(fte_days_available) )|> #regroup following merging the organisation codes
  mutate(percent=(fte_days_sick/fte_days_available)*100)|>
  filter(organisation_code=="REM"|organisation_code=="RBN"|organisation_code=="RVY"|
          organisation_code=="RJR" )
```

## Healthcare acquired infections

```{r}


hcai_data_combined<-hcai_formatting("Data/hai_cdiff_pre_2018.csv", 
                "Data/hai_cdiff.csv",
                "Data/hai_ecoli.csv",
                 "Data/hai_klebsiella.csv",
                 "Data/hai_mssa.csv",
                "Data/hai_mrsa.csv",
                "Data/hai_p_aeruginosa.csv")|>
  left_join(beddays_by_prov[,c("organisation_code", "yearmon", "beddays")], by=c("organisation_code", "month"="yearmon"))|>
  mutate(rate=(count_of_cases/beddays)*10000)|> #cases per 10,000 beddays
  group_by(month, organisation_code)|>
summarise(combined_rate=sum(rate))|>#calculate combined rate for all infectiond
  filter(month>="2018-03-01")|>
  filter(organisation_code=="REM")|> #for Royal Liverpool
    ggplot(aes(x = month, y =combined_rate) ) + 
   geom_line(linewidth=1) 




```
## In-hospital Falls and Fractures

```{r}

falls_and_fractures<- fun_load_sus_apcs("Data/nhp_hospsite_apcs_mth.csv", beddays)|>   rename(site_code=der_provider_site_code)|>
  rename(month=yearmon)|>
 merge_sites()|>
  group_by(site_code, month)|>
  summarise(fall_fracs=sum(fall_fracs), beddays=sum(beddays))|> #recalculate rate following merging sites
  mutate(ff_rate=(fall_fracs/beddays)*1000) #rate per 1000 beddays
 

```

## MISSING VALUES Summary Hospital-Level Mortality Indicator
```{r}
shmi_data<-wrangle_shmi("Data/sql_shmi.csv")|>
  mutate(month=floor_date(effective_snapshot_date, "month"))|> #Format date to monthly
  filter(level=="Site")|> #Select only Site data (only available 2019 onwards)
  merge_sites()|>
  group_by(month, site_code)|>
  summarise(observed=sum(observed), expected=sum(expected))|>
  mutate(shmi=observed/expected)
 # filter(site_code=="REMRQ"|site_code=="REM21"|site_code=="RBN01"|site_code=="REMBG"|
  #       site_code=="RVY01"|site_code=="RVY02"|site_code=="RJR05"|site_code=="RQ617")




shmi_data|>
  filter(organisation_code=="RGM")|>
    ggplot(aes(x = month, y =expected) ) + 
   geom_line(size=1) +
   labs( title = "",y = "No. of cases", x="")+
   theme( legend.position= c(0.25, 0.8))+
   scale_y_continuous(limits=c(0, NA)) 


friends_and_family_data|>
  filter(site_code=="RVJ01")|>
    ggplot(aes(x = month, y =percent) ) + 
   geom_line(size=1) +
   labs( title = "",y = "No. of cases", x="")+
   theme( legend.position= c(0.25, 0.8))+
   scale_y_continuous(limits=c(0, NA)) 

#RGM21 no shmi
#+RGM22 no f&f /shmi

 #RGN42 - no f&f/shmi
# RGN80

 #RVJ01+
 #  RVJ20 no shmi
 



 
```



## RTT waiting time
```{r}
rtt_data<-read.csv("Data/formatted_rtt_data.csv") |>
    mutate(month=as.Date(month))|>
    mutate(organisation_code=ifelse((organisation_code=="REM"|organisation_code=="RQ6"), "REM", organisation_code))|> #merge historical Royal Liverpool codes
    group_by(month, organisation_code)|>
  summarise(median_by_prov = median(rep(weeks,number_of_incomplete_pathways)), number_incomplete=sum(number_of_incomplete_pathways))|> #Median by month and provider 
  mutate(median_by_prov=ifelse(is.na(median_by_prov),0,median_by_prov))|>
    filter(organisation_code=="REM"|organisation_code=="RJR"|organisation_code=="RVY"|
           organisation_code==  "RBN")


```



## Bed occupancy
```{r}
occupancy_data<-wrangle_bed_occupancy("Data/sql_bed_occupancy.csv")|>
     mutate(effective_snapshot_date=as.Date(effective_snapshot_date,"%Y-%m-%d"))|> #Format date 
  mutate(month=floor_date(effective_snapshot_date, "month"))|> #Format date to monthly
  filter(report_period_length=="Quarterly")|>
      mutate(organisation_code=ifelse((organisation_code=="REM"|organisation_code=="RQ6"), "REM", organisation_code))|> #merge historical Royal Liverpool codes
  group_by(month, organisation_code)|>
  summarise(available=sum(available), occupied=sum(occupied))|>
  mutate(bed_occupancy=occupied/available)

```

## Length of Stay
```{r}

length_of_stay<- fun_load_sus_apcs("Data/nhp_hospsite_apcs_mth.csv", beddays)|>
  rename(site_code=der_provider_site_code)|>
  rename(month=yearmon)|>
 merge_sites()|>
  group_by(site_code, month)|>
  summarise(los=sum(los), spells=sum(spells))|> #recalculate following merge of sites
  mutate(avg_los=los/spells) |>
  filter(site_code=="RGM22")|> 
    ggplot(aes(x = month, y =avg_los) ) + 
   geom_line(linewidth=1) 


```

## TO DO Emergency readmissions


# Other plots information

## Cleaning staff
```{r}
cleaning_staff<-wrangle_eric("Data/sql_eric_09_15.csv", "Data/sql_eric_16_23.csv")|>
  filter(measure=="Cleaning staff (WTE)")|>
  filter(level=="Site")|>
  mutate(month=floor_date(effective_snapshot_date, "month"))|> #Format date to monthly
  left_join(beddays_by_site[,c("der_provider_site_code", "beddays", "yearmon")], 
                   by=c("site_code"= "der_provider_site_code", "month"="yearmon"))|>
 merge_sites()|>
  mutate(rate=(value/beddays)*1000) #WTE per 1000 beddays



```

## C. Difficile rate over time
```{r}

#c.diff only as this goes back before 2017/2018
hcai_formatting("Data/hai_cdiff_pre_2018.csv", 
                "Data/hai_cdiff.csv",
                "Data/hai_ecoli.csv",
                 "Data/hai_klebsiella.csv",
                 "Data/hai_mssa.csv",
                "Data/hai_mrsa.csv",
                "Data/hai_p_aeruginosa.csv")|>
  left_join(beddays_by_prov[,c("organisation_code", "yearmon", "beddays")], by=c("organisation_code", "month"="yearmon"))|>
  mutate(rate=(count_of_cases/beddays)*10000)|> #cases per 10,000 beddays
filter(collection=="C.difficile")|>
  filter(organisation_code=="REM")|> #for Royal Liverpool
    ggplot(aes(x = month, y =rate) ) + 
   geom_line(linewidth=1) 

# C. difficile numbers are too small to use in CIA as so much variability.

```

# Causal Impact analysis

## Staff sickness

```{r, include=TRUE}


# Find the best matches  
mm <- MarketMatching::best_matches(data=staff_sickness,
                   id_variable="organisation_code",
                   date_variable="month",
                   matching_variable="percent",
                   parallel=FALSE,
                   warping_limit=1, # warping limit=1
                   dtw_emphasis=1, # rely only on dtw for pre-screening
                   matches=2, # request 2 matches
                   start_match_period="2017-04-01",
                   end_match_period="2022-10-01")

#View the best matches
knitr::kable(head(mm$BestMatches))

results <- MarketMatching::inference(matched_markets = mm,
                                     analyze_betas=TRUE,
                                     test_market = "REM",
                                    end_post_period = "2023-10-01",
                                    alpha=0.05, 
                                    prior_level_sd=0.02,
                                    nseasons=12)

# Plot out actual vs expected
results$PlotActualVersusExpected

# Plot out cumulative effect
results$PlotCumulativeEffect

# Plot pointwise effect
results$PlotPointEffect

#Plot the actuals 
results$PlotActuals

# See which hospital receives the highest weight in determining the outcome
coeff <- results$Coefficients
knitr::kable(head(coeff))


```

```{r, include=FALSE}

#Store predicted values in dataframe
pred <- results$Predictions
knitr::kable(head(pred))

# Check out the DW and MAPE of the model
results$PlotPriorLevelSdAnalysis

#Prospective Pseudo Power Curves -will help you evaluate if your choice of test and control markets creates a sufficient model to measure a realistic lift from a future intervention. 

power <- MarketMatching::test_fake_lift(matched_markets = mm, 
                                      test_market = "REM", 
                                      end_fake_post_period = "2023-10-01", 
                                      prior_level_sd = 0.01, 
                                      steps=10,
                                      max_fake_lift=0.05)
#And plot the graph- Ideally, a curve that starts at high probability on the left side, reaches its minimum at zero lift, and then rises again symmetrically. If the curve does not reach its minimum at zero there may be systemic model bias in the post period. 
power$ResultsGraph


```

## RTT Waiting time data- Number of incomplete pathways

```{r}


# Find the best matches  
mm <- MarketMatching::best_matches(rtt_data,
                   id_variable="organisation_code",
                   date_variable="month",
                   matching_variable="number_incomplete",
                   parallel=FALSE,
                   warping_limit=1, # warping limit=1
                   dtw_emphasis=1, # rely only on dtw for pre-screening
                   matches=2, # request 5 matches
                   start_match_period="2017-04-01",
                   end_match_period="2022-10-01")

#View the best matches
knitr::kable(head(mm$BestMatches))

results <- MarketMatching::inference(matched_markets = mm,
                                     analyze_betas=TRUE,
                                     test_market = "REM",
                                    end_post_period = "2023-10-01",
                                    alpha=0.05, 
                                    prior_level_sd=0.01,
                                    nseasons=12)

#Absolute Effect indicates an increase in the median of 0.94 relative to what we expected. The Relative Effect provides a standardized view, indicating a 0.94% increase in the median. Probability of a causal impact indicates that the likelihood of observing this effect by chance is high (e.g., 100 - 55.2). 

# Plot out actual vs expected
results$PlotActualVersusExpected

# Plot out cumulative effect
results$PlotCumulativeEffect

# Plot pointwise effect
results$PlotPointEffect

#Plot the actuals 
results$PlotActuals


# See which hospital recieves the highest weight in determining the outcome
coeff <- results$Coefficients
knitr::kable(head(coeff))



```

```{r, include=FALSE}

#Store predicted values in dataframe
pred <- results$Predictions
knitr::kable(head(pred))

# Check out the DW and MAPE of the model
results$PlotPriorLevelSdAnalysis

#Prospective Pseudo Power Curves -will help you evaluate if your choice of test and control markets creates a sufficient model to measure a realistic lift from a future intervention. 

power <- MarketMatching::test_fake_lift(matched_markets = mm, 
                                      test_market = "REM", 
                                      end_fake_post_period = "2023-10-01", 
                                      prior_level_sd = 0.01, 
                                      steps=10,
                                      max_fake_lift=0.05)
#And plot the graph- Ideally, a curve that starts at high probability on the left side, reaches its minimum at zero lift, and then rises again symmetrically. If the curve does not reach its minimum at zero there may be systemic model bias in the post period. 
power$ResultsGraph



```







