---
title: "Measuring the impact of Single Bed Rooms: Causal Impact Analysis"
editor: visual
execute:
  echo: false
  message: false
  warning: false
  cache: false
lang: en-GB
author: Sarah Lucas
date: last-modified
date-format: "YYYY-MM-DD"
title-block-banner: "#f9bf07"
title-block-banner-color: "#333739"
format:
  html:
    embed-resources: true
    smooth-scroll: true
    theme: cosmo
    fontcolor: black
    toc: true
    toc-location: left
    toc-title: Summary
    toc-depth: 3
    grid:
      sidebar-width: 250px
      body-width: 1050px
      margin-width: 0px
      gutter-width: 1.5rem
css: styles.css
---

```{r, include=FALSE}

library(tidyverse)
library(MarketMatching)
library(tsibble)
library(targets)
library(janitor)
library(readxl)
library(zoo)
library(lubridate)
library(ggrepel)
library(flextable)
library(egg)
library(StrategyUnitTheme)
library(patchwork)
library(metafor)
library(bayesmeta)

## RTT waiting time
rtt_waiting_time<-tar_read(rtt_waiting_time_cia_format) 

## Bed occupancy
bed_occupancy<-tar_read(bed_occupancy_cia_format)

## Length of Stay
length_of_stay<- tar_read(length_of_stay_cia_format)

## Emergency readmissions
emergency_readmissions<-tar_read(emergency_readmissions_cia_format)

## Friends & Family
friends_and_family<-tar_read(friends_and_family_cia_format)

## Staff turnover
staff_turnover<-tar_read(staff_turnover_cia_format)

## Staff sickness
staff_sickness<-tar_read(staff_sickness_cia_format)

## Healthcare acquired infections - Infection rate per 10,000 bed days
hcai<-tar_read(hcai_cia_format)

## In-hospital Falls and Fractures - Fall rate per 1000 bed days
falls_and_fractures<- tar_read(falls_and_fractures_cia_format)

# SUS death rate (deaths/1000 admissions)
sus_deaths<- tar_read(sus_deaths_cia_format)

#Staff survey
staff_survey<-tar_read(staff_survey_cia_format)

# Cleaning costs
cleaning_costs<-tar_read(cleaning_costs_cia_format)

#Loading control data
single_bedroom_matches_final<-tar_read(single_bedroom_matches_final)

source("R/CIA_Functions.R")

test<-single_bedroom_matches_final|>
  filter(organisation_code=="RGM")

test2<-single_bedroom_matches_final|>
  filter(organisation_code=="RAL")


```

```{r, include=FALSE, fig.height=6, fig.width=10}

LoS_output<-tar_read(LoS_output)|>
filter(!is.na(site))

rma.uni(yi=RelEffect, vi=(RelEffect.sd)^2, data=LoS_output)

```

# Introduction

# Executive Summary

# Hospital Background

## Royal Liverpool

## Southmead

## Peterborough

### Availability of indicators over time 

```{r, fig.height=6, fig.width=10}

tar_read(indicator_availability_plot)

```

### Availability of indicators by site

```{r}

tar_read(indicator_availability_table)

```

# Productivity and Efficiency

## Waiting time- Median (in weeks)

::: panel-tabset
### Summary

Points to the left indicate a decrease in median waiting time following a switch to single bed rooms, which is considered a positive effect. Significant positive effects are in green, while significant negative effects (those on the right) are indicated in red. Grey indicates no significant change.

```{r, fig.width=8, fig.height=4}

waiting_time_median_output<-tar_read(waiting_time_median_output)

forest_plot(waiting_time_median_output)

model_effects_table(waiting_time_median_output)

```

#### Mean effect on median waiting time for DGH/Acute hospitals

```{r, fig.width=8, fig.height=2.5}

mean_forest_plot_DGH_Acute(waiting_time_median_output)

```

### Decrease

::: columns
::: {.column width="50%"}
#### Clatterbridge

```{r, fig.width=5, fig.height=6}

waiting_time_median_REN<-tar_read(waiting_time_median_REN)

#evaluating_model("REN", NA, rtt_waiting_time, "2020-06-01", "median_by_prov", 0.05, waiting_time_median_REN, single_bedroom_matches_final)

cia_summary_plots(waiting_time_median_REN, "Median waiting time (wks)", "2020-06-01")

```
:::

::: {.column width="50%"}
#### Peterborough

```{r,  fig.width=5, fig.height=6}

waiting_time_median_RGN<-tar_read(waiting_time_median_RGN)

#evaluating_model("RGN", NA, rtt_waiting_time, "2010-11-01", "median_by_prov", 0.01, waiting_time_median_RGN, single_bedroom_matches_final)

cia_summary_plots(waiting_time_median_RGN, "Median waiting time (wks)", "2010-11-01")

```
:::
:::

### No change

::: columns
::: {.column width="50%"}
#### Royal Liverpool

```{r, fig.width=5, fig.height=6}

waiting_time_median_REM<-tar_read(waiting_time_median_REM)

#evaluating_model("REM", NA,  rtt_waiting_time, "2022-10-01", "median_by_prov", 0.05, waiting_time_median_REM, single_bedroom_matches_final)

cia_summary_plots(waiting_time_median_REM, "Median waiting time (wks)", "2022-10-01")
```
:::

::: {.column width="50%"}
#### Papworth

```{r, fig.width=5, fig.height=6}

waiting_time_median_RGM<-tar_read(waiting_time_median_RGM)

#evaluating_model("RGM", NA, rtt_waiting_time, "2019-05-01", "median_by_prov", 0.05, waiting_time_median_RGM, single_bedroom_matches_final)

cia_summary_plots(waiting_time_median_RGM, "Median waiting time (wks)", "2019-05-01")

```
:::

```{r, fig.width=5, fig.height=6}
#### Chase Farm
#waiting_time_median_RAL<-tar_read(waiting_time_median_RAL)

#evaluating_model("RAL", NA, rtt_waiting_time, "2018-09-01", "median_by_prov", 0.01, waiting_time_median_RAL, single_bedroom_matches_final)

#cia_summary_plots(waiting_time_median_RAL, "Study site: Chase Farm, RAL","Median waiting time (wks)", "2018-09-01")

```

```{r, fig.width=5, fig.height=6}
#### Southmead
#waiting_time_median_RVJ<-tar_read(waiting_time_median_RVJ)

#evaluating_model("RVJ",NA,  rtt_waiting_time, "2014-05-01", "median_by_prov", 0.1, waiting_time_median_RVJ, single_bedroom_matches_final)

#cia_summary_plots(waiting_time_median_RVJ, "Median waiting time (wks)", "2014-05-01")
```
:::

### Increase

:::columns
::: {.column width="50%"}
#### Tunbridge Wells

```{r, fig.width=6, fig.height=5}

waiting_time_median_RWF<-tar_read(waiting_time_median_RWF)

#evaluating_model("RWF", NA, rtt_waiting_time, "2011-01-01", "median_by_prov", 0.01, waiting_time_median_RWF, single_bedroom_matches_final)

cia_summary_plots(waiting_time_median_RWF, "Median waiting time (wks)", "2011-01-01")
```
:::
:::

:::

## Waiting time - Total number waiting

::: panel-tabset
### Summary

Points to the left indicate a decrease in number of patients on waiting lists following a switch to single bed rooms, which is considered a positive effect. Significant positive effects are in green, while significant negative effects (those on the right) are indicated in red. Grey indicates no significant change.

```{r, fig.width=8, fig.height=4}

waiting_time_number_output<-tar_read(waiting_time_number_output)

forest_plot(waiting_time_number_output)

model_effects_table(waiting_time_number_output)


```

```{r, fig.width=8, fig.height=2.5}

mean_forest_plot_DGH_Acute(waiting_time_number_output)

```

### No change

::: columns
::: {.column width="50%"}
#### Papworth

```{r, fig.width=5, fig.height=6}

waiting_time_number_RGM<-tar_read(waiting_time_number_RGM)

#evaluating_model("RGM", NA, rtt_waiting_time, "2019-05-01", "number_incomplete", 0.05, waiting_time_number_RGM, single_bedroom_matches_final)

cia_summary_plots(waiting_time_number_RGM, "Number waiting", "2019-05-01")
```

```{r, fig.width=5, fig.height=6}
#### Chase Farm

#waiting_time_number_RAL<-tar_read(waiting_time_number_RAL)

#evaluating_model("RAL", NA, rtt_waiting_time, "2018-09-01", "number_incomplete", 0.05, waiting_time_number_RAL, single_bedroom_matches_final)

#cia_summary_plots(waiting_time_number_RAL, "Study site: Chase Farm, RAL","Number waiting", "2018-09-01")
```

```{r, fig.width=5, fig.height=6}
#### Southmead
#waiting_time_number_RVJ<-tar_read(waiting_time_number_RVJ) 

#evaluating_model("RVJ", NA, rtt_waiting_time, "2014-05-01", "number_incomplete", 0.1, waiting_time_number_RVJ, single_bedroom_matches_final)

#cia_summary_plots(waiting_time_number_RVJ, "Number waiting", "2014-05-01")
```

#### Royal Liverpool

```{r, fig.width=5, fig.height=6}

waiting_time_number_REM<-tar_read(waiting_time_number_REM)

#evaluating_model("REM", NA, rtt_waiting_time, "2022-10-01", "number_incomplete", 0.1, waiting_time_number_REM, single_bedroom_matches_final)

cia_summary_plots(waiting_time_number_REM, "Number waiting", "2022-10-01")
```
:::

::: {.column width="50%"}
#### Peterborough

```{r, fig.width=5, fig.height=6}

waiting_time_number_RGN<-tar_read(waiting_time_number_RGN)

#evaluating_model("RGN", NA, rtt_waiting_time, "2010-11-01","number_incomplete", 0.1, waiting_time_number_RGN, single_bedroom_matches_final)

cia_summary_plots(waiting_time_number_RGN, "Number waiting", "2010-11-01")
```
:::
:::

### Increase

::: columns
::: {.column width="50%"}
#### Tunbridge Wells

```{r, fig.width=5, fig.height=6}

waiting_time_number_RWF<-tar_read(waiting_time_number_RWF)

#evaluating_model("RWF", NA, rtt_waiting_time, "2011-01-01", "number_incomplete", 0.1, waiting_time_number_RWF, single_bedroom_matches_final)

cia_summary_plots(waiting_time_number_RWF, "Number waiting", "2011-01-01")
```
:::

::: {.column width="50%"}
#### Clatterbridge

```{r, fig.width=5, fig.height=6}

waiting_time_number_REN<-tar_read(waiting_time_number_REN)

#evaluating_model("REN", NA, rtt_waiting_time, "2020-06-01", "number_incomplete", 0.1, waiting_time_number_REN, single_bedroom_matches_final)

cia_summary_plots(waiting_time_number_REN, "Number waiting", "2020-06-01")

#rtt_waiting_time|>
#  filter(organisation_code=="REN")|>
#  ggplot()+
# geom_line(aes(y=number_incomplete, x=month))+
#  scale_y_continuous(limits=c(0,1200))

```
:::
:::
:::

## Length of stay

::: panel-tabset
### Summary

Points to the left indicate a decrease in average length of stay following a switch to single bed rooms, which is considered a positive effect. Significant positive effects are in green, while significant negative effects (those on the right) are indicated in red. Grey indicates no significant change.

```{r, fig.width=8, fig.height=4}

LoS_output<-tar_read(LoS_output)

forest_plot(LoS_output)

model_effects_table(LoS_output)

```

```{r, fig.width=8, fig.height=2.5}

mean_forest_plot_DGH_Acute(LoS_output)

```

### Decrease

```{r, fig.width=5, fig.height=6}
#### Papworth

#COVID-19 spikes in the post switch period are impacting LoS and these are not seen in the controls

#LoS_RGM<-tar_read(LoS_RGM)

#evaluating_model("RGM", "RGM22", length_of_stay, "2019-05-01", "avg_los", 0.05, LoS_RGM, single_bedroom_matches_final)

#cia_summary_plots(LoS_RGM, "Study site: Papworth, RGM","Average LoS (days)", "2019-05-01")
```

::: columns
::: {.column width="50%"}
#### Peterborough

```{r, fig.width=5, fig.height=6}

LoS_RGN<-tar_read(LoS_RGN)

#evaluating_model("RGN",  "RGN80", length_of_stay, "2010-11-01","avg_los", 0.01, LoS_RGN, single_bedroom_matches_final)

cia_summary_plots(LoS_RGN, "Average LoS (days)", "2010-11-01")
```

#### Chase Farm

```{r, fig.width=5, fig.height=6}

LoS_RAL<-tar_read(LoS_RAL)

#evaluating_model("RAL", "RALC7", length_of_stay, "2018-09-01", "avg_los", 0.05, LoS_RAL, single_bedroom_matches_final)

cia_summary_plots(LoS_RAL,"Average LoS (days)", "2018-09-01")
```
:::

::: {.column width="50%"}
#### Southmead

```{r, fig.width=5, fig.height=6}

LoS_RVJ<-tar_read(LoS_RVJ)

#evaluating_model("RVJ","RVJ01",  length_of_stay, "2014-05-01", "avg_los", 0.01, LoS_RVJ, single_bedroom_matches_final)

cia_summary_plots(LoS_RVJ,"Average LoS (days)", "2014-05-01")
```

#### Royal Liverpool

```{r, fig.width=5, fig.height=6}

LoS_REM<-tar_read(LoS_REM)

#evaluating_model("REM", "REMRQ",  length_of_stay, "2022-10-01", "avg_los", 0.05, LoS_REM, single_bedroom_matches_final)

cia_summary_plots(LoS_REM, "Average LoS (days)", "2022-10-01")
```
:::
:::

### No change

#### Tunbridge Wells

```{r, fig.width=5, fig.height=6}

LoS_RWF<-tar_read(LoS_RWF)

#evaluating_model("RWF",  "RWFTW", length_of_stay, "2011-01-01", "avg_los", 0.05, LoS_RWF, single_bedroom_matches_final)

cia_summary_plots(LoS_RWF,"Average LoS (days)", "2011-01-01")

```

### Increase

::: columns
::: {.column width="50%"}
#### Clatterbridge

```{r, fig.width=5, fig.height=6}

LoS_REN<-tar_read(LoS_REN)

#evaluating_model("REN", "REN22", length_of_stay, "2020-06-01", "avg_los", 0.1, LoS_REN, single_bedroom_matches_final)

cia_summary_plots(LoS_REN,"Average LoS (days)", "2020-06-01")

```
:::
:::
:::

## Emergency Readmissions

::: panel-tabset
### Summary

Points to the left indicate a decrease in emergency readmissions following a switch to single bed rooms, which is considered a positive effect. Significant positive effects are in green, while significant negative effects (those on the right) are indicated in red. Grey indicates no significant change.

```{r, fig.width=8, fig.height=4}

emergency_readmissions_output<-tar_read(emergency_readmissions_output)

forest_plot(emergency_readmissions_output)

model_effects_table(emergency_readmissions_output)


```

Mean effect for DGH/Acute hospitals

```{r, fig.width=8, fig.height=2.5}

mean_forest_plot_DGH_Acute(emergency_readmissions_output)

```

### Decrease

::: columns
::: {.column width="50%"}
#### Clatterbridge

```{r, fig.width=5, fig.height=6}

emergency_readmissions_REN<-tar_read(emergency_readmissions_REN)

#evaluating_model("REN", "REN22", emergency_readmissions, "2020-06-01","perc", 0.1, emergency_readmissions_REN, single_bedroom_matches_final)

cia_summary_plots(emergency_readmissions_REN, "% readmissions", "2020-06-01")

```

#### Peterborough

```{r, fig.width=5, fig.height=6}

emergency_readmissions_RGN<-tar_read(emergency_readmissions_RGN)

#evaluating_model("RGN",  "RGN80", emergency_readmissions, "2010-11-01","perc", 0.1, emergency_readmissions_RGN, single_bedroom_matches_final)

cia_summary_plots(emergency_readmissions_RGN,"% readmissions", "2010-11-01")
```
:::

::: {.column width="50%"}
#### Tunbridge Wells

```{r, fig.width=5, fig.height=6}

emergency_readmissions_RWF<-tar_read(emergency_readmissions_RWF)

#evaluating_model("RWF",  "RWFTW", emergency_readmissions, "2011-01-01", "perc", 0.01, emergency_readmissions_RWF, single_bedroom_matches_final)

cia_summary_plots(emergency_readmissions_RWF, "% readmissions", "2011-01-01")
```
:::
:::

### No change

::: columns
::: {.column width="50%"}
#### Royal Liverpool

```{r, fig.width=5, fig.height=6}

emergency_readmissions_REM<-tar_read(emergency_readmissions_REM)

#evaluating_model("REM", "REMRQ",  emergency_readmissions, "2022-10-01", "perc", 0.1, emergency_readmissions_REM, single_bedroom_matches_final)


cia_summary_plots(emergency_readmissions_REM, "% readmissions", "2022-10-01")
```

#### Papworth

```{r, fig.width=5, fig.height=6}

emergency_readmissions_RGM<-tar_read(emergency_readmissions_RGM)

#evaluating_model("RGM", "RGM22", emergency_readmissions, "2019-05-01", "perc", 0.1, emergency_readmissions_RGM, single_bedroom_matches_final)

cia_summary_plots(emergency_readmissions_RGM, "% readmissions", "2019-05-01")
```
:::

::: {.column width="50%"}
#### Chase Farm

```{r,  fig.width=5, fig.height=6}

emergency_readmissions_RAL<-tar_read(emergency_readmissions_RAL)

#evaluating_model("RAL", "RALC7", emergency_readmissions, "2018-09-01", "perc", 0.05, emergency_readmissions_RAL, single_bedroom_matches_final)

cia_summary_plots(emergency_readmissions_RAL,"% readmissions", "2018-09-01")

```

Controls for Chase Farm do not show the same trends; Chase Farm emergency readmissions were decreasing from 2012 while for the controls emergency readmissions were stay stable or increasing.

#### Southmead

```{r, fig.width=5, fig.height=6}

emergency_readmissions_RVJ<-tar_read(emergency_readmissions_RVJ)

#evaluating_model("RVJ","RVJ01",  emergency_readmissions, "2014-05-01","perc", 0.05, emergency_readmissions_RVJ, single_bedroom_matches_final)

cia_summary_plots(emergency_readmissions_RVJ, "% readmissions", "2014-05-01")
```
:::
:::
:::

## Bed Occupancy

::: panel-tabset
### Summary

Points to the right indicate a increase in bed occupancy following a switch to single bed rooms, which is considered a positive effect. Significant positive effects are in green, while significant negative effects (those on the left) are indicated in red. Grey indicates no significant change.

```{r, fig.width=8, fig.height=4}

bed_occupancy_output<-tar_read(bed_occupancy_output)

forest_plot(bed_occupancy_output)

model_effects_table(bed_occupancy_output)


```

Mean effect for DGH/Acute hospitals

```{r, fig.width=8, fig.height=2.5}

mean_forest_plot_DGH_Acute(bed_occupancy_output)

```

```{r, fig.width=5, fig.height=6}

#### Papworth - Only 4 points post switch and last one might be impacted by COVID

#Post switch period is impacted by COVID-19

#bed_occupancy_RGM<-tar_read(bed_occupancy_RGM)

#evaluating_model("RGM",NA, bed_occupancy, "2019-05-01", "bed_occupancy", 0.05, bed_occupancy_RGM, single_bedroom_matches_final)

#cia_summary_plots(bed_occupancy_RGM,"Percentage", "2019-05-01")
```

### Decrease

#### Chase Farm

```{r, fig.width=5, fig.height=6}

bed_occupancy_RAL<-tar_read(bed_occupancy_RAL)

#evaluating_model("RAL",NA,  bed_occupancy, "2018-09-01", "bed_occupancy", 0.05, bed_occupancy_RAL, single_bedroom_matches_final)

cia_summary_plots(bed_occupancy_RAL, "Percentage", "2018-09-01")
```

### Increase

::: columns
::: {.column width="50%"}
#### Royal Liverpool

```{r,  fig.width=5, fig.height=6}

bed_occupancy_REM<-tar_read(bed_occupancy_REM)

#evaluating_model("REM", NA, bed_occupancy, "2022-10-01", "bed_occupancy", 0.01, bed_occupancy_REM, single_bedroom_matches_final)

cia_summary_plots(bed_occupancy_REM, "Percentage", "2022-10-01")
```

#### Clatterbridge

```{r,  fig.width=5, fig.height=6}

bed_occupancy_REN<-tar_read(bed_occupancy_REN)

#evaluating_model("REN", NA, bed_occupancy, "2020-06-01", "bed_occupancy", 0.1, bed_occupancy_REN, single_bedroom_matches_final)

cia_summary_plots(bed_occupancy_REN,"Percentage", "2020-06-01")
```
:::

::: {.column width="50%"}
#### Southmead

```{r, fig.width=5, fig.height=6}

bed_occupancy_RVJ<-tar_read(bed_occupancy_RVJ)

#evaluating_model("RVJ", NA, bed_occupancy, "2014-05-01", "bed_occupancy", 0.1, bed_occupancy_RVJ, single_bedroom_matches_final)

cia_summary_plots(bed_occupancy_RVJ, "Percentage", "2014-05-01")
```


:::
:::

::: {.smaller}
Black dotted line indicates the time of the last data point prior to the switch to single bedrooms
:::
:::

# Health and Safety

## Healthcare acquired infections

Grey indicates no significant change in the combined rate of healthcare acquired infections (number per 10,000 beddays) following a switch to single bed rooms.

::: panel-tabset
### Summary

```{r, include=TRUE, fig.width=8, fig.height=4}

hcai_output<-tar_read(hcai_output)

forest_plot(hcai_output)

model_effects_table(hcai_output)

```

### No change

#### Royal Liverpool

```{r, fig.width=5, fig.height=6}

hcai_REM<-tar_read(hcai_REM)

#evaluating_model("REM", NA, hcai, "2022-10-01", "combined_rate", 0.1, hcai_REM, single_bedroom_matches_final)

cia_summary_plots(hcai_REM, "Rate/10,000 beddays", "2022-10-01")
```
:::

```{r,  fig.width=5, fig.height=6}
#### Clatterbridge

# Very low rate down to zero and some larger spikes-> CIs going negative

#hcai_REN<-tar_read(hcai_REN)

#evaluating_model("REN",NA,  hcai, "2020-06-01", "combined_rate", 0.01, hcai_REN, single_bedroom_matches_final)

#cia_summary_plots(hcai_REN, "Rate/10,000 beddays", "2020-06-01")
```

## Falls and Fractures in hospital

::: panel-tabset
### Summary

Points to the left indicate a decrease in falls and fractures following a switch to single bed rooms, which is considered a positive effect. Significant positive effects are in green, while significant negative effects (those on the right) are indicated in red. Grey indicates no significant change.

```{r, include=TRUE, fig.width=8, fig.height=4}

falls_and_fractures_output<-tar_read(falls_and_fractures_output)

forest_plot(falls_and_fractures_output)

model_effects_table(falls_and_fractures_output)

```

```{r, fig.width=8, fig.height=2}

mean_forest_plot_DGH_Acute(falls_and_fractures_output)

```

### Decrease

#### Peterborough

```{r, fig.width=5, fig.height=6}

falls_and_fractures_RGN<-tar_read(falls_and_fractures_RGN)

#evaluating_model("RGN",  "RGN80",falls_and_fractures, "2010-11-01","ff_rate", 0.01, falls_and_fractures_RGN, single_bedroom_matches_final)

cia_summary_plots(falls_and_fractures_RGN,"% of spells", "2010-11-01")
```

### No change

::: columns
::: {.column width="50%"}
#### Royal Liverpool

```{r, fig.width=5, fig.height=6}

falls_and_fractures_REM<-tar_read(falls_and_fractures_REM)

#evaluating_model("REM", "REMRQ",  falls_and_fractures, "2022-10-01", "ff_rate", 0.1, falls_and_fractures_REM, single_bedroom_matches_final)

cia_summary_plots(falls_and_fractures_REM, "% of spells", "2022-10-01")
```

#### Southmead

```{r,  fig.width=5, fig.height=6}

falls_and_fractures_RVJ<-tar_read(falls_and_fractures_RVJ)

#evaluating_model("RVJ","RVJ01",  falls_and_fractures, "2014-05-01","ff_rate", 0.1, falls_and_fractures_RVJ, single_bedroom_matches_final)

cia_summary_plots(falls_and_fractures_RVJ,"% of spells", "2014-05-01")
```

Outcome period is cut short as the rate of falls and fractures at Southmead jumps suddenly in the second year of the outcome period (Nov 2015); this change does not appear to be associated with the change to single rooms as it occurs suddenly almost 18 months after the change to single rooms.

```{r, fig.width=5, fig.height=6}
#### Clatterbridge

#falls_and_fractures_REN<-tar_read(falls_and_fractures_REN)

#evaluating_model("REN", "REN22", falls_and_fractures, "2020-06-01","ff_rate", 0.05, falls_and_fractures_REN, single_bedroom_matches_final)

#cia_summary_plots(falls_and_fractures_REN, "% of spells", "2020-06-01")


```

```{r, fig.width=5, fig.height=6}
#### Papworth
#falls_and_fractures_RGM<-tar_read(falls_and_fractures_RGM)

#evaluating_model("RGM", "RGM22", falls_and_fractures, "2019-05-01", "ff_rate", 0.05, falls_and_fractures_RGM, single_bedroom_matches_final)

#cia_summary_plots(falls_and_fractures_RGM, "% of spells", "2019-05-01")
```

```{r, fig.width=5, fig.height=6}
#### Chase Farm
#falls_and_fractures_RAL<-tar_read(falls_and_fractures_RAL)

#evaluating_model("RAL", "RALC7", falls_and_fractures, "2018-09-01", "ff_rate", 0.05, falls_and_fractures_RAL, single_bedroom_matches_final)

#cia_summary_plots(falls_and_fractures_RAL,"% of spells", "2018-09-01")
```
:::

::: {.column width="50%"}
#### Tunbridge Wells

```{r, fig.width=5, fig.height=6}

falls_and_fractures_RWF<-tar_read(falls_and_fractures_RWF)

#evaluating_model("RWF",  "RWFTW", falls_and_fractures, "2011-01-01", "ff_rate", 0.05, falls_and_fractures_RWF, single_bedroom_matches_final)

cia_summary_plots(falls_and_fractures_RWF, "% of spells", "2011-01-01")
```
:::
:::
:::

## Deaths in hospital

::: panel-tabset
### Summary

Points to the left indicate a decrease in hospital deaths following a switch to single bed rooms, which is considered a positive effect. Significant positive effects are in green, while significant negative effects (those on the right) are indicated in red. Grey indicates no significant change.

```{r, include=TRUE, fig.width=8, fig.height=4}

sus_deaths_output<-tar_read(sus_deaths_output)

forest_plot(sus_deaths_output)

model_effects_table(sus_deaths_output)

```

```{r, fig.width=8, fig.height=2}

mean_forest_plot_DGH_Acute(sus_deaths_output)

```

### Decrease

::: columns
::: {.column width="50%"}
#### Peterborough
```{r, fig.width=5, fig.height=6}

sus_deaths_RGN<-tar_read(sus_deaths_RGN)

#evaluating_model("RGN",  "RGN80", sus_deaths, "2010-11-01","hosp_rate_1000", 0.1, sus_deaths_RGN, single_bedroom_matches_final)

cia_summary_plots(sus_deaths_RGN, "No./per 1,000 discharges", "2010-11-01")
```
:::

::: {.column width="50%"}
#### Tunbridge Wells
```{r, fig.width=5, fig.height=6}

sus_deaths_RWF<-tar_read(sus_deaths_RWF)

#evaluating_model("RWF",  "RWFTW", sus_deaths, "2011-01-01", "hosp_rate_1000", 0.01, sus_deaths_RWF, single_bedroom_matches_final)

cia_summary_plots(sus_deaths_RWF, "No./per 1,000 discharges", "2011-01-01")
```
:::
:::

### No change

::: columns
::: {.column width="50%"}
#### Royal Liverpool

```{r,  fig.width=5, fig.height=6}

sus_deaths_REM<-tar_read(sus_deaths_REM)

#evaluating_model("REM", "REMRQ",  sus_deaths, "2022-10-01", "hosp_rate_1000", 0.05, sus_deaths_REM, single_bedroom_matches_final)

cia_summary_plots(sus_deaths_REM, "No./per 1,000 discharges", "2022-10-01")
```

```{r, fig.width=5, fig.height=6}
#### Papworth
#sus_deaths_RGM<-tar_read(sus_deaths_RGM)

#evaluating_model("RGM", "RGM22", sus_deaths, "2019-05-01", "hosp_rate_1000", 0.05, sus_deaths_RGM, single_bedroom_matches_final)

#cia_summary_plots(sus_deaths_RGM, "No./per 1,000 discharges", "2019-05-01")

```

```{r, include=FALSE}

sapply(file.path(tempdir(), list.files(tempdir())), unlink)
```

```{r, fig.width=5, fig.height=6}
#### Chase Farm

#sus_deaths_RAL<-tar_read(sus_deaths_RAL)

#evaluating_model("RAL", "RALC7", sus_deaths, "2018-09-01","hosp_rate_1000", 0.05, sus_deaths_RAL, single_bedroom_matches_final)

#cia_summary_plots(sus_deaths_RAL, "No./per 1,000 discharges", "2018-09-01")
```
:::

::: {.column width="50%"}
#### Southmead

```{r,  fig.width=5, fig.height=6}

sus_deaths_RVJ<-tar_read(sus_deaths_RVJ)

#evaluating_model("RVJ","RVJ01",  sus_deaths, "2014-05-01","hosp_rate_1000", 0.01, sus_deaths_RVJ, single_bedroom_matches_final)

cia_summary_plots(sus_deaths_RVJ,"No./per 1,000 discharges", "2014-05-01")
```
:::
:::

### Increase

#### Clatterbridge

```{r,  fig.width=5, fig.height=6}

sus_deaths_REN<-tar_read(sus_deaths_REN)

#evaluating_model("REN", "REN22", sus_deaths, "2020-06-01","hosp_rate_1000", 0.1, sus_deaths_REN, single_bedroom_matches_final )

cia_summary_plots(sus_deaths_REN, "No./per 1,000 discharges", "2020-06-01")


```
:::

# Patient and Staff Experience

It should be noted that for the friends and family test scores there is significant missing data from March 2020 until late/early 2021, therefore for both Papworth and Clatterbridge there is missing data during the post switch period, although data is missing for both these study sites and for there control sites.

## Patient experience - Friends and Family scores

::: panel-tabset
### Summary

Points to the right indicate a increase in positive scores on the Friends and Family patient experience test following a switch to single bed rooms, which is considered a positive effect. Significant positive effects are in green, while significant negative effects (those on the left) are indicated in red. Grey indicates no significant change.

```{r, include=TRUE, fig.width=8, fig.height=4}

friends_and_family_output<-tar_read(friends_and_family_output)

forest_plot(friends_and_family_output)

model_effects_table(friends_and_family_output)

```

### Decrease

#### Clatterbridge (REN)

```{r, fig.width=5, fig.height=6}

friends_and_family_REN<-tar_read(friends_and_family_REN)

#evaluating_model("REN","REN22", friends_and_family,"2020-06-01", "friends_and_family_percent", 0.1, friends_and_family_REN, single_bedroom_matches_final )

cia_summary_plots(friends_and_family_REN,"Positive responses (%)", "2020-06-01")

#Last data point prior to switch was about 4 months prior then no data for 8 months after, as switch came during COVID
friends_and_family_REN$CausalImpactObject$report
```

### No Change

::: columns
::: {.column width="50%"}
#### Royal Liverpool (REMRQ)

```{r, fig.width=5,fig.height=6 }

friends_and_family_REM<-tar_read(friends_and_family_REM)

#evaluating_model("REM","REMRQ", friends_and_family,"2022-10-01", "friends_and_family_percent", 0.1, friends_and_family_REM, single_bedroom_matches_final)

cia_summary_plots(friends_and_family_REM, "Positive responses (%)", "2022-10-01")

# Large amount of data missing in the two years prior due to gap over covid. One of the control sites doesn't go back far enough for it is causing the data to be cut off. Think I need to have less matches for this one. But would still have a disturbed pre switch period due to COVID

```

#### Papworth (RGM)

```{r, fig.width=5, fig.height=6}

friends_and_family_RGM<-tar_read(friends_and_family_RGM)

#evaluating_model("RGM", "RGM22", friends_and_family,"2019-05-01", "friends_and_family_percent", 0.1, friends_and_family_RGM, single_bedroom_matches_final)

cia_summary_plots(friends_and_family_RGM, "Positive responses (%)", "2019-05-01")

```
:::

::: {.column width="50%"}
#### Chase Farm Hospital (RAL)

```{r, fig.width=5, fig.height=6}

friends_and_family_RAL<-tar_read(friends_and_family_RAL)

#evaluating_model("RAL","RALC7",  friends_and_family,"2018-09-01", "friends_and_family_percent", 0.01, friends_and_family_RAL, single_bedroom_matches_final)

cia_summary_plots(friends_and_family_RAL, "Positive responses (%)", "2018-09-01")
```
:::
:::

:::

## Staff sickness

::: panel-tabset
### Summary

Points to the left indicate a decrease in staff sickness following a switch to single bed rooms, which is considered a positive effect. Significant positive effects are in green, while significant negative effects (those on the right) are indicated in red. Grey indicates no significant change.

```{r, include=TRUE, fig.width=8, fig.height=4}

staff_sickness_output<-tar_read(staff_sickness_output)

forest_plot(staff_sickness_output)

model_effects_table(staff_sickness_output)

```

```{r, fig.width=8, fig.height=2}

mean_forest_plot_DGH_Acute(staff_sickness_output)

```

### No change

::: columns
::: {.column width="50%"}
#### Royal Liverpool (REM)

```{r, fig.height=5, fig.width=6}

staff_sickness_REM<-tar_read(staff_sickness_REM)

#evaluating_model("REM",NA, staff_sickness,"2022-10-01", "staff_sickness_percent", 0.05, staff_sickness_REM, single_bedroom_matches_final)

cia_summary_plots(staff_sickness_REM, "Sickness Rate (%)", "2022-10-01")

```

#### Clatterbridge (REN)

```{r, fig.width=5, fig.height=6}

staff_sickness_REN<-tar_read(staff_sickness_REN)

#evaluating_model("REN", NA,staff_sickness,"2020-06-01", "staff_sickness_percent", 0.1,staff_sickness_REN, single_bedroom_matches_final )

cia_summary_plots(staff_sickness_REN, "Sickness Rate (%)", "2020-06-01")

```
:::

::: {.column width="50%"}
#### Papworth (RGM)

```{r, fig.width=5, fig.height=6}

staff_sickness_RGM<-tar_read(staff_sickness_RGM)

#evaluating_model("RGM", NA,staff_sickness,"2019-05-01", "staff_sickness_percent", 0.05, staff_sickness_RGM, single_bedroom_matches_final)

cia_summary_plots(staff_sickness_RGM, "Sickness Rate (%)", "2019-05-01")
```

#### Chase Farm Hospital (RAL)

```{r,  fig.width=5, fig.height=6}

staff_sickness_RAL<-tar_read(staff_sickness_RAL)

#evaluating_model("RAL", staff_sickness,"2018-09-01", "staff_sickness_percent", 0.05, staff_sickness_RAL, single_bedroom_matches_final)

cia_summary_plots(staff_sickness_RAL, "Sickness Rate (%)", "2018-09-01")
```
:::
:::

### Increase

#### Southmead (RVJ)

```{r, fig.width=5, fig.height=6}

staff_sickness_RVJ<-tar_read(staff_sickness_RVJ)

#evaluating_model("RVJ", NA,staff_sickness,"2014-05-01", "staff_sickness_percent", 0.05, staff_sickness_RVJ, single_bedroom_matches_final)

cia_summary_plots(staff_sickness_RVJ, "Sickness Rate (%)", "2014-05-01")
```
:::

## Staff turnover

::: panel-tabset
### Summary

```{r, include=TRUE, fig.width=8, fig.height=4}

staff_turnover_output<-tar_read(staff_turnover_output)

forest_plot(staff_turnover_output)

model_effects_table(staff_turnover_output)

```

### No change

#### Royal Liverpool (REM)

```{r, fig.width=5, fig.height=6}

staff_turnover_REM<-tar_read(staff_turnover_REM)

#evaluating_model("REM", NA,staff_turnover,"2022-10-01", "leaving_rate", 0.1, staff_turnover_REM, single_bedroom_matches_final)

cia_summary_plots(staff_turnover_REM, "Staff leaving rate (%)", "2022-10-01")
```
:::

## Staff survey

::: panel-tabset
### Summary

Points to the right indicate a increase in positive responses to the NHS staff survey following a switch to single bed rooms, which is considered a positive effect. Significant positive effects are in green, while significant negative effects (those on the left) are indicated in red. Grey indicates no significant change.

```{r, include=TRUE, fig.width=8, fig.height=4}

staff_survey_output<-tar_read(staff_survey_output)

forest_plot(staff_survey_output)

model_effects_table(staff_survey_output)

```

```{r, fig.width=8, fig.height=2}

mean_forest_plot_DGH_Acute(staff_survey_output)

```

### Decrease

#### Clatterbridge (REN)

```{r,  fig.width=5, fig.height=6}

staff_survey_REN<-tar_read(staff_survey_REN)
  
#evaluating_model("REN", NA,staff_survey,"2020-06-01", "positive_responses", 0.01, staff_survey_REN, single_bedroom_matches_final)

cia_summary_plots( staff_survey_REN, "Positive Responses (%)", "2020-06-01")
```
::: {.smaller}
Black dotted line indicates the time of the last data point prior to the switch to single bedrooms
:::
### No change

::: columns
::: {.column width="50%"}
#### Royal Liverpool (REM)

```{r, fig.width=5, fig.height=6}

staff_survey_REM<-tar_read(staff_survey_REM)
  
#evaluating_model("REM", NA,staff_survey,"2022-10-01", "positive_responses", 0.01, staff_survey_REM, single_bedroom_matches_final)

cia_summary_plots( staff_survey_REM, "Positive Responses (%)", "2022-10-01")
```

#### Chase Farm (RAL)

```{r,  fig.width=5, fig.height=6}

staff_survey_RAL<-tar_read(staff_survey_RAL)
  
#evaluating_model("RAL", NA,staff_survey,"2018-09-01", "positive_responses", 0.01, staff_survey_RAL, single_bedroom_matches_final)

cia_summary_plots( staff_survey_RAL, "Positive Responses (%)", "2018-09-01")
```
:::

::: {.column width="50%"}
#### Southmead (RVJ)

```{r, fig.width=5, fig.height=6}

staff_survey_RVJ<-tar_read(staff_survey_RVJ)
  
#evaluating_model("RVJ", NA,staff_survey,"2014-05-01", "positive_responses", 0.01, staff_survey_RVJ, single_bedroom_matches_final)

cia_summary_plots( staff_survey_RVJ, "Positive Responses (%)", "2014-05-01")
```
:::
:::

::: {.smaller}
Black dotted line indicates the time of the last data point prior to the switch to single bedrooms
:::

### Increase

#### Papworth (RGM)

```{r, fig.width=5, fig.height=6}

staff_survey_RGM<-tar_read(staff_survey_RGM)
  
#evaluating_model("RGM", NA,staff_survey,"2019-05-01", "positive_responses", 0.01, staff_survey_RGM, single_bedroom_matches_final)

cia_summary_plots( staff_survey_RGM, "Positive Responses (%)", "2019-05-01")


matches<-select_matches("RGN",
           NA,
           staff_survey,
           "2010-11-01",
           "positive_responses",
           single_bedroom_matches_final) 


```
::: {.smaller}
Black dotted line indicates the time of the last data point prior to the switch to single bedrooms
:::

:::



## Cleaning costs

::: panel-tabset
### Summary

Points to the left indicate a decrease in cleaning costs following a switch to single bed rooms, which is considered a positive effect. Significant positive effects are in green, while significant negative effects (those on the right) are indicated in red. Grey indicates no significant change.

```{r, include=TRUE, fig.width=8, fig.height=4}

cleaning_costs_output<-tar_read(cleaning_costs_output)

forest_plot(cleaning_costs_output)

model_effects_table(cleaning_costs_output)

```

### No change

#### Papworth (RGM)

```{r, fig.width=5, fig.height=6}

cleaning_costs_RGM<-tar_read(cleaning_costs_RGM)
  
#evaluating_model("RGM", "RGM22",cleaning_costs,"2019-05-01","cleaning_service_cost", 0.01, cleaning_costs_RGM, single_bedroom_matches_final)

cia_summary_plots( cleaning_costs_RGM, "Cost", "2019-05-01")
```
::: {.smaller}
Black dotted line indicates the time of the last data point prior to the switch to single bedrooms
:::
### Increase

::: columns
::: {.column width="50%"}
#### Royal Liverpool (REM)

```{r, fig.width=5, fig.height=6}

cleaning_costs_REM<-tar_read(cleaning_costs_REM)
  
#evaluating_model("REM","REMRQ",cleaning_costs,"2022-10-01", "cleaning_service_cost", 0.01, cleaning_costs_REM, single_bedroom_matches_final)

cia_summary_plots( cleaning_costs_REM, "Cost", "2022-10-01")
```

#### Chase Farm (RAL)

```{r,  fig.width=5, fig.height=6}

cleaning_costs_RAL<-tar_read(cleaning_costs_RAL)
  
#evaluating_model("RAL", "RALC7",cleaning_costs,"2018-09-01", "cleaning_service_cost", 0.01, cleaning_costs_RAL, single_bedroom_matches_final)

cia_summary_plots(cleaning_costs_RAL, "Cost", "2018-09-01")
```
:::

::: {.column width="50%"}
#### Clatterbridge (REN)

```{r,  fig.width=5, fig.height=6}

cleaning_costs_REN<-tar_read(cleaning_costs_REN)
  
#evaluating_model("REN", "REN22",cleaning_costs,"2020-06-01", "cleaning_service_cost", 0.01, cleaning_costs_REN, single_bedroom_matches_final)

cia_summary_plots( cleaning_costs_REN, "Cost", "2020-06-01")
```
:::
:::

::: {.smaller}
Black dotted line indicates the time of the last data point prior to the switch to single bedrooms
:::

:::

## Summary of effects across sites

```{r}
summary_table_indicators_and_sites(waiting_time_median_output,
                                             waiting_time_number_output,
                                             LoS_output,
                                             emergency_readmissions_output,
                                             cleaning_costs_output,
                                             bed_occupancy_output,
                                             hcai_output,
                                             falls_and_fractures_output,
                                             sus_deaths_output,
                                             friends_and_family_output,
                                             staff_sickness_output,
                                             staff_survey_output) 




```
