---
title: "Measuring the impact of Single Bed Rooms: Causal Impact Analysis"
editor: visual
execute:
  echo: false
  message: false
  warning: false
  cache: false
lang: en-GB
authors: Andrew Hood, Sarah Lucas and Anya Ferguson
date: last-modified
date-format: "YYYY-MM-DD"
title-block-banner: "#f9bf07"
title-block-banner-color: "#333739"
format:
  html:
    embed-resources: true
    smooth-scroll: true
    theme: cosmo
    fontcolor: black
    toc: true
    toc-location: left
    toc-title: Summary
    toc-depth: 3
    grid:
      sidebar-width: 250px
      body-width: 1050px
      margin-width: 0px
      gutter-width: 1.5rem
css: styles.css

bibliography: references.bib
---

```{r packages, include=FALSE}
library(bayesmeta)
library(DiagrammeR)
library(egg)
library(flextable)
library(ggrepel)
library(glue)
library(imputeTS)
library(janitor)
library(lubridate)
library(MarketMatching)
library(metafor)
library(patchwork)
library(readxl)
library(StrategyUnitTheme)
library(stringr)
library(targets)
library(tidyverse)
library(tsibble)
library(zoo)
```

```{r functions}
source("R/CIA_Functions.R")
source("R/plot_functions.R")
source("R/formatting_outputs_functions.R")
```

```{r reading_data}
## RTT waiting time
rtt_waiting_time <- tar_read(rtt_waiting_time_cia_format)

## Bed occupancy
bed_occupancy <- tar_read(bed_occupancy_cia_format)

## Length of Stay
length_of_stay <- tar_read(length_of_stay_cia_format)

## Emergency readmissions
emergency_readmissions <- tar_read(emergency_readmissions_cia_format)

## Friends & Family
friends_and_family <- tar_read(friends_and_family_cia_format)

## Staff turnover
staff_turnover <- tar_read(staff_turnover_cia_format)

## Staff sickness
staff_sickness <- tar_read(staff_sickness_cia_format)

## Healthcare acquired infections - Infection rate per 10,000 bed days
hcai <- tar_read(hcai_cia_format)

cdiff <- tar_read(cdiff_cia_format)

## In-hospital Falls and Fractures - Fall rate per 1000 bed days
falls_and_fractures <- tar_read(falls_and_fractures_cia_format)

# SUS death rate (deaths/1000 admissions)
sus_deaths <- tar_read(sus_deaths_cia_format)

#Staff survey
staff_survey <- tar_read(staff_survey_cia_format)

# Cleaning costs
cleaning_costs <- tar_read(cleaning_costs_cia_format)

#Loading control data
single_bedroom_matches_final <- tar_read(single_bedroom_matches_final)

#Model outputs
waiting_time_median_output <- tar_read(waiting_time_median_output)
waiting_time_number_output <- tar_read(waiting_time_number_output)
LoS_output <- tar_read(LoS_output)
emergency_readmissions_output <- tar_read(emergency_readmissions_output)
bed_occupancy_output <- tar_read(bed_occupancy_output)
hcai_output <- tar_read(hcai_output)
cdiff_output <- tar_read(cdiff_output)
falls_and_fractures_output <- tar_read(falls_and_fractures_output)
sus_deaths_output <- tar_read(sus_deaths_output)
friends_and_family_output <- tar_read(friends_and_family_output)
staff_sickness_output <- tar_read(staff_sickness_output)
staff_turnover_output <- tar_read(staff_turnover_output)
staff_survey_output <- tar_read(staff_survey_output)
cleaning_costs_output <- tar_read(cleaning_costs_output)

controls <- tar_read(control_pool)
hospitals <- tar_read(hospitals)
```

```{r titles}
title_los <- get_title("los")
title_wait_time_median <- get_title("wait_time_median")
title_wait_time_number <- get_title("wait_time_number")
title_bed_occup <- get_title("bed_occup")
title_readmissions <- get_title("readmissions")
title_cleaning <- get_title("cleaning")
title_deaths <- get_title("deaths")
title_falls_fractures <- get_title("falls_fractures")
title_hcai <- get_title("hcai")
title_cdiff <- get_title("cdiff")
title_friends_family <- get_title("friends_family")
title_staff_sickness <- get_title("staff_sickness")
title_staff_turnover <- get_title("staff_turnover")
title_staff_survey <- get_title("staff_survey")
```

```{r, include=FALSE, fig.height=6, fig.width=10}

#LoS_output_test<-tar_read(LoS_output)|>
#filter(!is.na(site))|>
#  mutate(group=ifelse(site %in% c("Royal Liverpool", "Tunbridge Wells", "Southmead", "Peterborough"), "DGH", #"Specialist" ))

#LoS_output_DGH<-LoS_output_test|>
#  filter(group=="DGH")

#test<-rma.uni(yi=RelEffect, vi=(RelEffect.sd)^2, method="REML", data=LoS_output_DGH)
#forest(test)

#test2<-rma.mv(RelEffect, (RelEffect.sd)^2,  mod=~group, method="REML", data=LoS_output_test)
#forest(test2)

#res <- rma.mv(RelEffect, (RelEffect.sd)^2,  random = ~ 1 | group/site,  data=LoS_output_test)
#forest(res)
```

# Foreword??

Ask Cheryl / Eammon to write...otherwise omit.

# Introduction and background

Taken from initial plan and NHP update slides.

\<<include overview map>\>

# Executive Summary

# What we already know

There have been 2 NHP commissioned pieces of work in the recent past aiming to better understand the nature and scale of any impacts related to switching from multi-occupancy hospital rooms to single-bed rooms.

The Health Economics Unit undertook a literature review [@HEU_2022] primarily around clinical impacts, patient/staff experience and the economic impacts of the structural changes. The review highlighted, from evidence, the following with potential to be impacted in some way:

-   Mortality
-   Complications of disease
-   HCAI
-   Falls and patient safety
-   Readmissions
-   Privacy
-   Loneliness
-   Disturbance
-   Quality of Life
-   Length of stay
-   Costs of care

The conclusions of the review were that **"moving adult and child inpatients from older hospitals with largely shared rooms to fully single-room accommodation is unlikely to lead to a meaningful difference in clinical outcomes, may reduce overall costs per patient, and will lead to greater satisfaction in a majority of patients. However, switching to 100% single rooms will leave a substantial minority of people feeling lonely and socially isolated, with many patients preferring to be in a shared room. A compromise approach -- where accommodation is largely in single rooms but includes some bays with two to four beds -- may provide maximum satisfaction and minimise overall costs without adversely affecting clinical outcomes."**

More latterly, the Innovations team at NHP have created a living evidence review [@innovations_2024] on the topic to identify new and emerging evidence of effects of implementing single bedrooms and their potential scale. The review highlighted the ongoing variable nature of impacts with both positive, negative and neutral impacts found across length of stay, mortality, patient experience and staff attitudes.

Broadly speaking, the evidence points towards an increase in falls/fall risk, improved infection control and increased patient satisfaction with admitted care. More positive outcome impacts were generally demonstrated for specific clinical subgroups of patients notably intensive care; maternal and neonates; oncology.

The review summary suggests that **"Overall, 87% of studies analysed by Taylor et al., 2018 reported advantages associated with single patient rooms. Of these, 27% reported a combination of advantages and disadvantages, while 22% of the studies reported a combination of advantages and neutral results."**

# Hospital Background

Initially 11 hospitals were identified to have made a switch to single bedrooms. However due to being unable to access data for hospitals outside England 3 hospitals (Ulster Hospital, Glasgow Central and The Grange Hospital) were excluded from this analysis. James Paget hospital made a switch to single bedrooms in May 2023 but was also excluded from analysis, due to the switch being too recent and that currently the ward is used as interim beds for RAAC remedial work. An overview of the remaining seven hospitals that switched to SBR is shown in @tbl-sbr-switch.

```{r table_sbr_switch}
#| label: tbl-sbr-switch
#| tbl-cap: "Details of the switch to single bed accommodation at the seven intervention sites."
 
sbr_details <- tar_read(sbr_details)

tar_read(sbr_details_table)
```

## Royal Liverpool University Hospital

Royal Liverpool University Hospital is a large acute hospital. It mainly focuses on complex planned care and specialist services including nephrology, renal transplantation, nuclear medicine, haematology, lithotripsy, dermatology and urology [@royalliverpool_web]. The provider Liverpool University Hospitals NHS Foundation also manages Aintree University hospital and Broadgreen hospital. Royal Liverpool University Hospital moved to new site single bed accommodation in October 2022. Prior to the change, the site had been operating `r sbr_details |> filter(name == "Royal Liverpool") |> pull(pre_sbr_perc)`% single bed room accommodation [@eric].

## Clatterbridge Cancer Centre

The Clatterbridge Trust operates 3 cancer centres in the Cheshire and Merseyside area. The Liverpool centre moved to fully single-bed rooms in June 2020 having previously been at `r sbr_details |> filter(name == "Clatterbridge Cancer Centre") |> pull(pre_sbr_perc)`% SBR [@eric]. The centre offers the full range of cancer treatment, both routine and surgical as well as diagnostics, outpatient appointments and associated support services [@ccc_liverpool].

## Royal Papworth

Royal Papworth hospital is a specialist centre for cardiothoracic (heart and lung) treatment, surgery and transplantation [@papworth_web]. The move to single bed accommodation occurred in May 2019. Prior to the change, the site had been operating `r sbr_details |> filter(name == "Royal Papworth") |> pull(pre_sbr_perc)`% single bed room accommodation [@eric].

## Chase Farm

Chase Farm hospital is a planned care centre operated by the Royal Free London NHS Trust. The Trust also runs the Royal Free and Barnet Hospital sites as well as other acute service across greater London [@chasefarm_web]. The new-build Chase Farm site, opened in September 2018 and has `r sbr_details |> filter(name == "Chase Farm Hospital") |> pull(post_sbr_perc)`% single bed rooms having previously had `r sbr_details |> filter(name == "Chase Farm Hospital") |> pull(pre_sbr_perc)`% [@eric].

## Southmead

Southmead hospital is run by the North Bristol NHS Trust who also operate Frenchay and Cossham Hospitals as well as other acute and rehabilitation services. The Brunel building housing the hospital opened in May 2014 with `r sbr_details |> filter(name == "Southmead Hospital") |> pull(post_sbr_perc)`% single bed ensuite rooms. Previously the SBR provision for the trusts' main sites was around `r sbr_details |> filter(name == "Southmead Hospital") |> pull(pre_sbr_perc)`% [@eric].

## Tunbridge Wells

The new hospital at Tunbridge Wells, replacing services at Pembury and Kent & Sussex, opened in 2 phases in January 2011 (maternity and children) and September 2011 (other inpatient services). According to ERIC [@eric] the site has `r sbr_details |> filter(name == "Tunbridge Wells") |> pull(post_sbr_perc)`% single bed inpatient rooms, with levels prior to 2011 being `r sbr_details |> filter(name == "Tunbridge Wells") |> pull(pre_sbr_perc)`%.

## Peterborough

Peterborough City Hospital, operated by North West Anglia NHS Trust, was opened in November 2010 offering a range of acute and specialist services [@peterborough_web]. The site went from `r sbr_details |> filter(name == "Peterborough (city) Hospital") |> pull(pre_sbr_perc)`% single bed inpatient rooms to `r sbr_details |> filter(name == "Peterborough (city) Hospital") |> pull(post_sbr_perc)`% SBR [@eric].

# Impact measures and data sources

Categorisation of the evidence suggests that impacts can be considered under one or more of health & safety, staff & patient experience and productivity & efficiency. A long list of potential impacts were drawn from the existing evidence reviews and measures were sought from published data that were specific to the logic/causal relationship or were proxies for the suggested effect. Measures were screened into the study if there were sufficient time series, if the data were consistent, if the data were available at least at provider level.

Where existing data sources were lacking, and for those impacts based on hospital data, we derived suitable measures from Secondary User Service (SUS) data held within NCDR [@ncdr].

Our final set of impact measures are thus:

[ ](images/indicators.png)

## Table with further detail when decided format

## Availability of indicators over time and for each site

@fig-avail demonstrates the availability of indicator datasets over time and the 'intervention' dates of the 7 sites to allow for general assessment of suitability for testing.

```{r indicator_availability_plot, fig.height = 6, fig.width = 10}
#| label: fig-avail
#| fig-cap: "Availability of indicators over time. Dashed lines represent the month of the switch to SBR in each intervention site."
tar_read(indicator_availability_plot)
```

Additional data issues have been uncovered during preparation of the data for analysis and some further omissions of some indicator/site combinations have been made. Full notes on data availability and suitability in relation to the analysis can be found in Appendix B (@sec-appendix-B).

@tbl-avail summarises which indicators have been been investigated for each site, and where analyses were not possible due to lack of data or other data issues.

```{r indicator_availability_table}
#| label: tbl-avail
#| tbl-cap: "Summary of indicators that were investigated for each site."
tar_read(indicator_availability_table)
```

For Royal Liverpool there is only 1 year post switch to single bedrooms, it is possible the effect size or overall direction of the effect may be different if there was a slightly longer outcome period.

For some sites (i.e Chase Farm, Clatterbridge and Papworth) at least part of the outcome period is impacted by COVID-19. While COVID-19 effects will also be present in the matched control sites, the magnitude of effects varies greatly between hospitals. Indeed, for some measures Papworth was excluded as it appears to have been impacted to a much greater degree by COVID-19 than it's control sites.

In some cases there is missing data or anomalies in the outcome periods, i.e. sudden increases or decreases, which has meant the outcome period has been cut short. For the Health and Safety indicators the rates were generally low at the specialist sites (Papworth, Clatterbridge and Chase Farm), often dropping to zero in some months, which meant it was not always possible to fit a suitable causal impact model.

For some indicator variables data is only available at a provider level, this means that where the switch to single bedrooms occurred at a provider with multiple sites the effects of the switch will be diluted by the lack of the change in single bedroom percentage at the other sites.

# Description of methods {#sec-methods}

Causal Impact Analysis is a technique that uses a control group to estimate the post-intervention counterfactual against which to measure study group impacts [@broderson2015]. We have used this method to quantify the change in the study hospitals following their switch to single-bed rooms by comparing the actual effects to a control group (similar hospital providers, patient case-mix and prior trends) that have been used to predict what would have happened to the outcome of interest had there been no switch.

## Finding control hospitals {#sec-methods-controls}

There was a multi-phase selection process to create a pool of controls for each site. A summary of these steps is presented in @fig-flow-controls. The first step was to match the intervention site and controls on type of site. For Clatterbridge the pool was limited to cancer-only sites and for Royal Papworth the pool was limited to cardiac sites. For all other intervention sites the pool was limited to general acute sites.

```{r selecting_controls_flow_chart}
#| label: fig-flow-controls
#| fig-cap: "Flow chart of the multi-phase process used to select the top 20 controls for each site. *The similarity rank is calculated as the sum of the ranked difference of floor space, median age of patients and the elective:non-elective ratio of admissions."
tar_read(flow_chart_selecting_controls)
```

```{r selecting_controls_number_sites}
number_control_sites <- tar_read(number_control_sites)
```

Controls were then matched on the percentage of single bed rooms available at the provider. Providers were excluded if the difference between their SBR percentage and the intervention's provider was greater than 5% at the time of the SBR switch. Then providers were excluded if their SBR percentage increased by 5% or more after this point.

Differences in floor space, the median age of inpatients and the elective:non-elective ratio of admissions were calculated between the controls and intervention sites and ranked. A similarity rank was calculated by ranking the sum of these three ranks and sites with a similarity rank less than or equal to 20 formed the control pool for further analysis. Due to Clatterbridge and Royal Papworth being specialist trusts, there were only `r number_control_sites |> filter(organisation_code == "REN") |> pull()` and `r number_control_sites |> filter(organisation_code == "RGM") |> pull()` sites respectively in the control pools.

A full list and map of the sites in the control pools for each intervention site can be found in Appendix C (@sec-appendix-C).

## Causal Impact Analysis {#sec-methods-cia}

The causal impact analysis is implemented using the `MarketMatching` [@MarketMatching] package in R , which uses the `dtw` [@dtw] and `CausalImpact` [@CausalImpact] R packages to provide a simple way to find the most appropriate control matches using dynamic time warping and then using these controls for causal impact analysis using Bayesian structural time-series models. Using control sites means that seasonal changes are accounted for within the analysis. The dynamic time warping approach prevents potential controls being excluded if their relationship with the study site is temporarily shifted; it accounts for any shifts in any historic trends, such as a winter peak starting slightly earlier or later at a potential control site.

Following the multi-phase control selection process outlined in @sec-methods-controls, the control pools for each site were fed into the `MarketMatching` package. This step selects the best matched control sites based on them having similar trends in the variable of interest over time to the study site. Up to 5 control sites were selected for each study site, but for some sites, particularly the specialist centres, the number of appropriate matches was smaller and so fewer than 5 control sites were selected. Control sites are selected for each site and indicator variable and as this matching of controls is based on similar trends over time a study site may have different control sites selected for different indicators. A list of the control providers/sites identified by `MarketMatching` for each indicator can be found in Appendix D (@sec-appendix-D).

The causal impact models were generated for each site and for each indicator where sufficient data was available to fit a model and there was at least 1 year of outcome period. Where possible a 2-year outcome period was used. Ideally at least a 2-year baseline period would have been used, but to maximise the number of sites we could analyse data for a shorter baseline period was used if an appropriate model could be fitted to the data. The Mean Absolute Percentage Error (MAPE) and Durbin-Watson statistic of the models were checked, and the prior local level standard error adjusted if required to ensure a good historical model fit while minimising the forecasting intervals.

## Aggregate (meta) analysis

Where possible, for each indicator variable a meta-analysis was conducted using the data for district general and acute hospitals. The specialist hospital sites were excluded from this analysis as it is felt the effects at these sites may not be generalisable when considering future building of general acute hospitals.

A random-effects meta-analysis was conducted using the `metafor` R package [@metafor] and weighting the relative effects for each site using the inverse variance, as used for meta-analysis of causal impact models by [@Schmitt2017ExtendingBS].

## Interpreting the causal impact analysis

Plots for each causal impact model are shown in appendix A (@sec-appendix-A). These plots are made up of three graphs, with the time point of the switch shown in red.

For example:

::: columns
::: {.column width="50%"}
```{r, fig.width=5, fig.height=6}
LoS_RGN <- tar_read(LoS_RGN)

cia_summary_plots(LoS_RGN, "Average LoS (days)", "2010-11-01")
```
:::

::: {.column width="50%"}
<br> 
<br>
<br>

1)  The expected value of the indicator in the outcome period, compared to the actual values of the study site.

<br> 
<br> 
<br>

2)  The point estimate shows the difference between the expected values and actual values at each time point, so at time points where the posterior intervals do not include zero there is a significant difference.

<br>
<br>

3)  The cumulative difference between the expected and actual values over the outcome period.
:::
:::

@sec-results give the summary effects for each indicator.

**Forest plots** give the relative effect in the outcome period, which is the proportional change that occurs following a switch to single bedrooms compared to what would be expected had the number of single bedroom not changed. For example, for median length of stay the effect size for Peterborough hospital is -0.19 (with a 95% credible interval of -0.22 to -0.16), i.e. 19% decrease in the median length of stay. Points to the left of the zero line on the forest plot with a credible interval that does not cross zero indicate there was a significant decrease. As a decrease in length of stay is considered a positive result so the point is coloured green. Any significant negative effect effect, such as an increase in length of stay or a decrease in positive responses to Friends and Family test, are shown in red.

Where there are results for 2 or more general acute hospitals a second forest plot shows the effects for just these general acute hospitals, alongside the mean value calculated in the meta-analysis. In this case the size of points indicates the weight that each site has been given in the analysis; those with the smallest credible intervals are given the greatest weight in calculating the mean.

**Results tables** give the average values over the outcome period, i.e. the cumulative effect at the end of the outcome period divided by the number of points in the outcome period. Due to data availability and issues the length of outcome period varies between sites, therefore the cumulative effect is not always comparable across sites. The tables give the actual value for the study site in the outcome period, the predicted value had no change in single bedrooms occurred, and the the absolute effect, which is the difference between the actual and predicted value. The relative effect size is a proportional change relative to the predicted value.

For example, Peterborough was predicted to have an mean length of stay in the outcome period of 4.8 days, however, following a switch to single bedrooms the actual average length of stay in the outcome period was 3.9 days. This is an absolute difference between predicted and actual values of 0.9 days, which is a 19% reduction in average length of stay compared to predicted values.

**Utilising the relative effect** - The relative effect gives us the proportional change that appears to occur as a result of switching to single bedrooms, so when future hospitals are being designed this % change could be directly applied to the predicted values at any particular point in time to show the impact that single bedrooms may have compared to multi-bed bays. For example, if length of stay at some future time point in a hospital with multi-bed bays is predicted to be 5 days, then a mean 8% decrease in length of stay would suggest that if the hospital was to have single bedroom the average length of stay would be only 4.6 days. 

Some of our indicators are rates, so the percentage change is a change in a rate. For example, a 10% decrease in emergency readmissions following a switch to single bedrooms means that if a future multi-bed hospital that was predicted to have a 20% emergency readmission rate, the emergency readmission rate for a single bedroom hospital would be expected to be 18%.

It is assumed the effects have stabilised within the 2 year outcome period so that the average relative effect in the outcome period is reflective of the true ongoing effect at any point in time, and any changes are not cumulative. Interpretation of median waiting time is more complex; it is possible there may be cumulative impacts as a result of sustained changes in productivity affecting waiting list size.


# Main results (including related notes from lookback exercise) {#sec-results}

## Productivity and Efficiency

### `r title_los`

Mean length of stay (in days) significantly decreased at 3/6 sites (Southmead, Peterborough and Chase Farm), was unchanged at 2/6 sites (Royal Liverpool and Tunbridge Wells), but significantly increased at Clatterbridge.

```{r, fig.width=8, fig.height=4}
forest_plot(
  LoS_output,
  "Points to the left indicate a decrease in mean length of stay following a switch to single bed   rooms, which is considered a positive effect. Significant positive effects are green, while significant negative effects (on the right) are red. Grey indicates no significant change.",
  "Relative effect of switching to single bedrooms on mean length of stay"
)

model_effects_table(LoS_output,
                    "Average effects of switching to single bedrooms on mean length of stay")
```

```{r, fig.width=8, fig.height=2.5}
mean_forest_plot_DGH_Acute(LoS_output,
                           "Mean effect on length of stay at general acute hospitals")
```

The effect on length of stay was highly variable with the Chase Farm (an elective care site) having a 55% reduction in length and Clatterbridge (a cancer centre) having a 34% increase. At the general acute hospitals the change in average length of stay varied from a 3% increase (equivalent to 0.1 days) at Tunbridge Wells to a significant 19% decrease (equivalent to 0.9 days) at Peterborough. For mean effect at general acute hospitals was a non-significant 8% reduction in length of stay.

Clatterbridge is a specialist cancer centre, so it is possible the switch to single bed rooms had a different impact on length of stay due to the nature of the activity at the site. Indeed, the average length of stay predicted for Clatterbridge based on historical trends (7.5 days) is higher than for the other sites, likely reflecting the different type of activity at this site. Average length of stay at Chase Farm was predicted to be 6 days, but following the switch was actually just over 2.5 days, such a large change may reflect a change in the type of activity conducted at the site following the switch, especially as this site conducts only elective care.

### `r title_wait_time_median`

The median waiting time (in weeks) significantly decreased at 2/5 sites (Royal Liverpool and Peterborough) and was unchanged at 2/5 sites (Papworth and Clatterbridge).

```{r, fig.width=8, fig.height=4}
forest_plot(
  waiting_time_median_output,
  "Points to the left indicate a decrease in median waiting time following a switch to single bed rooms, which is considered a positive effect. Significant positive effects are green, while significant negative effects (on the right) are indicated red. Grey indicates no significant change.",
  "Relative effect of switching to single bedrooms on median waiting time"
)

model_effects_table(
  waiting_time_median_output,
  "Average effects of switching to single bedrooms on median waiting time (in wks)"
)
```

```{r, fig.width=8, fig.height=2.5}
mean_forest_plot_DGH_Acute(
  waiting_time_median_output,
  "Mean effect on median waiting time at general acute hospitals"
)
```

The effect on median waiting time varied from a 12% reduction to a 15% increase. Both Royal Liverpool and Peterborough had a 12% reduction in median waiting time, which equated to a decrease from 19 wks to 16.7 wks at Royal Liverpool and from 5 wks to 4.3 wks at Peterborough. The mean effect at general acute hospitals was a non-significant 3% reduction in median waiting time.

At Peterborough median waiting time dropped and was then relatively stable for the 2-year outcome period suggesting there was a fixed effect and median waiting time would be unlikely to drop over time as a result of the switch to single bedrooms (@fig-wait-peterborough). For Royal Liverpool we only have 1-year of outcome data and it is not clear whether the change in median waiting time has stabilised or whether the switch to single rooms will result in a continued reduction in median waiting time over time.

Median waiting time significantly increased at Tunbridge Wells, but this effect appeared to only be temporary during the first year post-switch, during the second year of the outcome period the waiting times fall back in line with the expected values (@fig-wait-tunbridge). The switch to single bedrooms at Tunbridge Wells started in Jan 2011, which is the date we have used in our analysis, but occurred in stages between Jan and Sept 2011, so the differences seen in the first year could be due to disruption of services while the hospital was in a transition period.

### `r title_bed_occup`

Bed occupancy is measured quarterly and is only available at a Provider level. The percentage of available beds occupied significantly increased at 2/4 sites (Clatterbridge and Southmead) and was unchanged at 2/4 (Royal Liverpool and and Chase Farm). An increase in bed occupancy is generally considered a positive result, provided it does not result in an increase in Emergency department waiting times. We have not looked at Emergency department waiting times. However, Chase Farm only does elective care and Clatterbridge is a cancer centre, and so neither of these sites have Emergency departments.

```{r, fig.width=8, fig.height=4}
forest_plot(
  bed_occupancy_output,
  "Points to the right indicate an increase in bed occupancy following a switch to single bed rooms, which is considered a positive effect. Significant positive effects are green, while significant negative effects (on the left) are indicated red. Grey indicates no significant change.",
  "Relative effect of switching to single bedrooms on bed occupancy"
)

model_effects_table(
  bed_occupancy_output,
  "Average effects of switching to single bedrooms on % of bed occupancy"
)
```

```{r, fig.width=8, fig.height=2.5}
mean_forest_plot_DGH_Acute(bed_occupancy_output,
                           "Mean effect on bed occupancy at general acute hospitals")
```

Bed occupancy was either unchanged or increased by up to 13%. The mean effect at the 2 general acute hospitals was a non-significant 4% increase in bed occupancy.

For Southmead bed occupancy increased 8%, it was predicted to be on average 86% in the outcome period but an increase to 93% bed occupancy was seen. It is perhaps unsurprising there was no significant increase in bed occupancy at the Royal Liverpool as based on historic trends bed occupancy was already predicted to be over 95%, leaving little scope to increase this.

### `r title_readmissions`

The percentage of admissions that are emergency readmissions significantly decreased at 3/7 sites (Tunbridge Wells, Peterborough and Clatterbridge) and was unchanged at the remaining 4/7 sites.

```{r, fig.width=8, fig.height=4}
forest_plot(
  emergency_readmissions_output,
  "Points to the left indicate a decrease in emergency readmissions following a switch to single bed rooms, which is considered a positive effect. Significant positive effects are green, while significant negative effects (on the right) are red. Grey indicates no significant change.",
  "Relative effect of switching to single bedrooms on emergency readmissions"
)

model_effects_table(
  emergency_readmissions_output,
  "Average effects of switching to single bedrooms on % of emergency readmissions"
)
```

```{r, fig.width=8, fig.height=2.5}
mean_forest_plot_DGH_Acute(
  emergency_readmissions_output,
  "Mean effect on emergency readmission rate at general acute hospitals"
)
```

Emergency readmission rate was either unchanged or decreased by up to 28%. The mean effect at general acute hospitals was a non-significant 10% reduction in emergency readmissions. At Peterborough the % of emergency readmissions was predicted to be 34% but dropped to 25% following a switch to single bedrooms, while at Tunbridge Wells it was predicted to be 30% and dropped to 26%.

### `r title_cleaning`

The cleaning costs (in £) per square metre of occupied floor space significantly increased at 1/3 sites (Royal Liverpool) but decreased at 2/3 sites (Clatterbridge and Papworth).

```{r, include=TRUE, fig.width=8, fig.height=4}
forest_plot(
  cleaning_costs_output,
  "Points to the left indicate a decrease in cleaning costs following a switch to single bed rooms, which is considered a positive effect. Significant positive effects are green, while significant negative effects (on the right) are red. Grey indicates no significant change.",
  "Relative effect of switching to single bedrooms on cleaning costs"
)

model_effects_table(
  cleaning_costs_output,
  "Average effects of switching to single bedrooms on cleaning costs (£) per sqm"
)
```

Cleaning costs increased by 37% at Royal Liverpool, but decreased by 35% and 42% at Clatterbridge and Papworth, respectively. At Royal Liverpool the 37% increase reflects an increase of £14 per square metre from a predicted £44 to £58 per square metre.

Cleaning costs data are an annual measure, so there is limited data with only 1 or 2 data points in the outcome period, and the first data point in the outcome period may not reflect the true changes in cost as some of the costs will have occurred prior to the switch. Also, results shoudl be interpreted cautiously as there is missing occupied floor space data for 2020 and 2021, so we have had to impute values based on the available data and the time point when the switch to single bedrooms occurred.

## Health and Safety

### `r title_deaths`

The rate of in-hospital deaths (number per 1,000 discharges) significantly decreased at 1/5 sites (Peterborough), and was unchanged at 4/5 sites (Royal Liverpool, Tunbridge Wells, Clatterbridge and Southmead).

```{r, include=TRUE, fig.width=8, fig.height=4}
forest_plot(
  sus_deaths_output,
  "Points to the left indicate a decrease in hospital deaths following a switch to single bed rooms, which is considered a positive effect. Significant positive effects green, while significant negative effects (on the right) are red. Grey indicates no significant change.",
  "Relative effect of switching to single bedrooms on in-hospital deaths"
)

model_effects_table(
  sus_deaths_output,
  "Average effects of switching to single bedrooms on in-hospital deaths/1,000 discharges"
)
```

```{r, fig.width=8, fig.height=2.5}
mean_forest_plot_DGH_Acute(sus_deaths_output,
                           "Mean effect on in-hospital death rate at general acute hospitals")
```

In-hospital deaths were generally unchanged but decreased by 37% at Peterborough. The 37% decrease at Peterborough reflects a decrease from a predicted 38 deaths per 1,000 discharges to 24 deaths. The mean effect at general acute hospitals was a non-significant decrease of 11% in in-hospital death.

### `r title_falls_fractures`

The rate of in-hospital falls and injuries (% of spells) significantly decreased at 1/4 sites (Peterborough), and was unchanged at 3/4 sites (Royal Liverpool, Tunbridge Wells and Southmead).

```{r, include=TRUE, fig.width=8, fig.height=4}
forest_plot(
  falls_and_fractures_output,
  "Points to the left indicate a decrease in falls and fractures following a switch to single bed rooms, which is considered a positive effect. Significant positive effects are green, while significant negative effects (on the right) are red. Grey indicates no significant change.",
  "Relative effect of switching to single bedrooms on in-hospital falls, fractures and injuries"
)

model_effects_table(
  falls_and_fractures_output,
  "Average effects of switching to single bedrooms on % of spells with in-hospital fall or injury"
)
```

```{r, fig.width=8, fig.height=2.5}
mean_forest_plot_DGH_Acute(
  falls_and_fractures_output,
  "Mean effect on rate of falls, fractures and injuries while in hospital at general acute hospitals"
)
```

The in-hospital falls and injuries rate was generally unchanged, but decreased by 21% at Peterborough. The 21% decrease at Peterborough reflects a decrease from a predicted 3.2% of hospital spells having a fall or injury to 2.5%. The mean effect at general acute hospitals was a non-significant 3% reduction in the rate of in-hospital falls, injuries and fractures.

### `r title_cdiff`

The rate of healthcare acquired C.Difficile infections (cases per 10,000 bed days) decreased at 2/3 sites (Chase Farm and Southmead) but was unchanged at Royal Liverpool.

```{r, fig.width=8, fig.height=4}
forest_plot(
  cdiff_output,
  "Points to the left indicate a decrease in healthcare acquired C.Difficile infections  following a switch to single bed rooms, which is considered a positive effect. Significant positive effects are green. Grey indicates no significant change.",
  "Relative effect of switching to single bedrooms on rate of healthcare acquired C.Difficile infections"
)

model_effects_table(
  cdiff_output,
  "Average effects of switching to single bedrooms on cases of healthcare acquired C.Difficile infections /10,000 bed days"
)
```

```{r, fig.width=8, fig.height=2.5}
mean_forest_plot_DGH_Acute(
  cdiff_output,
  "Mean effect on the rate heathlcare acquired C.Difficile infections at general acute hospitals"
)
```

The rate of healthcare acquired C.Difficile was either unchanged or decreased by up to 36%. The 36% decrease in C.Diff infections at Southmead reflects a decrease from a predicted 2.1 cases per 10,000 beddays to 1.3 cases. The mean effect at general acute hospitals was a non-significant 24% reduction in the rate of C.Difficile infections.

## Patient and Staff Experience

### `r title_friends_family`

Patient experience was determined using the results of the Friends and Family test. The percentage of positive responses significantly decreased at 1/5 sites (Clatterbridge), and was unchanged at the other 4/5 sites (Royal Liverpool, Papworth, Southmead and Chase Farm).

```{r, include=TRUE, fig.width=8, fig.height=4}
forest_plot(
  friends_and_family_output,
  "Points to the right indicate an increase in positive scores on the Friends and Family patient experience test following a switch to single bed rooms, which is considered a positive effect. Significant positive effects are green, while significant negative effects (on the left) are red. Grey indicates no significant change.",
  "Relative effect of switching to single bedrooms on positive scores on the Friends and Family test"
)

model_effects_table(
  friends_and_family_output,
  "Average effects of switching to single bedrooms on % of positive responses on the Friends and Family test"
)
```

```{r, fig.width=8, fig.height=2.5}
mean_forest_plot_DGH_Acute(
  friends_and_family_output,
  "Mean effect on the % of positive responses to the Friends and Family test at general acute hospitals"
)
```

The percentage of positive responses to the Friend and Family Test generally remain unchanged but did decrease by 4% at Clatterbridge. It should be noted that based on historic trends Clatterbridge was predicted to have over 97% of positive responses, so although there was a small decrease the percentage of positive responses remained at almost 94%, which is broadly similar to that expected at the other study sites.

It should be noted that due to the COVID-19 pandemic there is missing friends and family test scores data from March 2020 until late 2020/early 2021 for all sites. Therefore, both Papworth and Clatterbridge have missing data in their outcome periods.

### `r title_staff_sickness`

The percentage of available days taken off sick by staff significantly increased at 2/7 sites (Southmead and Tunbridge Wells) and was unchanged at the remaining 5 sites.

```{r, include=TRUE, fig.width=8, fig.height=4}
forest_plot(
  staff_sickness_output,
  "Points to the left indicate a decrease in staff sickness following a switch to single bed rooms, which is considered a positive effect. Significant positive effects are green, while significant negative effects (on the right) are red. Grey indicates no significant change.",
  "Relative effect of switching to single bedrooms on staff sickness rate"
)

model_effects_table(
  staff_sickness_output,
  "Average effects of switching to single bedrooms on staff sickness rate (% of available days)"
)
```

```{r, fig.width=8, fig.height=2.5}
mean_forest_plot_DGH_Acute(
  staff_sickness_output,
  "Mean effect on the rate of staff sickness at general acute hospitals"
)
```

Staff sickness rate generally remained unchanged, but there was a 7% increase at Southmead. The mean effect at general acute was a significant increase of 6% in the staff sickness rate.

While there was a significant increase in staff sickness at Southmead (average of 4.6% of available days taken as sick days compared to a predicted 4.3%) this seems to have been a temporary effect. The sickness rate is increased in the first year after the switch to single bedrooms and during this period there is a significantly larger winter peak. In the second year of the outcome period staff sickness rates fell back in line with the expected rates. A similar, albeit non-significant, effect is seen at Peterborough with a larger winter spike in the first year of the outcome period before sickness levels return to expected levels.

### `r title_staff_turnover`

Staff turnover measured as percentage of staff leaving was not significantly changed at any of the 3 sites where data was available.

```{r, fig.width=8, fig.height=2}
forest_plot(
  staff_turnover_output,
  "Grey indicates no significant change in staff turnover following a switch to single bed rooms.",
  "Relative effect of switching to single bedrooms on staff turnover"
)

model_effects_table(
  staff_turnover_output,
  "Average effects of switching to single bedrooms on rate of staff turnover (% leaving)"
)
```

### `r title_staff_survey`

To assess staff experience the NHS staff survey was used and we analysed the percentage of staff that Agreed or Strongly Agreed with the statement 'I would recommend my trust as a place to work'.

The percentage of staff that would recommend their trust as a place to work significantly increased at 1/6 sites (Papworth), and was unchanged at 3/6 (Chase Farm, Royal Liverpool and Tunbridge Wells). At 2/6 sites (Southmead and Clatterbridge) there was a significant decrease in the percentage that would recommend their trust as a place to work.

```{r, include=TRUE, fig.width=8, fig.height=4}
forest_plot(
  staff_survey_output,
  "Points to the right indicate an increase in positive responses to the NHS staff survey following a switch to single bed rooms, which is considered a positive effect. Significant positive effects are green, while significant negative effects (on the left) are red. Grey indicates no significant change.",
  "Relative effect of switching to single bedrooms on % of NHS staff that recommend their workplace"
)

model_effects_table(
  staff_survey_output,
  "Average effects of switching to single bedrooms on % of NHS staff who would recommend their workplace"
)
```

```{r, fig.width=8, fig.height=2.5}
mean_forest_plot_DGH_Acute(
  staff_survey_output,
  "Mean effect on percentage of staff that would recommend their trust as a place to work at general acute hospitals"
)
```

The effect on the percentage of staff that would recommend their workplace varied from a 20% decrease to a 12% increase. At Southmead the 20% reduction in the percentage of staff recommending their workplace equates to a reduction from a predicted percentage of 57% recommending their workplace to 45% following the switch to single bedrooms. The mean effect at general acute hospitals was a significant reduction of 15% in the percentage of staff who would recommend their workplace.

At Southmead the decrease appears to be temporary, occurring in the first year post-switch to single bed rooms with positive responses increase back to the expected level in the second year of the outcome period.

The staff survey is an annual measure so there is limited data, with only 1 or 2 data points in the outcome period. The staff survey data is collected over a period of time in the autumn each year, but for analysis purposes we have set the date as the last day of the year in which the data was collected. Both Chase Farm and Royal Liverpool switched to single rooms during the autumn, so the data for the first data point in the outcome period would actually have been collected during the transition period which may have had an impact on the results.

## Summary of results

```{r}
summary_table_indicators_and_sites(
  LoS_output,
  waiting_time_median_output,
  bed_occupancy_output,
  emergency_readmissions_output,
  cleaning_costs_output,
  sus_deaths_output,
  falls_and_fractures_output,
  cdiff_output,
  friends_and_family_output,
  staff_sickness_output,
  staff_turnover_output,
  staff_survey_output
) 
```

```{r, fig.width=7, fig.height=3.4}
summary_forest_plot(
  LoS_output,
  waiting_time_median_output,
  bed_occupancy_output,
  emergency_readmissions_output,
  cleaning_costs_output,
  sus_deaths_output,
  falls_and_fractures_output,
  cdiff_output,
  friends_and_family_output,
  staff_sickness_output,
  staff_survey_output
)

dataset <- deparse(substitute(staff_survey_output))
```

The impact of switching to single bedrooms appears to vary depending on the hospital site, the switch at Peterborough has generally resulted in positive impacts, while the switch at Clatterbridge has been more negative overall. There are some factors that may be influencing some of the apparent negative impacts at the site, so the results should be interpreted cautiously.

Generally, following a switch to single bedrooms the productivity and efficiency measures are showing positive impacts, apart from at Clatterbridge. The median waiting time does increase at Tunbridge Wells but only during the first year, by on average less than 1 week. It should also be noted that although the date of the switch was set at Jan 2011, when the switch started, the switch was not completed until Sept 2011, so much of the increase in waiting time could be attributed to disruption during the transition period. Although the data is limited it does appear that cleaning costs may increase, which would not be unexpected given an increase in time is likely required to clean separate bedrooms and additional bathrooms.

Switching to single bedrooms appears to have a positive or neutral effect on Health and Safety measures. It could be considered that no change in health and safety measures is a positive effect, as patient safety does not appear to be impacted, which was a concern that has been raised about single bedroom accommodation as patients are potentially less visible to the staff. It is thought single bed accommodation may reduce hospital acquired infections; our data on this is very limited, but there is some evidence to suggest C.Difficile infection rates may decrease.

In terms of patient and staff experiences the switch to single bedrooms generally has negative effect, for staff in particular. For general acute hospitals there was a significant reduction of 15% in the percentage of staff who would recommend their trust as a place to work and a significant increase in staff sickness. Although it should be noted that some of these negative effects are seen primarily in the first year post-switch before returning to expected levels during the second year.

# Limitations and discussion

**Data quality and availability**

Our analyses rely on historical data collections, some of which do not go back as far as 2008 as shown in @fig-avail. There are also gaps/anomalous data in the time series for some providers and potential control sites. How some metrics have been measured is likely to have changed over time, although the causal impact analysis uses control data from sites without interventions which will help to correct for any changes occurring at all sites. Some study sites have been involved in trust mergers/site changes in the time period prior to switching to single bedrooms; we have merged historic data where appropriate, but these mergers may have impacted the time series.

Some variables are only available at provider level (@tbl-avail) so where providers have more than one site any change that may occur following a switch to single bedrooms at one site will be diluted by a lack of change at the other sites at the provider.

Also the variables that we have measured are not always entirely specific to the impact we are trying to measure, for example we are using both staff sickness and staff turnover as a proxy for staff experience, with the assumption that increased staff turnover and sickness absences will indicate that staff are less happy in their workplace following a switch to single bedrooms. It is possible that sickness absences may be influenced in other ways by a switch to single bedrooms for example if single bedrooms reduce outbreaks of the contagious illness and better protect staff from contracting them themselves then sickness absences could be reduced.

Some measures are recorded quarterly or annually so we have less data points with which to fit our models and assess outcomes and less temporal specificity to detect changes.

COVID-19 has impacted many of the variables for sites that switched just before or after the onset of the pandemic (Royal Liverpool, Clatterbridge and Papworth). While the causal impact analysis does use control sites to account for changes over time that would have happened without the intervention, the impact of the COVID-19 was variable between study sites and their controls.

**Model fit and methodology**

Model fit was assessed using the Mean Absolute Percentage Error (MAPE) and Durbin-Watson statistic of the models, and adjustments were made to try to ensure a good historical model fit while minimising the forecasting intervals. However, for some data the models will be a less good fit and will have large credible intervals in the outcome period due to the variability in the indicator not being well explained by the control time series.

Three of the seven study sites were specialist sites (Papworth is a specialist cardiothoracic/transplant centre, Clatterbridge is a cancer centre and Chase Farm only conducts elective care), making it more difficult to select well matched control sites. The number of control sites was very limited for both Clatterbridge (`r number_control_sites |> filter(organisation_code == "REN") |> pull()`) and Papworth (`r number_control_sites |> filter(organisation_code == "RGM") |> pull()`), which may impact the quality of the model fit and reliability of the outcome.

The three specialist provider sites were excluded from the meta-analysis as the impacts on these sites may be less generalisable to new general acute hospitals that may be built in the future. The meta-analyses were weighted based on the inverse variance of the relative effects, but other factors that may influence how much weight should be given to a particular site were not included.

**General**

For our analysis we have had to specify the month in which the switch to single bedrooms occurred. However, at some sites the switch was done over a longer period of time with certain services moving at different stages. For example, Tunbridge Wells moved Women and Children's wards to SBR in January 2011 and the remainder of inpatient services in September 2011. We have used the month when the switch started, so that control site selection and predictions are not affected by changes in the transition period, but this means that we may see initial changes related to the transition period or that some changes may not be seen until later in the outcome period when the full switch had occurred.

When the sites switched to single bedrooms there are likely to have been other changes to how services operate and at multi-site providers there may also have been changes to what services are provided at which sites, so there are likely to be confounding factors that influence our results.

Not all sites switch entirely to single bed rooms, for example, Peterborough in November 2010 introduced SBR alongside three- to four-bedded ward areas [@peterborough_web]. The sites that switched to single bedrooms will have had different designs and the differences in results between sites may be due to different single bedroom designs working better, or worse, than others. It is also possible that the best design may vary by hospital type and a design that suits a general acute hospital may work less well at a specialist site. Where there are potential negative impacts of a switch to single bedrooms some sites may have had mitigating factors in place from the start while at other schemes any mitigating factors may have occurred later.

We see some evidence that the rate of hospital acquired C.Difficile infections may be reduced, but unfortunately it was not possible to assess other healthcare acquired infections (MSSA, MRSA, Klebsiella and P.Aeruginosa) due to a lack of data availability before 2017. In addition, it is possible that the spread of other contagious conditions, such as influenza and COVID-19, may be reduced by single bed rooms, but data on this is not available for analysis.

# Recommendations for modelling and future evaluation

# Appendices

## A. CIA charts by indicator and hospital site/provider {#sec-appendix-A}

### `r title_los`

::: panel-tabset
#### Decrease

```{r, fig.width=5, fig.height=6}
#### Papworth

#COVID-19 spikes in the post switch period are impacting LoS and these are not seen in the controls

#RGM_matches<-single_bedroom_matches_final|>
#  filter(organisation_code=="RGM")

#test<-length_of_stay|>
#  filter(site_code=="RGM22" | (site_code %in% RGM_matches$site_code))

#test|>
#  filter(month>"2015-01-01")|>
#  ggplot()+
#geom_line(aes(x=month, y=avg_los, group=site_code, colour=site_code))+
#  facet_wrap(~site_code)

#LoS_RGM<-tar_read(LoS_RGM)

#evaluating_model("RGM", "RGM22", length_of_stay, "2019-05-01", "avg_los", 0.05, LoS_RGM, single_bedroom_matches_final)

#cia_summary_plots(LoS_RGM, "Average LoS (days)", "2019-05-01")
```

::: columns
::: {.column width="50%"}
Peterborough

```{r, fig.width=5, fig.height=6}
LoS_RGN <- tar_read(LoS_RGN)

#evaluating_model("RGN",  "RGN80", length_of_stay, "2010-11-01","avg_los", 0.01, LoS_RGN, single_bedroom_matches_final)

cia_summary_plots(LoS_RGN, "Average LoS (days)", "2010-11-01")
```

Chase Farm

```{r, fig.width=5, fig.height=6}
LoS_RAL <- tar_read(LoS_RAL)

#evaluating_model("RAL", "RALC7", length_of_stay, "2018-09-01", "avg_los", 0.05, LoS_RAL, single_bedroom_matches_final)

cia_summary_plots(LoS_RAL, "Average LoS (days)", "2018-09-01")
```
:::

::: {.column width="50%"}
Southmead

```{r, fig.width=5, fig.height=6}
LoS_RVJ <- tar_read(LoS_RVJ)

#evaluating_model("RVJ","RVJ01",  length_of_stay, "2014-05-01", "avg_los", 0.01, LoS_RVJ, single_bedroom_matches_final)

cia_summary_plots(LoS_RVJ, "Average LoS (days)", "2014-05-01")
```
:::
:::

#### No change

::: columns
::: {.column width="50%"}
Tunbridge Wells

```{r, fig.width=5, fig.height=6}
LoS_RWF <- tar_read(LoS_RWF)

#evaluating_model("RWF",  "RWFTW", length_of_stay, "2011-01-01", "avg_los", 0.05, LoS_RWF, single_bedroom_matches_final)

cia_summary_plots(LoS_RWF, "Average LoS (days)", "2011-01-01")
```
:::

::: {.column width="50%"}
Royal Liverpool

```{r, fig.width=5, fig.height=6}
LoS_REM <- tar_read(LoS_REM)

#evaluating_model("REM", "REMRQ",  length_of_stay, "2022-10-01", "avg_los", 0.05, LoS_REM, single_bedroom_matches_final)

cia_summary_plots(LoS_REM, "Average LoS (days)", "2022-10-01")
```
:::
:::

#### Increase

::: columns
::: {.column width="50%"}
Clatterbridge

```{r, fig.width=5, fig.height=6}
LoS_REN <- tar_read(LoS_REN)

#evaluating_model("REN", "REN22", length_of_stay, "2020-06-01", "avg_los", 0.1, LoS_REN, single_bedroom_matches_final)

cia_summary_plots(LoS_REN, "Average LoS (days)", "2020-06-01")
```
:::
:::
:::

### `r title_wait_time_median`

::: panel-tabset
#### Decrease

::: columns
::: {.column width="50%"}
Royal Liverpool

```{r, fig.width=5, fig.height=6}
waiting_time_median_REM <- tar_read(waiting_time_median_REM)

#evaluating_model("REM", NA,  rtt_waiting_time, "2022-10-01", "median_by_prov", 0.05, waiting_time_median_REM, single_bedroom_matches_final)

cia_summary_plots(waiting_time_median_REM,
                  "Median waiting time (wks)",
                  "2022-10-01")
```
:::

::: {.column width="50%"}
Peterborough

```{r,  fig.width=5, fig.height=6}
#| label: fig-wait-peterborough
waiting_time_median_RGN <- tar_read(waiting_time_median_RGN)

#evaluating_model("RGN", NA, rtt_waiting_time, "2010-11-01", "median_by_prov", 0.01, waiting_time_median_RGN, single_bedroom_matches_final)

cia_summary_plots(waiting_time_median_RGN,
                  "Median waiting time (wks)",
                  "2010-11-01")
```
:::
:::

#### No change

::: columns
::: {.column width="50%"}
Clatterbridge

```{r, fig.width=5, fig.height=6}
waiting_time_median_REN <- tar_read(waiting_time_median_REN)

#evaluating_model("REN", NA, rtt_waiting_time, "2020-06-01", "median_by_prov", 0.05, waiting_time_median_REN, single_bedroom_matches_final)

cia_summary_plots(waiting_time_median_REN,
                  "Median waiting time (wks)",
                  "2020-06-01")
```
:::

::: {.column width="50%"}
Papworth

```{r, fig.width=5, fig.height=6}
waiting_time_median_RGM <- tar_read(waiting_time_median_RGM)

#evaluating_model("RGM", NA, rtt_waiting_time, "2019-05-01", "median_by_prov", 0.05, waiting_time_median_RGM, single_bedroom_matches_final)

cia_summary_plots(waiting_time_median_RGM,
                  "Median waiting time (wks)",
                  "2019-05-01")
```
:::

```{r, fig.width=5, fig.height=6}
#### Chase Farm
# waiting_time_median_RAL <- tar_read(waiting_time_median_RAL)
# 
# evaluating_model("RAL", NA, rtt_waiting_time, "2018-09-01", "median_by_prov", 0.01, waiting_time_median_RAL, single_bedroom_matches_final)
#
# cia_summary_plots(
#   waiting_time_median_RAL,
#   "Study site: Chase Farm, RAL",
#   "Median waiting time (wks)",
#   "2018-09-01"
# )
```

```{r, fig.width=5, fig.height=6}
#### Southmead
# waiting_time_median_RVJ <- tar_read(waiting_time_median_RVJ)
# 
# evaluating_model(
#   "RVJ",
#   NA,
#   rtt_waiting_time,
#   "2014-05-01",
#   "median_by_prov",
#   0.1,
#   waiting_time_median_RVJ,
#   single_bedroom_matches_final
# )
# 
# cia_summary_plots(waiting_time_median_RVJ,
#                   "Median waiting time (wks)",
#                   "2014-05-01")
```
:::

#### Increase

::: columns
::: {.column width="50%"}
Tunbridge Wells

```{r, fig.width=5, fig.height=6}
#| label: fig-wait-tunbridge
waiting_time_median_RWF <- tar_read(waiting_time_median_RWF)

#evaluating_model("RWF", NA, rtt_waiting_time, "2011-01-01", "median_by_prov", 0.01, waiting_time_median_RWF, single_bedroom_matches_final)

cia_summary_plots(waiting_time_median_RWF,
                  "Median waiting time (wks)",
                  "2011-01-01")
```
:::
:::
:::

### `r title_bed_occup`

::: panel-tabset
#### No change

::: columns
::: {.column width="50%"}
Chase Farm

```{r, fig.width=5, fig.height=6}
bed_occupancy_RAL <- tar_read(bed_occupancy_RAL)

#evaluating_model("RAL",NA,  bed_occupancy, "2018-09-01", "bed_occupancy", 0.1, bed_occupancy_RAL, single_bedroom_matches_final)

cia_summary_plots(bed_occupancy_RAL, "Percentage", "2018-09-01")
```
:::

::: {.column width="50%"}
Royal Liverpool

```{r,  fig.width=5, fig.height=6}
bed_occupancy_REM <- tar_read(bed_occupancy_REM)

#evaluating_model("REM", NA, bed_occupancy, "2022-10-01", "bed_occupancy", 0.05, bed_occupancy_REM, single_bedroom_matches_final)

cia_summary_plots(bed_occupancy_REM, "Percentage", "2022-10-01")
```
:::
:::

#### Increase

::: columns
::: {.column width="50%"}
Clatterbridge

```{r,  fig.width=5, fig.height=6}
bed_occupancy_REN <- tar_read(bed_occupancy_REN)

#evaluating_model("REN", NA, bed_occupancy, "2020-06-01", "bed_occupancy", 0.1, bed_occupancy_REN, single_bedroom_matches_final)

cia_summary_plots(bed_occupancy_REN, "Percentage", "2020-06-01")
```
:::

::: {.column width="50%"}
Southmead

```{r, fig.width=5, fig.height=6}
bed_occupancy_RVJ <- tar_read(bed_occupancy_RVJ)

#evaluating_model("RVJ", NA, bed_occupancy, "2014-05-01", "bed_occupancy", 0.1, bed_occupancy_RVJ, single_bedroom_matches_final)

cia_summary_plots(bed_occupancy_RVJ, "Percentage", "2014-05-01")
```
:::
:::

Black dotted line indicates the time of the last data point prior to the switch to single bedrooms
:::

### `r title_readmissions`

::: panel-tabset
#### Decrease

::: columns
::: {.column width="50%"}
Clatterbridge

```{r, fig.width=5, fig.height=6}
emergency_readmissions_REN <- tar_read(emergency_readmissions_REN)

#evaluating_model("REN", "REN22", emergency_readmissions, "2020-06-01","perc", 0.1, emergency_readmissions_REN, single_bedroom_matches_final)

cia_summary_plots(emergency_readmissions_REN, "% readmissions", "2020-06-01")
```

Peterborough

```{r, fig.width=5, fig.height=6}
emergency_readmissions_RGN <- tar_read(emergency_readmissions_RGN)

#evaluating_model("RGN",  "RGN80", emergency_readmissions, "2010-11-01","perc", 0.1, emergency_readmissions_RGN, single_bedroom_matches_final)

cia_summary_plots(emergency_readmissions_RGN, "% readmissions", "2010-11-01")
```
:::

::: {.column width="50%"}
Tunbridge Wells

```{r, fig.width=5, fig.height=6}
emergency_readmissions_RWF <- tar_read(emergency_readmissions_RWF)

#evaluating_model("RWF",  "RWFTW", emergency_readmissions, "2011-01-01", "perc", 0.01, emergency_readmissions_RWF, single_bedroom_matches_final)

cia_summary_plots(emergency_readmissions_RWF, "% readmissions", "2011-01-01")
```
:::
:::

#### No change

::: columns
::: {.column width="50%"}
Royal Liverpool

```{r, fig.width=5, fig.height=6}
emergency_readmissions_REM <- tar_read(emergency_readmissions_REM)

#evaluating_model("REM", "REMRQ",  emergency_readmissions, "2022-10-01", "perc", 0.1, emergency_readmissions_REM, single_bedroom_matches_final)

cia_summary_plots(emergency_readmissions_REM, "% readmissions", "2022-10-01")
```

Papworth

```{r, fig.width=5, fig.height=6}
emergency_readmissions_RGM <- tar_read(emergency_readmissions_RGM)

#evaluating_model("RGM", "RGM22", emergency_readmissions, "2019-05-01", "perc", 0.1, emergency_readmissions_RGM, single_bedroom_matches_final)

cia_summary_plots(emergency_readmissions_RGM, "% readmissions", "2019-05-01")
```
:::

::: {.column width="50%"}
Chase Farm

```{r,  fig.width=5, fig.height=6}
emergency_readmissions_RAL <- tar_read(emergency_readmissions_RAL)

#evaluating_model("RAL", "RALC7", emergency_readmissions, "2018-09-01", "perc", 0.01, emergency_readmissions_RAL, single_bedroom_matches_final)

cia_summary_plots(emergency_readmissions_RAL, "% readmissions", "2018-09-01")
```

Southmead

```{r, fig.width=5, fig.height=6}
emergency_readmissions_RVJ <- tar_read(emergency_readmissions_RVJ)

#evaluating_model("RVJ","RVJ01",  emergency_readmissions, "2014-05-01","perc", 0.05, emergency_readmissions_RVJ, single_bedroom_matches_final)

cia_summary_plots(emergency_readmissions_RVJ, "% readmissions", "2014-05-01")
```
:::
:::
:::

### `r title_cleaning`

::: panel-tabset
#### Decrease

::: columns
::: {.column width="50%"}
Papworth (RGM)

```{r, fig.width=5, fig.height=6}
cleaning_costs_RGM <- tar_read(cleaning_costs_RGM)

#evaluating_model("RGM", "RGM22",cleaning_costs,"2019-05-01","cleaning_service_cost", 0.01, cleaning_costs_RGM, single_bedroom_matches_final)

cia_summary_plots(cleaning_costs_RGM, "Cost", "2019-05-01")
```

```{r, fig.width=5, fig.height=6}
#Chase Farm (RAL)

#cleaning_costs_RAL<-tar_read(cleaning_costs_RAL)
  
#evaluating_model("RAL", "RALC7",cleaning_costs,"2018-09-01","cleaning_service_cost", 0.01, cleaning_costs_RAL, single_bedroom_matches_final)

#cia_summary_plots( cleaning_costs_RAL, "Cost", "2018-09-01")
```
:::

::: {.column width="50%"}
Clatterbridge (REN)

```{r,  fig.width=5, fig.height=6}
cleaning_costs_REN <- tar_read(cleaning_costs_REN)

#evaluating_model("REN", "REN22",cleaning_costs,"2020-06-01", "cleaning_service_cost", 0.01, cleaning_costs_REN, single_bedroom_matches_final)

cia_summary_plots(cleaning_costs_REN, "Cost", "2020-06-01")
```
:::
:::

Black dotted line indicates the time of the last data point prior to the switch to single bedrooms

#### Increase

::: columns
::: {.column width="50%"}
Royal Liverpool (REM)

```{r, fig.width=5, fig.height=6}
cleaning_costs_REM <- tar_read(cleaning_costs_REM)

#evaluating_model("REM","REMRQ",cleaning_costs,"2022-10-01", "cleaning_service_cost", 0.01, cleaning_costs_REM, single_bedroom_matches_final)

cia_summary_plots(cleaning_costs_REM, "Cost", "2022-10-01")
```
:::
:::

Black dotted line indicates the time of the last data point prior to the switch to single bedrooms
:::

### `r title_deaths`

::: panel-tabset
#### Decrease

::: columns
::: {.column width="50%"}
Peterborough

```{r, fig.width=5, fig.height=6}
sus_deaths_RGN <- tar_read(sus_deaths_RGN)

#evaluating_model("RGN",  "RGN80", sus_deaths, "2010-11-01","hosp_rate_1000", 0.1, sus_deaths_RGN, single_bedroom_matches_final)

cia_summary_plots(sus_deaths_RGN, "No./per 1,000 discharges", "2010-11-01")
```
:::

::: {.column width="50%"}
:::
:::

#### No change

::: columns
::: {.column width="50%"}
Royal Liverpool

```{r,  fig.width=5, fig.height=6}
sus_deaths_REM <- tar_read(sus_deaths_REM)

#evaluating_model("REM", "REMRQ",  sus_deaths, "2022-10-01", "hosp_rate_1000", 0.05, sus_deaths_REM, single_bedroom_matches_final)

cia_summary_plots(sus_deaths_REM, "No./per 1,000 discharges", "2022-10-01")
```

```{r, include=FALSE}
sapply(file.path(tempdir(), list.files(tempdir())), unlink)
```

Tunbridge Wells

```{r, fig.width=5, fig.height=6}
sus_deaths_RWF <- tar_read(sus_deaths_RWF)

#evaluating_model("RWF",  "RWFTW", sus_deaths, "2011-01-01", "hosp_rate_1000", 0.01, sus_deaths_RWF, single_bedroom_matches_final)

cia_summary_plots(sus_deaths_RWF, "No./per 1,000 discharges", "2011-01-01")
```
:::

::: {.column width="50%"}
Southmead

```{r,  fig.width=5, fig.height=6}
sus_deaths_RVJ <- tar_read(sus_deaths_RVJ)

#evaluating_model("RVJ","RVJ01",  sus_deaths, "2014-05-01","hosp_rate_1000", 0.01, sus_deaths_RVJ, single_bedroom_matches_final)

cia_summary_plots(sus_deaths_RVJ, "No./per 1,000 discharges", "2014-05-01")
```

Clatterbridge

```{r,  fig.width=5, fig.height=6}
sus_deaths_REN <- tar_read(sus_deaths_REN)

#evaluating_model("REN", "REN22", sus_deaths, "2020-06-01","hosp_rate_1000", 0.05, sus_deaths_REN, single_bedroom_matches_final )

cia_summary_plots(sus_deaths_REN, "No./per 1,000 discharges", "2020-06-01")
```
:::
:::
:::

### `r title_falls_fractures`

::: panel-tabset
#### Decrease

Peterborough

```{r, fig.width=5, fig.height=6}
falls_and_fractures_RGN <- tar_read(falls_and_fractures_RGN)

#evaluating_model("RGN",  "RGN80",falls_and_fractures, "2010-11-01","ff_rate", 0.01, falls_and_fractures_RGN, single_bedroom_matches_final)

cia_summary_plots(falls_and_fractures_RGN, "% of spells", "2010-11-01")
```

#### No change

::: columns
::: {.column width="50%"}
Royal Liverpool

```{r, fig.width=5, fig.height=6}
falls_and_fractures_REM <- tar_read(falls_and_fractures_REM)

#evaluating_model("REM", "REMRQ",  falls_and_fractures, "2022-10-01", "ff_rate", 0.05, falls_and_fractures_REM, single_bedroom_matches_final)

cia_summary_plots(falls_and_fractures_REM, "% of spells", "2022-10-01")
```

Southmead

```{r,  fig.width=5, fig.height=6}
falls_and_fractures_RVJ <- tar_read(falls_and_fractures_RVJ)

#evaluating_model("RVJ","RVJ01",  falls_and_fractures, "2014-05-01","ff_rate", 0.05, falls_and_fractures_RVJ, single_bedroom_matches_final)

cia_summary_plots(falls_and_fractures_RVJ, "% of spells", "2014-05-01")
```

Outcome period is cut short as the rate of falls and fractures at Southmead jumps suddenly in the second year of the outcome period (Nov 2015); this change does not appear to be associated with the change to single rooms as it occurs suddenly almost 18 months after the change to single rooms.
:::

::: {.column width="50%"}
Tunbridge Wells

```{r, fig.width=5, fig.height=6}
falls_and_fractures_RWF <- tar_read(falls_and_fractures_RWF)

#evaluating_model("RWF",  "RWFTW", falls_and_fractures, "2011-01-01", "ff_rate", 0.05, falls_and_fractures_RWF, single_bedroom_matches_final)

cia_summary_plots(falls_and_fractures_RWF, "% of spells", "2011-01-01")
```
:::
:::
:::

### `r title_cdiff`

#### Decrease

Chase Farm

```{r, fig.width=5, fig.height=6}
cdiff_RAL <- tar_read(cdiff_RAL)

#evaluating_model("RAL", NA, cdiff, "2018-09-01", "rate", 0.1, cdiff_RAL, single_bedroom_matches_final)

cia_summary_plots(cdiff_RAL, "Rate/10,000 beddays", "2018-09-01")
```

Southmead

```{r, fig.width=5, fig.height=6}
cdiff_RVJ <- tar_read(cdiff_RVJ)

evaluating_model("RVJ",
                 NA,
                 cdiff,
                 "2014-05-01",
                 "rate",
                 0.1,
                 cdiff_RVJ,
                 single_bedroom_matches_final)

cia_summary_plots(cdiff_RVJ, "Rate/10,000 beddays", "2014-05-01")
```

#### No change

Royal Liverpool

```{r, fig.width=5, fig.height=6}
cdiff_REM <- tar_read(cdiff_REM)

#evaluating_model("REM", NA, cdiff, "2022-10-01", "rate", 0.1, cdiff_REM, single_bedroom_matches_final)

cia_summary_plots(cdiff_REM, "Rate/10,000 beddays", "2022-10-01")
```

```{r, include=FALSE, fig.width=5, fig.height=6}
hcai_REN <- tar_read(hcai_REN)

#evaluating_model("REN", NA, hcai, "2020-06-01", "combined_rate", 0.01, hcai_REN, single_bedroom_matches_final)

cia_summary_plots(hcai_REN, "Rate/10,000 beddays", "2022-10-01")
```

### `r title_friends_family`

::: panel-tabset
#### Decrease

Clatterbridge (REN)

```{r, fig.width=5, fig.height=6}
friends_and_family_REN <- tar_read(friends_and_family_REN)

#evaluating_model("REN","REN22", friends_and_family,"2020-06-01", "friends_and_family_percent", 0.1, friends_and_family_REN, single_bedroom_matches_final )

cia_summary_plots(friends_and_family_REN, "Positive responses (%)", "2020-06-01")

#Last data point prior to switch was about 4 months prior then no data for 8 months after, as switch came during COVID
```

#### No Change

::: columns
::: {.column width="50%"}
Royal Liverpool (REMRQ)

```{r, fig.width=5,fig.height=6 }
friends_and_family_REM <- tar_read(friends_and_family_REM)

#evaluating_model("REM","REMRQ", friends_and_family,"2022-10-01", "friends_and_family_percent", 0.1, friends_and_family_REM, single_bedroom_matches_final)

cia_summary_plots(friends_and_family_REM, "Positive responses (%)", "2022-10-01")

# Large amount of data missing in the two years prior due to gap over covid. One of the control sites doesn't go back far enough for it is causing the data to be cut off. Think I need to have less matches for this one. But would still have a disturbed pre switch period due to COVID
```

Papworth (RGM)

```{r, fig.width=5, fig.height=6}
friends_and_family_RGM <- tar_read(friends_and_family_RGM)

#evaluating_model("RGM", "RGM22", friends_and_family,"2019-05-01", "friends_and_family_percent", 0.1, friends_and_family_RGM, single_bedroom_matches_final)

cia_summary_plots(friends_and_family_RGM, "Positive responses (%)", "2019-05-01")
```
:::

::: {.column width="50%"}
Chase Farm Hospital (RAL)

```{r, fig.width=5, fig.height=6}
friends_and_family_RAL <- tar_read(friends_and_family_RAL)

#evaluating_model("RAL","RALC7",  friends_and_family,"2018-09-01", "friends_and_family_percent", 0.01, friends_and_family_RAL, single_bedroom_matches_final)

cia_summary_plots(friends_and_family_RAL, "Positive responses (%)", "2018-09-01")
```

Southmead (RVJ)

```{r, fig.width=5, fig.height=6}
friends_and_family_RVJ <- tar_read(friends_and_family_RVJ)

#evaluating_model("RVJ","RVJ01",  friends_and_family,"2014-05-01", "friends_and_family_percent", 0.01, friends_and_family_RVJ, single_bedroom_matches_final)

cia_summary_plots(friends_and_family_RVJ, "Positive responses (%)", "2014-05-01")
```
:::
:::
:::

### `r title_staff_sickness`

::: panel-tabset
#### Increase

::: columns
::: {.column width="50%"}
Southmead (RVJ)

```{r, fig.width=5, fig.height=6}
staff_sickness_RVJ <- tar_read(staff_sickness_RVJ)

#evaluating_model("RVJ", NA,staff_sickness,"2014-05-01", "staff_sickness_percent", 0.05, staff_sickness_RVJ, single_bedroom_matches_final)

cia_summary_plots(staff_sickness_RVJ, "Sickness Rate (%)", "2014-05-01")
```
:::

::: {.column width="50%"}
Tunbridge Wells (RWF)

```{r, fig.width=5, fig.height=6}
staff_sickness_RWF <- tar_read(staff_sickness_RWF)

#evaluating_model("RWF", NA,staff_sickness,"2011-01-01", "staff_sickness_percent", 0.1,staff_sickness_RWF, single_bedroom_matches_final )

cia_summary_plots(staff_sickness_RWF, "Sickness Rate (%)", "2011-01-01")
```
:::
:::

#### No change

::: columns
::: {.column width="50%"}
Royal Liverpool (REM)

```{r, fig.height=6, fig.width=5}
staff_sickness_REM <- tar_read(staff_sickness_REM)

#evaluating_model("REM",NA, staff_sickness,"2022-10-01", "staff_sickness_percent", 0.05, staff_sickness_REM, single_bedroom_matches_final)

cia_summary_plots(staff_sickness_REM, "Sickness Rate (%)", "2022-10-01")
```

Clatterbridge (REN)

```{r, fig.width=5, fig.height=6}
staff_sickness_REN <- tar_read(staff_sickness_REN)

#evaluating_model("REN", NA,staff_sickness,"2020-06-01", "staff_sickness_percent", 0.05,staff_sickness_REN, single_bedroom_matches_final )

cia_summary_plots(staff_sickness_REN, "Sickness Rate (%)", "2020-06-01")
```

Peterborough (RGN)

```{r, fig.width=5, fig.height=6}
staff_sickness_RGN <- tar_read(staff_sickness_RGN)

#evaluating_model("RGN", NA,staff_sickness,"2010-11-01", "staff_sickness_percent", 0.1,staff_sickness_RGN, single_bedroom_matches_final )

cia_summary_plots(staff_sickness_RGN, "Sickness Rate (%)", "2010-11-01")
```
:::

::: {.column width="50%"}
Papworth (RGM)

```{r, fig.width=5, fig.height=6}
staff_sickness_RGM <- tar_read(staff_sickness_RGM)

#evaluating_model("RGM", NA,staff_sickness,"2019-05-01", "staff_sickness_percent", 0.05, staff_sickness_RGM, single_bedroom_matches_final)

cia_summary_plots(staff_sickness_RGM, "Sickness Rate (%)", "2019-05-01")
```

Chase Farm Hospital (RAL)

```{r,  fig.width=5, fig.height=6}
staff_sickness_RAL <- tar_read(staff_sickness_RAL)

#evaluating_model("RAL", NA, staff_sickness,"2018-09-01", "staff_sickness_percent", 0.05, staff_sickness_RAL, single_bedroom_matches_final)

cia_summary_plots(staff_sickness_RAL, "Sickness Rate (%)", "2018-09-01")
```
:::
:::
:::

### `r title_staff_turnover`

#### No change

::: columns
::: {.column width="50%"}
Royal Liverpool (REM)

```{r, fig.width=5, fig.height=6}
staff_turnover_REM <- tar_read(staff_turnover_REM)

#evaluating_model("REM", NA,staff_turnover,"2022-10-01", "leaving_rate", 0.1, staff_turnover_REM, single_bedroom_matches_final)

cia_summary_plots(staff_turnover_REM, "Staff leaving rate (%)", "2022-10-01")
```

Papworth (RGM)

```{r, fig.width=5, fig.height=6}
staff_turnover_RGM <- tar_read(staff_turnover_RGM)

#evaluating_model("RGM", NA,staff_turnover,"2019-05-01", "leaving_rate", 0.01, staff_turnover_RGM, single_bedroom_matches_final)

cia_summary_plots(staff_turnover_RGM, "Staff leaving rate (%)", "2019-05-01")
```
:::

::: {.column width="50%"}
Clatterbridge (REN)

```{r, fig.width=5, fig.height=6}
staff_turnover_REN <- tar_read(staff_turnover_REN)

#evaluating_model("REN", NA,staff_turnover,"2020-06-01", "leaving_rate", 0.1, staff_turnover_REN, single_bedroom_matches_final)

cia_summary_plots(staff_turnover_RGM, "Staff leaving rate (%)", "2020-06-01")
```
:::
:::

### `r title_staff_survey`

```{r, include=FALSE}
Peterborough_matches <- single_bedroom_matches_final |>
  filter(organisation_code == "RGN") |>
  filter(rank_of_ranks <= 10)

Peterborough_analysis <- staff_survey |>
  filter(organisation_code == "RGN" |
           (
             organisation_code %in% (Peterborough_matches$matching_organisation_code)
           ))

Peterborough_analysis |>
  filter(
    organisation_code == "RGN" |
      organisation_code == "RXH" |
      organisation_code == "RJR" |
      organisation_code == "RXN" |
      organisation_code == "RXK" |
      organisation_code == "RPA"
  ) |>
  ggplot() +
  geom_line(
    aes(
      x = month,
      y = positive_responses,
      group = organisation_code,
      colour = organisation_code
    )
  ) +
  geom_vline(
    aes(xintercept = as.Date('2010-11-01')),
    linetype = "dotted",
    linewidth = 0.6,
    color = "#ec6555"
  )


Peterborough_analysis |>
  filter(
    organisation_code == "RGN" |
      organisation_code == "RXH" |
      organisation_code == "RJR" |
      organisation_code == "RXN" |
      organisation_code == "RXK" |
      organisation_code == "RPA"
  ) |>
  filter(month == '2009-12-31' | month == '2012-12-31') |>
  spread(key = month, value = positive_responses) |>
  mutate(change = (((`2012-12-31` - `2009-12-31`) / `2009-12-31`
  ) * 100))
```

::: panel-tabset
#### Decrease

::: columns
::: {.column width="50%"}
Clatterbridge (REN)

```{r,  fig.width=5, fig.height=6}
staff_survey_REN <- tar_read(staff_survey_REN)

#evaluating_model("REN", NA,staff_survey,"2020-06-01", "positive_responses", 0.01, staff_survey_REN, single_bedroom_matches_final)

cia_summary_plots(staff_survey_REN, "Positive Responses (%)", "2020-06-01")
```
:::

::: {.column width="50%"}
Southmead (RVJ)

```{r, fig.width=5, fig.height=6}
staff_survey_RVJ <- tar_read(staff_survey_RVJ)

#evaluating_model("RVJ", NA,staff_survey,"2014-05-01", "positive_responses", 0.01, staff_survey_RVJ, single_bedroom_matches_final)

cia_summary_plots(staff_survey_RVJ, "Positive Responses (%)", "2014-05-01")
```
:::

Black dotted line indicates the time of the last data point prior to the switch to single bedrooms
:::

#### No change

::: columns
::: {.column width="50%"}
Royal Liverpool (REM)

```{r, fig.width=5, fig.height=6}
staff_survey_REM <- tar_read(staff_survey_REM)

#evaluating_model("REM", NA,staff_survey,"2022-10-01", "positive_responses", 0.01, staff_survey_REM, single_bedroom_matches_final)

cia_summary_plots(staff_survey_REM, "Positive Responses (%)", "2022-10-01")
```

Tunbridge Wells (RWF)

```{r, fig.width=5, fig.height=6}
staff_survey_RWF <- tar_read(staff_survey_RWF)

#evaluating_model("RWF", NA,staff_survey,"2011-01-01", "positive_responses", 0.001, staff_survey_RWF, single_bedroom_matches_final)

cia_summary_plots(staff_survey_RWF, "Positive Responses (%)", "2011-01-01")
```

For Tunbridge Wells due to the limited data the controls have been matched using purely correlation rather than dynamic time warping.
:::

::: {.column width="50%"}
Chase Farm (RAL)

```{r,  fig.width=5, fig.height=6}
staff_survey_RAL <- tar_read(staff_survey_RAL)

#evaluating_model("RAL", NA,staff_survey,"2018-09-01", "positive_responses", 0.01, staff_survey_RAL, single_bedroom_matches_final)

cia_summary_plots(staff_survey_RAL, "Positive Responses (%)", "2018-09-01")
```
:::
:::

Black dotted line indicates the time of the last data point prior to the switch to single bedrooms

#### Increase

::: columns
::: {.column width="50%"}
Papworth (RGM)

```{r, fig.width=5, fig.height=6}
staff_survey_RGM <- tar_read(staff_survey_RGM)

#evaluating_model("RGM", NA,staff_survey,"2019-05-01", "positive_responses", 0.01, staff_survey_RGM, single_bedroom_matches_final)

cia_summary_plots(staff_survey_RGM, "Positive Responses (%)", "2019-05-01")
```
:::
:::

Black dotted line indicates the time of the last data point prior to the switch to single bedrooms
:::

## B. Notes on data quality and suitability (for CIA) {#sec-appendix-B}

**RTT waiting time data**

-   Only available at provider level
-   Chase Farm was excluded as there was only 4 months of data available in the outcome period.
-   Southmead was excluded due to a period of missing data in the 2 years prior to the switch to single rooms.

**`r title_los`**

-   Papworth was excluded as there were 2 large COVID-19 related spikes in length of stay in the outcome period that were significantly larger than the COVID-19 effects in the control sites, so it was not possible to determine if there would have been a change in length of stay without COVID-19 and thus this data has been excluded from the analysis.

**`r title_bed_occup`**

-   Only available at provider level
-   This is a quarterly measure so there is more limited data and depending on the time point at which the switch to single bedrooms occurred the may be no data until 3 months after the switch or the last point of baseline may be 3 months prior to the switch.
-   For Papworth bed occupancy was highly affected by COVID-19 in the outcome period, an effect which was not seen to the same extent at the control sites, so it wasn't possible to determine whether there would have an effect on bed occupancy had COVID-19 not occurred.

**`r title_cleaning`**

-   This is an annual measure, so there are limited data points in the pre-switch period and only 1 or 2 points in the outcome period.
-   For Chase Farm the cleaning costs were quite variable and it was difficult to find appropriate controls, so we were not able to fit a suitable model.

**Healthcare acquired infections**

-   Only available at provider level
-   C.Difficile infection rates could not be analysed for Clatterbridge or Papworth as the rates were low, often zero, and so combined with the high level of variability in the data it meant it was not possible to fit a suitable model for these sites.

**`r title_falls_fractures`**

-   Clatterbridge, Papworth and Chase Farm were all excluded as the rates were very low, often zero, so it wasn't possible to fit suitable models to the data.

**`r title_deaths`**

-   Papworth was excluded due to a large COVID-19 spike in the outcome period that was greater than that seen in the control sites, so it was not possible to determine if there would have been a change had COVID-19 not occurred.
-   Chase Farm was excluded as the rate was very low, often zero, so it wasn't possible to fit a suitable model, this low rate is unsurprising given it is only conducting elective care.

**Patient experience**

-   There is around a year of missing Friends and Family Test data for all sites during the COVID-19 pandemic (March 2020 until late 2020/early 2021), this means that there is some missing data in the baseline period for Royal Liverpool and some missing data in the outcome periods for Clatterbridge, Papworth and Chase Farm.

**`r title_staff_sickness`**

-   Only available at provider level

**`r title_staff_turnover`**

-   Only available at provider level
-   Data is only available for Royal Liverpool

**`r title_staff_survey`**

-   Only available at provider level
-   This is an annual measure, so there are limited data points in the pre-switch period and only 1 or 2 points in the outcome period.

## C. Control pools for each intervention site {#sec-appendix-C}

As outlined in @sec-methods-controls, there was a multi-phase control selection process to create a pool of control sites for each intervention site for further analysis. The most similar control sites for each intervention site are shown below. Note that, whilst controls will always be selected from within these sets, the exact controls will not be the same for every indicator as the CIA approach further refines matches based on similar pre-intervention time series.

::: panel-tabset
### Royal Liverpool

```{r royal_liverpool_map}
tar_read(map_REM)
```

```{r royal_liverpool_controls_table}
tar_read(controls_table_REM)
```

### Clatterbridge

```{r clatterbridge_map}
tar_read(map_REN)
```

```{r clatterbridge_controls_table}
tar_read(controls_table_REN)
```

### Royal Papworth

```{r royal_papworth_map}
tar_read(map_RGM)
```

```{r royal_papworth_controls_table}
tar_read(controls_table_RGM)
```

### Peterborough

```{r peterborough_map}
tar_read(map_RGN)
```

```{r peterborough_controls_table}
tar_read(controls_table_RGN)
```

### Chase Farm

```{r chase_farm_map}
tar_read(map_RAL)
```

```{r chase_farm_controls_table}
tar_read(controls_table_RAL)
```

### Southmead

```{r southmead_map}
tar_read(map_RVJ)
```

```{r southmead_controls_table}
tar_read(controls_table_RVJ)
```

### Tunbridge Wells

```{r tunbridge_wells_map}
tar_read(map_RWF)
```

```{r tunbridge_wells_controls_table}
tar_read(controls_table_RWF)
```
:::

## D. List of control sites/providers by indicator {#sec-appendix-D}

A different set of controls was identified by `MarketMatching` for each indicator and each intervention hospital for the CIA (@sec-methods-cia). A full list of the sites or providers used in each CIA is available below for each indicator and intervention hospital.

::: panel-tabset
### `r title_los`

```{r LoS_controls}
get_market_matched_controls_table_site(hospitals, 
                                       controls, 
                                       "LoS"                                       )
```

### `r title_wait_time_median`

```{r waiting_time_median}
get_market_matched_controls_table_provider(hospitals,
                                           controls,
                                           "waiting_time_median")
```

### `r title_wait_time_number`

```{r waiting_time_number_controls}
get_market_matched_controls_table_provider(hospitals, 
                                           controls, 
                                           "waiting_time_number")
```

### `r title_bed_occup`

```{r bed_occupancy_controls}
get_market_matched_controls_table_provider(hospitals, 
                                           controls, 
                                           "bed_occupancy")
```

### `r title_readmissions`

```{r emergency_readmissions_controls}
get_market_matched_controls_table_site(hospitals, 
                                       controls, 
                                       "emergency_readmissions")
```

### `r title_cleaning`

```{r cleaning_costs_controls}
get_market_matched_controls_table_site(hospitals, 
                                       controls, 
                                       "cleaning_costs")
```

### `r title_deaths`

```{r sus_deaths_controls}
get_market_matched_controls_table_site(hospitals, 
                                       controls, 
                                       "sus_deaths")
```

### `r title_falls_fractures`

```{r falls_and_fractures_controls}
get_market_matched_controls_table_site(hospitals, 
                                       controls, 
                                       "falls_and_fractures")
```

### `r title_hcai`

```{r hcai_controls}
get_market_matched_controls_table_provider(hospitals, 
                                           controls, 
                                           "hcai")
```

### `r title_cdiff`

```{r cdiff_controls}
get_market_matched_controls_table_provider(hospitals, 
                                           controls, 
                                           "cdiff")
```

### `r title_friends_family`

```{r friends_and_family_controls}
get_market_matched_controls_table_site(hospitals, 
                                       controls, 
                                       "friends_and_family")
```

### `r title_staff_sickness`

```{r staff_sickness_controls}
get_market_matched_controls_table_provider(hospitals, 
                                           controls, 
                                           "staff_sickness")
```

### `r title_staff_turnover`

```{r staff_turnover_controls}
get_market_matched_controls_table_provider(hospitals, 
                                           controls, 
                                           "staff_turnover")
```

### `r title_staff_survey`

```{r staff_survey_controls}
get_market_matched_controls_table_provider(hospitals, 
                                           controls, 
                                           "staff_survey")
```
:::

## E. Provider and site codes? {#sec-appendix-E}

------------------------------------------------------------------------
