---
title: "Measuring the impact of Single Bed Rooms: Causal Impact Analysis"
editor: visual
execute:
  echo: false
  message: false
  warning: false
  cache: false
lang: en-GB
authors: Andrew Hood, Sarah Lucas and Anya Ferguson
date: last-modified
date-format: "YYYY-MM-DD"
title-block-banner: "#f9bf07"
title-block-banner-color: "#333739"
format:
  html:
    embed-resources: true
    smooth-scroll: true
    theme: cosmo
    fontcolor: black
    toc: true
    toc-location: left
    toc-title: Summary
    toc-depth: 3
    grid:
      sidebar-width: 250px
      body-width: 1050px
      margin-width: 0px
      gutter-width: 1.5rem
css: styles.css

bibliography: references.bib
---

```{r, include=FALSE}

library(tidyverse)
library(MarketMatching)
library(tsibble)
library(targets)
library(janitor)
library(readxl)
library(zoo)
library(lubridate)
library(ggrepel)
library(flextable)
library(egg)
library(StrategyUnitTheme)
library(patchwork)
library(metafor)
library(bayesmeta)
library(DiagrammeR)

## RTT waiting time
rtt_waiting_time<-tar_read(rtt_waiting_time_cia_format) 

## Bed occupancy
bed_occupancy<-tar_read(bed_occupancy_cia_format)

## Length of Stay
length_of_stay<- tar_read(length_of_stay_cia_format)

## Emergency readmissions
emergency_readmissions<-tar_read(emergency_readmissions_cia_format)

## Friends & Family
friends_and_family<-tar_read(friends_and_family_cia_format)

## Staff turnover
staff_turnover<-tar_read(staff_turnover_cia_format)

## Staff sickness
staff_sickness<-tar_read(staff_sickness_cia_format)

## Healthcare acquired infections - Infection rate per 10,000 bed days
hcai<-tar_read(hcai_cia_format)

## In-hospital Falls and Fractures - Fall rate per 1000 bed days
falls_and_fractures<- tar_read(falls_and_fractures_cia_format)

# SUS death rate (deaths/1000 admissions)
sus_deaths<- tar_read(sus_deaths_cia_format)

#Staff survey
staff_survey<-tar_read(staff_survey_cia_format)

# Cleaning costs
cleaning_costs<-tar_read(cleaning_costs_cia_format)

#Loading control data
single_bedroom_matches_final<-tar_read(single_bedroom_matches_final)

#Model outputs
waiting_time_median_output<-tar_read(waiting_time_median_output)
waiting_time_number_output<-tar_read(waiting_time_number_output)
LoS_output<-tar_read(LoS_output)
emergency_readmissions_output<-tar_read(emergency_readmissions_output)
bed_occupancy_output<-tar_read(bed_occupancy_output)
hcai_output<-tar_read(hcai_output)
falls_and_fractures_output<-tar_read(falls_and_fractures_output)
sus_deaths_output<-tar_read(sus_deaths_output)
friends_and_family_output<-tar_read(friends_and_family_output)
staff_sickness_output<-tar_read(staff_sickness_output)
staff_turnover_output<-tar_read(staff_turnover_output)
staff_survey_output<-tar_read(staff_survey_output)
cleaning_costs_output<-tar_read(cleaning_costs_output)

source("R/CIA_Functions.R")
source("R/plot_functions.R")
```

```{r, include=FALSE, fig.height=6, fig.width=10}

#LoS_output_test<-tar_read(LoS_output)|>
#filter(!is.na(site))|>
#  mutate(group=ifelse(site %in% c("Royal Liverpool", "Tunbridge Wells", "Southmead", "Peterborough"), "DGH", #"Specialist" ))

#LoS_output_DGH<-LoS_output_test|>
#  filter(group=="DGH")

#test<-rma.uni(yi=RelEffect, vi=(RelEffect.sd)^2, method="REML", data=LoS_output_DGH)
#forest(test)

#test2<-rma.mv(RelEffect, (RelEffect.sd)^2,  mod=~group, method="REML", data=LoS_output_test)
#forest(test2)

#res <- rma.mv(RelEffect, (RelEffect.sd)^2,  random = ~ 1 | group/site,  data=LoS_output_test)
#forest(res)
```

# Foreword??

Ask Cheryl / Eammon to write...otherwise omit.

# Introduction and background

Taken from initial plan and NHP update slides.

\<<include overview map>\>

# Executive Summary

# What we already know

Previous literature [@ref] and evidence [@ref] reviews have....

# Hospital Background

## Royal Liverpool University Hospital

Large acute hospital. Mainly focuses on complex planned care and specialist services. These include nephrology, renal transplantation, nuclear medicine, haematology, lithotripsy, dermatology and urology [@royalliverpool_web]. Provider also manages Aintree University hospital and Broadgreen hospital. Moved to new site single bed accommodation in October 2022. Prior to the change, the site had been operating 16.6% single bed room accommodation [@eric].

## Clatterbridge Cancer Centre

The Clatterbridge Trust operates 3 cancer centres in the Cheshire and Merseyside area. The Liverpool centre moved to fully single-bed rooms in June 2020 having previously been at 41% SBR [@eric]. The centre offers the full range of cancer treatment, both routine and surgical as well as diagnostics, outpatient appointments and associated support services [@ccc_liverpool].

## Royal Papworth

Royal Papworth hospital is a specialist centre for cardiothoracic (heart and lung) treatment, surgery and transplantation [@papworth_web]. The move to single bed accommodation occured in May 2019. Prior to the change, the site had been operating 32.8% single bed room accommodation [@eric].

## Chase Farm

Chase Farm hospital is a planned care centre operated by the Royal Free London NHS Trust. The Trust also runs the Royal Free and Barnet Hospital sites as well as other acute service across greater London [@chasefarm_web]. The new-build Chase Farm site, opened in September 2018, has 90% single bed rooms having previously had 29.4% [@eric].

## Southmead

Southmead hospital is run by the North Bristol NHS Trust who also operate Frenchay and Cossham Hospitals as well as other acute and rehabilitation services. The Brunel building housing the hospital opened in May 2014 with 75% single bed ensuite rooms. Previously the SBR provision for the trusts main sites was around 10% [@eric].

## Tunbridge Wells

The new hospital at Tunbridge Wells, replacing services at Pembury and Kent & Sussex, opened in 2 phases in January 2011 (maternity and children) and September 2011 (other inpatient services). According to ERIC [@eric] the site has 80% single bed inpatient rooms, with levels prior to 2011 being 28.3%.

## Peterborough

Peterborough City Hospital, operated by North West Anglia NHS Trust, was opened in November 2010 offering a range of acute and specialist services [@peterborough_web]. The site went from 10% single bed inpatient rooms to 98% SBR [@eric].

# Impact measures and data sources

Categorisation of the evidence suggests that impacts can be considered under one or more of health & safety, staff & patient experience and productivity & efficiency. A long list of potential impacts were drawn from the existing evidence reviews and measures were sought from published data that were specific to the logic/causal relationship or were proxies for the suggested effect. Measures were screened into the study if there were sufficient time series, if the data were consistent, if the data were available at least at provider level.

Where existing data sources were lacking, and for those impacts based on hospital data, we derived suitable measures from Secondary User Service (SUS) data held within NCDR [@ncdr].

Our final set of impact measures are thus:

[ ](images/indicators.png)

## Table with further detail when decided format

## Availability of indicators over time and for each site

The chart below demonstrates the availability of indicator datasets over time and the 'intervention' dates of the 7 sites to allow for general assessment of suitability for testing.

```{r, fig.height=6, fig.width=10}
tar_read(indicator_availability_plot)


```

Additional data issues have been uncovered during preparation of the data for analysis and some further omissions of some indicator/site combinations have been made. Full notes on data availability and suitability in relation to the analysis can be found in Appendix B.

The table below summarises which indicators have been been investigated for each site, and where analyses were not possible due to lack of data or other data issues.

```{r}

tar_read(indicator_availability_table)

```

For Royal Liverpool there is only 1 year post switch to single bedrooms, it is possible the effect size or overall direction of the effect may be different if there was a slightly longer outcome period.

For some sites (i.e Chase Farm, Clatterbridge and Papworth) at least part of the outcome period is impacted by COVID-19. While COVID-19 effects are also present in the matched control sites, the magnitude of effects varies between hospitals/regions.

There are also some situations where there is missing data or anomalies in the outcome periods, i.e. sudden increases or decreases, which has meant the outcome period has been cut short.

# Description of methods

Causal Impact Analysis is a technique that uses a control group to estimate the post-intervention counterfactual against which to measure study group impacts [@broderson2015]. We have used this method to quantify the change in the study hospitals following their switch to single-bed rooms by comparing the actual effects to a control group (similar hospital providers, patient case-mix and prior trends) that have been used to predict what would have happened to the outcome of interest had there been no switch.

## Finding control hospitals

There was a multi-phase selection process to create a pool of controls for each site. A summary of these steps is presented in @fig-flow-controls.

```{r flow_chart_selecting_controls}
#| label: fig-flow-controls
#| fig-cap: "Flow chart of the multi-phase process used to select the top 20 controls for each site."
tar_read(flow_chart_selecting_controls)
```

The first step was to match the intervention site and controls on type of site. For Clatterbridge the pool was limited to other cancer sites, for Royal Papworth cardiac sites and for all other sites general acute sites. Other intervention sites were excluded from the pool.

Controls were then matched on the percentage of single bed rooms available at the provider. Providers were excluded if the difference between their SBR percentage and the intervention's provider was greater than 5% at the time of the SBR switch. Then providers were excluded if their SBR percentage increased by 5% or more after this point.

Differences in floor space, median age and elective:non-elective ratios were calculated between the controls and intervention sites and ranked. The sum of these ranks were then ranked and the top 20 sites were chosen to form the control pool for further analysis.

## Causal Impact Analysis

The causal impact analysis is implemented using the MarketMatching package in R [@MarketMatching], which uses the dtw and CausalImpact R packages [@dtw] [@CausalImpact], to provide a simple way to find the most appropriate control matches using dynamic time warping and then use these controls for causal impact analysis using Bayesian structural time-series models.

Once suitable matches for each study site were determined and ranked, and the top ranking 20 sites for each study site were selected and fed into the MarketMatching package, for the final selection of control sites. This step selects the best matched control sites based on them having similar trends in the variable of interest over time to the study site. Up to 5 control sites were selected for each study site, but for some site, particularly the specialist centres, the number of appropriate matches was smaller and so fewer than 5 control sites were selected. Controls sites are selected for each site and indicator variable and as this matching of controls is based on similar trends over time a study site may have different control sites selected for different indicators.

The causal impact models were generated if there was at least 2 years of data prior to the switch to single bedrooms and at least 1 year of outcome period after the switch. Where possible a 2-year outcome period was used. The Mean Absolute Percentage Error (MAPE) and Durbin-Watson statistic of the models were checked, and the prior local level standard error adjusted if required to ensure a good historical model fit while minimising the forecasting intervals.

### Outputs of the causal impact analysis

The plots show:

1\) The expected value of the indicator in the outcome period, compared to the actual values of the study site.

2\) The point estimate shows the difference between the expected values and actual values over time, so at time points where the posterior intervals do not include zero there is a significant difference.

3\) The cumulative difference between the expected and actual values over the outcome period.

The values given in the tables and on forest plots are the average effects over the outcome period. Since the length of outcome period varies between sites due to availability of data/data issues the cumulative effect is not always comparable across sites.

## Aggregate (meta) analysis

Where possible, for each indicator variable a meta-analysis was conducted using only the data for district general and acute hospitals; the specialist hospital sites were excluded from this analysis.

A random-effects meta-analysis was conducted using the metafor R package [@metafor] and weighting the relative effects for each site using the inverse variance, as used for meta-analysis of causal impact models by [@Schmitt2017ExtendingBS].

# Main results (including related notes from lookback exercise)

## Productivity and Efficiency

### Length of stay

Mean length of stay significantly decreased at 3/6 sites (Southmead, Peterborough and Chase Farm), was unchanged at 2/6 sites (Royal Liverpool and Tunbridge Wells), but significantly increased at Clatterbridge. Clatterbridge is a specialist cancer centre, so it is possible the switch to single bed rooms had a different impact on length of stay due to the nature of the activity at the site.

```{r, fig.width=8, fig.height=4}

forest_plot(LoS_output,  "Points to the left indicate a decrease in mean length of stay following a switch to single bed   rooms, which is considered a positive effect. Significant positive effects are green, while significant negative effects (on the right) are red. Grey indicates no significant change.",
            "Average relative effect of switching to single bedrooms on mean length of stay")

model_effects_table(LoS_output, "Average effects of switching to single bedrooms on mean length of stay")
```


```{r, fig.width=8, fig.height=2.5}

mean_forest_plot_DGH_Acute(LoS_output, "Mean effect on length of stay at general/acute hospitals")

```

### Waiting time- Median (in weeks)

The median waiting time in weeks significantly decreased at 2/5 sites (Royal Liverpool and Peterborough) and was unchanged at 2/5 sites (Papworth and Clatterbridge). Median waiting time significantly increased at Tunbridge Wells, but this effect appeared to only be temporary during the first year post-switch, during the second year of the outcome period the waiting times fall back in line with the expected values. 

```{r, fig.width=8, fig.height=4}

forest_plot(waiting_time_median_output, "Points to the left indicate a decrease in median waiting time following a switch to single bed rooms, which is considered a positive effect. Significant positive effects are green, while significant negative effects (on the right) are indicated red. Grey indicates no significant change.",
         "Average relative effect of switching to single bedrooms on median waiting time"   )

model_effects_table(waiting_time_median_output, "Average effects of switching to single bedrooms on median waiting time (in wks)")

```

```{r, fig.width=8, fig.height=2.5}

mean_forest_plot_DGH_Acute(waiting_time_median_output, "Mean effect on median waiting time at general/acute hospitals")

```


### Waiting time - Total number of patients waiting

The total number of patients on waiting lists significantly decreased at 1/5 sites (Royal Liverpool) and was unchanged at 3/5 sites (Papworth, Peterborough and Tunbridge Wells). Total waiting list size increased at Clatterbridge, although it should be noted that Clatterbridge switched to single bedrooms mid-2020 so the outcome period is affected by COVID-19, with a large spike in patients waiting to be seen in early 2021. It is possible the impact of COVID-19 was greater at Clatterbridge than at the other cancer centres used as controls. 

```{r, fig.width=8, fig.height=4}

forest_plot(waiting_time_number_output, "Points to the left indicate a decrease in number of patients on waiting lists following a switch to single bed rooms, which is considered a positive effect. Significant positive effects are green, while significant negative effects (on the right) are red. Grey indicates no significant change.",
            "Average relative effect of switching to single bedrooms on number of patients on waiting lists")

model_effects_table(waiting_time_number_output, "Average effects of switching to single bedrooms on number of patients on waiting lists")

```


```{r, fig.width=8, fig.height=2.5}

mean_forest_plot_DGH_Acute(waiting_time_number_output, "Mean effect on number of patients on waiting lists at general/acute hospitals")

```

### Bed Occupancy

Bed occupancy is measured quarterly and is only available at a Provider level. The percentage of beds occupied  significantly increased at 2/4 sites (Clatterbridge and Southmead) and was unchanged at 2/4 (Royal Liverpool and and Chase Farm). An increase in bed occupancy is generally considered a positive result, provided it does not result in an increase in Emergency department waiting times. We have not looked at Emergency department waiting times. However, Chase Farm only does elective care and Clatterbridge is a cancer centre, and so neither of these sites have Emergency departments. 

```{r, fig.width=8, fig.height=4}

forest_plot(bed_occupancy_output, "Points to the right indicate an increase in bed occupancy following a switch to single bed rooms, which is considered a positive effect. Significant positive effects are green, while significant negative effects (on the left) are indicated red. Grey indicates no significant change.",
            "Average relative effect of switching to single bedrooms on bed occupancy")

model_effects_table(bed_occupancy_output, "Average effects of switching to single bedrooms on % of bed occupancy")


```

```{r, fig.width=8, fig.height=2.5}

mean_forest_plot_DGH_Acute(bed_occupancy_output, "Mean effect on bed occupancy at general/acute hospitals")

```

### Emergency Readmissions

The percentage of emergency readmissions significantly decreased at 3/7 sites (Tunbridge Wells, Peterborough  and Clatterbridge) and was unchanged at the remaining 4/7 sites.

```{r, fig.width=8, fig.height=4}

forest_plot(emergency_readmissions_output, "Points to the left indicate a decrease in emergency readmissions following a switch to single bed rooms, which is considered a positive effect. Significant positive effects are green, while significant negative effects (on the right) are red. Grey indicates no significant change.",
             "Average relative effect of switching to single bedrooms on emergency readmissions")

model_effects_table(emergency_readmissions_output, "Average effects of switching to single bedrooms on % of emergency readmissions")

```

```{r, fig.width=8, fig.height=2.5}

mean_forest_plot_DGH_Acute(emergency_readmissions_output, "Mean effect on emergency readmission rate at general/acute hospitals")

```

### Cleaning costs

Cleaning costs data are an annual measure, so there is limited data with only 1 or 2 data points in the outcome period. The total cleaning cost (in million £) significantly increased at 2/3 sites (Clatterbridge and Royal Liverpool) but remained unchanged at Papworth. 

```{r, include=TRUE, fig.width=8, fig.height=4}

forest_plot(cleaning_costs_output, "Points to the left indicate a decrease in cleaning costs following a switch to single bed rooms, which is considered a positive effect. Significant positive effects are green, while significant negative effects (on the right) are red. Grey indicates no significant change.",
            "Average relative effect of switching to single bedrooms on cleaning costs" )

model_effects_table(cleaning_costs_output, "Average effects of switching to single bedrooms on cleaning costs (in million £)")

```



## Health and Safety

### Deaths in hospital

The rate of in-hospital deaths (number per 1,000 discharges) significantly decreased at 1/5 sites (Peterborough), and was unchanged at 4/5 sites (Royal Liverpool, Tunbridge Wells, Clatterbridge and Southmead). 

```{r, include=TRUE, fig.width=8, fig.height=4}

forest_plot(sus_deaths_output, "Points to the left indicate a decrease in hospital deaths following a switch to single bed rooms, which is considered a positive effect. Significant positive effects green, while significant negative effects (on the right) are red. Grey indicates no significant change.",
            "Average relative effect of switching to single bedrooms on in-hospital deaths" )

model_effects_table(sus_deaths_output, "Average effects of switching to single bedrooms on in-hospital deaths/1,000 discharges")

```


```{r, fig.width=8, fig.height=2.5}

mean_forest_plot_DGH_Acute(sus_deaths_output, "Mean effect on in-hospital death rate at general/acute hospitals")

```

### Falls, Fractures and injuries in hospital

The rate of in-hospital falls, fractures and injuries (% of spells) significantly decreased at 1/4 sites (Peterborough), and was unchanged at 3/4 sites (Royal Liverpool, Tunbridge Wells and Southmead). 

```{r, include=TRUE, fig.width=8, fig.height=4}

forest_plot(falls_and_fractures_output, "Points to the left indicate a decrease in falls and fractures following a switch to single bed rooms, which is considered a positive effect. Significant positive effects are green, while significant negative effects (on the right) are red. Grey indicates no significant change.",
             "Average relative effect of switching to single bedrooms on in-hospital falls, fractures and injuries")

model_effects_table(falls_and_fractures_output, "Average effects of switching to single bedrooms on % of spells with in-hospital fall, fracture or injury")

```



```{r, fig.width=8, fig.height=2.5}

mean_forest_plot_DGH_Acute(falls_and_fractures_output, "Mean effect on rate of falls, fractures and injuries while in hospital at general/acute hospitals")

```

### Healthcare acquired infections

The combined rate of healthcare acquired infections could only be analysed for Royal Liverpool, and no significant change was seen. The combined rate of healthcare acquired infections is the sum of the rates (cases per 10,000 bed days) of C.difficile, E.Coli, MSSA, MRSA, Klebsiella and P.Aeruginosa. 

```{r, fig.width=8, fig.height=2}

forest_plot(hcai_output, "Grey indicates no significant change in the combined rate of healthcare acquired infections following a switch to single bed rooms.",
             "Average relative effect of switching to single bedrooms on rate of healthcare acquired infections")

model_effects_table(hcai_output, "Average effects of switching to single bedrooms on cases of healthcare acquired infections /10,000 bed days")

```

## Patient and Staff Experience


### Patient experience - Positive responses to the the Friends and Family Test 

Patient experience was determined using the results of the Friends and Family test. The percentage of positive responses significantly decreased at 1/4 sites (Clatterbridge), and was unchanged at the other 3/4 sites (Royal Liverpool, Papworth and Chase Farm). 

It should be noted that due to the COVID-19 pandemic there is missing friends and family test scores data from March 2020 until late 2020/early 2021 for all sites. Therefore, both Papworth and Clatterbridge have missing data in their outcome periods.

```{r, include=TRUE, fig.width=8, fig.height=4}

forest_plot(friends_and_family_output, "Points to the right indicate an increase in positive scores on the Friends and Family patient experience test following a switch to single bed rooms, which is considered a positive effect. Significant positive effects are green, while significant negative effects (on the left) are red. Grey indicates no significant change.",
            "Average relative effect of switching to single bedrooms on positive scores on the Friends and Family test" )

model_effects_table(friends_and_family_output, "Average effects of switching to single bedrooms on % of positive responses on the Friends and Family test")

```

### Staff sickness

The percentage of available days taken off sick by staff significantly increased at 1/5 sites (Southmead) and was unchanged at 4/5 sites (Royal Liverpool, Papworth, Clatterbridge and Chase Farm). 

While there was an increase in staff sickness at Southmead this seems to have been a temporary effect. The sickness rate is increased in the first year after the switch to single bedrooms and during this period there is a significantly larger winter peak. In the second year of the outcome period staff sickness rates fell back in line with the expected rates.

```{r, include=TRUE, fig.width=8, fig.height=4}

forest_plot(staff_sickness_output, "Points to the left indicate a decrease in staff sickness following a switch to single bed rooms, which is considered a positive effect. Significant positive effects are green, while significant negative effects (on the right) are red. Grey indicates no significant change.",
             "Average relative effect of switching to single bedrooms on staff sickness rate")

model_effects_table(staff_sickness_output, "Average effects of switching to single bedrooms on staff sickness rate (% of available days)")

```



```{r, fig.width=8, fig.height=2.5}

mean_forest_plot_DGH_Acute(staff_sickness_output, "Mean effect on rate of staff sickness at general/acute hospitals")

```



### Staff turnover

Staff turnover measured as percentage of staff leaving could only be measured for Royal Liverpool, where no significant changes was found. 

```{r, fig.width=8, fig.height=2}

forest_plot(staff_turnover_output, "Grey indicates no significant change in staff turnover following a switch to single bed rooms.",
             "Average relative effect of switching to single bedrooms on staff turnover")

model_effects_table(staff_turnover_output, "Average effects of switching to single bedrooms on rate of staff turnover (% leaving)")

```

### Staff survey

To assess staff experience the NHS staff survey was used and we analysed the percentage of staff that Agreed or Strongly Agreed with the statement 'I would recommend my trust as a place to work'. The staff survey is an annual measure so there is limited data, with only 1 or 2 data points in the outcome period. 

The staff survey data is collected over a period of time in the autumn each year, but for analysis purposes we have set the date as the last day of the year in which the data was collected. Both Chase Farm and Royal Liverpool switched to single rooms during the autumn, so the data for the first data point in the outcome period would actually have been collected during the transition period which may have had an impact on the results.

The percentage of staff that would recommend their trust as a place to work significantly increased at 1/5 sites (Papworth), and was unchanged at 2/5 (Chase Farm and Royal Liverpool). At 2/5 sites (Southmead and Clatterbridge) there was a significant decrease in the percentage that would recommend their trust as a place to work. At Southmead the decrease appears to be temporary, occurring in the first year post-switch to single bed rooms with positive responses increase back to the expected level in the second year of the outcome period. 

```{r, include=TRUE, fig.width=8, fig.height=4}

forest_plot(staff_survey_output,"Points to the right indicate an increase in positive responses to the NHS staff survey following a switch to single bed rooms, which is considered a positive effect. Significant positive effects are green, while significant negative effects (on the left) are red. Grey indicates no significant change.", "Average relative effect of switching to single bedrooms on % of NHS staff that recommend their workplace")

model_effects_table(staff_survey_output, "Average effects of switching to single bedrooms on % of NHS staff who would recommend their workplace")

```


```{r, fig.width=8, fig.height=2.5}

mean_forest_plot_DGH_Acute(staff_survey_output, "Mean effect on percentage of staff that would recommend their trust as a place to work at general/acute hospitals")

```


## Summary of results

```{r}
summary_table_indicators_and_sites(LoS_output,
                                    waiting_time_median_output,
                                    waiting_time_number_output,
                                    bed_occupancy_output,
                                    emergency_readmissions_output,
                                    cleaning_costs_output,
                                    sus_deaths_output,
                                    falls_and_fractures_output,
                                    hcai_output,
                                    friends_and_family_output,
                                    staff_sickness_output,
                                    staff_turnover_output,
                                    staff_survey_output) 

```

# Limitations and discussion

# Reccommendations for modelling and future evaluation

# Appendices

## A.CIA charts by indicator and hospital site/provider

### Length of stay

::: panel-tabset
#### Decrease

```{r, fig.width=5, fig.height=6}
#### Papworth

#COVID-19 spikes in the post switch period are impacting LoS and these are not seen in the controls

#LoS_RGM<-tar_read(LoS_RGM)

#evaluating_model("RGM", "RGM22", length_of_stay, "2019-05-01", "avg_los", 0.05, LoS_RGM, single_bedroom_matches_final)

#cia_summary_plots(LoS_RGM, "Average LoS (days)", "2019-05-01")
```

::: columns
::: {.column width="50%"}
Peterborough

```{r, fig.width=5, fig.height=6}

LoS_RGN<-tar_read(LoS_RGN)

#evaluating_model("RGN",  "RGN80", length_of_stay, "2010-11-01","avg_los", 0.01, LoS_RGN, single_bedroom_matches_final)

cia_summary_plots(LoS_RGN, "Average LoS (days)", "2010-11-01")

```

Chase Farm

```{r, fig.width=5, fig.height=6}

LoS_RAL<-tar_read(LoS_RAL)

#evaluating_model("RAL", "RALC7", length_of_stay, "2018-09-01", "avg_los", 0.05, LoS_RAL, single_bedroom_matches_final)

cia_summary_plots(LoS_RAL,"Average LoS (days)", "2018-09-01")
```
:::

::: {.column width="50%"}
Southmead

```{r, fig.width=5, fig.height=6}

LoS_RVJ<-tar_read(LoS_RVJ)

#evaluating_model("RVJ","RVJ01",  length_of_stay, "2014-05-01", "avg_los", 0.01, LoS_RVJ, single_bedroom_matches_final)

cia_summary_plots(LoS_RVJ,"Average LoS (days)", "2014-05-01")
```
:::
:::

#### No change

::: columns
::: {.column width="50%"}
Tunbridge Wells

```{r, fig.width=5, fig.height=6}

LoS_RWF<-tar_read(LoS_RWF)

#evaluating_model("RWF",  "RWFTW", length_of_stay, "2011-01-01", "avg_los", 0.05, LoS_RWF, single_bedroom_matches_final)

cia_summary_plots(LoS_RWF,"Average LoS (days)", "2011-01-01")

```
:::

::: {.column width="50%"}
Royal Liverpool

```{r, fig.width=5, fig.height=6}

LoS_REM<-tar_read(LoS_REM)

#evaluating_model("REM", "REMRQ",  length_of_stay, "2022-10-01", "avg_los", 0.05, LoS_REM, single_bedroom_matches_final)

cia_summary_plots(LoS_REM, "Average LoS (days)", "2022-10-01")
```
:::
:::

#### Increase

::: columns
::: {.column width="50%"}
Clatterbridge

```{r, fig.width=5, fig.height=6}

LoS_REN<-tar_read(LoS_REN)

#evaluating_model("REN", "REN22", length_of_stay, "2020-06-01", "avg_los", 0.1, LoS_REN, single_bedroom_matches_final)

cia_summary_plots(LoS_REN,"Average LoS (days)", "2020-06-01")

```
:::
:::
:::

### Waiting time- Median (in weeks)

::: panel-tabset
#### Decrease

::: columns
::: {.column width="50%"}
Royal Liverpool

```{r, fig.width=5, fig.height=6}

waiting_time_median_REM<-tar_read(waiting_time_median_REM)

#evaluating_model("REM", NA,  rtt_waiting_time, "2022-10-01", "median_by_prov", 0.05, waiting_time_median_REM, single_bedroom_matches_final)

cia_summary_plots(waiting_time_median_REM, "Median waiting time (wks)", "2022-10-01")
```
:::

::: {.column width="50%"}
Peterborough

```{r,  fig.width=5, fig.height=6}

waiting_time_median_RGN<-tar_read(waiting_time_median_RGN)

#evaluating_model("RGN", NA, rtt_waiting_time, "2010-11-01", "median_by_prov", 0.01, waiting_time_median_RGN, single_bedroom_matches_final)

cia_summary_plots(waiting_time_median_RGN, "Median waiting time (wks)", "2010-11-01")

```
:::
:::

#### No change

::: columns
::: {.column width="50%"}
Clatterbridge

```{r, fig.width=5, fig.height=6}

waiting_time_median_REN<-tar_read(waiting_time_median_REN)

#evaluating_model("REN", NA, rtt_waiting_time, "2020-06-01", "median_by_prov", 0.05, waiting_time_median_REN, single_bedroom_matches_final)

cia_summary_plots(waiting_time_median_REN, "Median waiting time (wks)", "2020-06-01")

```
:::

::: {.column width="50%"}
Papworth

```{r, fig.width=5, fig.height=6}

waiting_time_median_RGM<-tar_read(waiting_time_median_RGM)

#evaluating_model("RGM", NA, rtt_waiting_time, "2019-05-01", "median_by_prov", 0.05, waiting_time_median_RGM, single_bedroom_matches_final)

cia_summary_plots(waiting_time_median_RGM, "Median waiting time (wks)", "2019-05-01")

```
:::

```{r, fig.width=5, fig.height=6}
#### Chase Farm
#waiting_time_median_RAL<-tar_read(waiting_time_median_RAL)

#evaluating_model("RAL", NA, rtt_waiting_time, "2018-09-01", "median_by_prov", 0.01, waiting_time_median_RAL, single_bedroom_matches_final)

#cia_summary_plots(waiting_time_median_RAL, "Study site: Chase Farm, RAL","Median waiting time (wks)", "2018-09-01")

```

```{r, fig.width=5, fig.height=6}
#### Southmead
#waiting_time_median_RVJ<-tar_read(waiting_time_median_RVJ)

#evaluating_model("RVJ",NA,  rtt_waiting_time, "2014-05-01", "median_by_prov", 0.1, waiting_time_median_RVJ, single_bedroom_matches_final)

#cia_summary_plots(waiting_time_median_RVJ, "Median waiting time (wks)", "2014-05-01")
```
:::

#### Increase

::: columns
::: {.column width="50%"}
Tunbridge Wells

```{r, fig.width=5, fig.height=6}

waiting_time_median_RWF<-tar_read(waiting_time_median_RWF)

#evaluating_model("RWF", NA, rtt_waiting_time, "2011-01-01", "median_by_prov", 0.01, waiting_time_median_RWF, single_bedroom_matches_final)

cia_summary_plots(waiting_time_median_RWF, "Median waiting time (wks)", "2011-01-01")
```
:::
:::
:::

### Waiting time - Total number of patients waiting

::: panel-tabset
#### Decrease

Royal Liverpool

```{r, fig.width=5, fig.height=6}

waiting_time_number_REM<-tar_read(waiting_time_number_REM)

#evaluating_model("REM", NA, rtt_waiting_time, "2022-10-01", "number_incomplete", 0.1, waiting_time_number_REM, single_bedroom_matches_final)

cia_summary_plots(waiting_time_number_REM, "Number waiting", "2022-10-01")

```

#### No change

::: columns
::: {.column width="50%"}
Papworth

```{r, fig.width=5, fig.height=6}

waiting_time_number_RGM<-tar_read(waiting_time_number_RGM)

#evaluating_model("RGM", NA, rtt_waiting_time, "2019-05-01", "number_incomplete", 0.05, waiting_time_number_RGM, single_bedroom_matches_final)

cia_summary_plots(waiting_time_number_RGM, "Number waiting", "2019-05-01")
```

Peterborough

```{r, fig.width=5, fig.height=6}

waiting_time_number_RGN<-tar_read(waiting_time_number_RGN)

#evaluating_model("RGN", NA, rtt_waiting_time, "2010-11-01","number_incomplete", 0.1, waiting_time_number_RGN, single_bedroom_matches_final)

cia_summary_plots(waiting_time_number_RGN, "Number waiting", "2010-11-01")
```
:::

::: {.column width="50%"}
Tunbridge Wells

```{r, fig.width=5, fig.height=6}

waiting_time_number_RWF<-tar_read(waiting_time_number_RWF)

#evaluating_model("RWF", NA, rtt_waiting_time, "2011-01-01", "number_incomplete", 0.1, waiting_time_number_RWF, single_bedroom_matches_final)

cia_summary_plots(waiting_time_number_RWF, "Number waiting", "2011-01-01")
```
:::
:::

#### Increase

::: columns
::: {.column width="50%"}
Clatterbridge

```{r, fig.width=5, fig.height=6}

waiting_time_number_REN<-tar_read(waiting_time_number_REN)

#evaluating_model("REN", NA, rtt_waiting_time, "2020-06-01", "number_incomplete", 0.1, waiting_time_number_REN, single_bedroom_matches_final)

cia_summary_plots(waiting_time_number_REN, "Number waiting", "2020-06-01")
```
:::
:::
:::

### Bed Occupancy

::: panel-tabset
#### No change

::: columns
::: {.column width="50%"}
Chase Farm

```{r, fig.width=5, fig.height=6}

bed_occupancy_RAL<-tar_read(bed_occupancy_RAL)

#evaluating_model("RAL",NA,  bed_occupancy, "2018-09-01", "bed_occupancy", 0.1, bed_occupancy_RAL, single_bedroom_matches_final)

cia_summary_plots(bed_occupancy_RAL, "Percentage", "2018-09-01")
```
:::

::: {.column width="50%"}
Royal Liverpool

```{r,  fig.width=5, fig.height=6}

bed_occupancy_REM<-tar_read(bed_occupancy_REM)

#evaluating_model("REM", NA, bed_occupancy, "2022-10-01", "bed_occupancy", 0.05, bed_occupancy_REM, single_bedroom_matches_final)

cia_summary_plots(bed_occupancy_REM, "Percentage", "2022-10-01")
```
:::
:::

#### Increase

::: columns
::: {.column width="50%"}
Clatterbridge

```{r,  fig.width=5, fig.height=6}

bed_occupancy_REN<-tar_read(bed_occupancy_REN)

#evaluating_model("REN", NA, bed_occupancy, "2020-06-01", "bed_occupancy", 0.1, bed_occupancy_REN, single_bedroom_matches_final)

cia_summary_plots(bed_occupancy_REN,"Percentage", "2020-06-01")
```
:::

::: {.column width="50%"}
Southmead

```{r, fig.width=5, fig.height=6}

bed_occupancy_RVJ<-tar_read(bed_occupancy_RVJ)

#evaluating_model("RVJ", NA, bed_occupancy, "2014-05-01", "bed_occupancy", 0.1, bed_occupancy_RVJ, single_bedroom_matches_final)

cia_summary_plots(bed_occupancy_RVJ, "Percentage", "2014-05-01")
```
:::
:::

Black dotted line indicates the time of the last data point prior to the switch to single bedrooms
:::

### Emergency Readmissions

::: panel-tabset
#### Decrease

::: columns
::: {.column width="50%"}
Clatterbridge

```{r, fig.width=5, fig.height=6}

emergency_readmissions_REN<-tar_read(emergency_readmissions_REN)

#evaluating_model("REN", "REN22", emergency_readmissions, "2020-06-01","perc", 0.1, emergency_readmissions_REN, single_bedroom_matches_final)

cia_summary_plots(emergency_readmissions_REN, "% readmissions", "2020-06-01")

```

Peterborough

```{r, fig.width=5, fig.height=6}

emergency_readmissions_RGN<-tar_read(emergency_readmissions_RGN)

#evaluating_model("RGN",  "RGN80", emergency_readmissions, "2010-11-01","perc", 0.1, emergency_readmissions_RGN, single_bedroom_matches_final)

cia_summary_plots(emergency_readmissions_RGN,"% readmissions", "2010-11-01")
```
:::

::: {.column width="50%"}
Tunbridge Wells

```{r, fig.width=5, fig.height=6}

emergency_readmissions_RWF<-tar_read(emergency_readmissions_RWF)

#evaluating_model("RWF",  "RWFTW", emergency_readmissions, "2011-01-01", "perc", 0.01, emergency_readmissions_RWF, single_bedroom_matches_final)

cia_summary_plots(emergency_readmissions_RWF, "% readmissions", "2011-01-01")
```
:::
:::

#### No change

::: columns
::: {.column width="50%"}
Royal Liverpool

```{r, fig.width=5, fig.height=6}

emergency_readmissions_REM<-tar_read(emergency_readmissions_REM)

#evaluating_model("REM", "REMRQ",  emergency_readmissions, "2022-10-01", "perc", 0.1, emergency_readmissions_REM, single_bedroom_matches_final)

cia_summary_plots(emergency_readmissions_REM, "% readmissions", "2022-10-01")
```

Papworth

```{r, fig.width=5, fig.height=6}

emergency_readmissions_RGM<-tar_read(emergency_readmissions_RGM)

#evaluating_model("RGM", "RGM22", emergency_readmissions, "2019-05-01", "perc", 0.1, emergency_readmissions_RGM, single_bedroom_matches_final)

cia_summary_plots(emergency_readmissions_RGM, "% readmissions", "2019-05-01")
```
:::

::: {.column width="50%"}
Chase Farm

```{r,  fig.width=5, fig.height=6}

emergency_readmissions_RAL<-tar_read(emergency_readmissions_RAL)

#evaluating_model("RAL", "RALC7", emergency_readmissions, "2018-09-01", "perc", 0.01, emergency_readmissions_RAL, single_bedroom_matches_final)

cia_summary_plots(emergency_readmissions_RAL,"% readmissions", "2018-09-01")

```

Southmead

```{r, fig.width=5, fig.height=6}

emergency_readmissions_RVJ<-tar_read(emergency_readmissions_RVJ)

#evaluating_model("RVJ","RVJ01",  emergency_readmissions, "2014-05-01","perc", 0.05, emergency_readmissions_RVJ, single_bedroom_matches_final)

cia_summary_plots(emergency_readmissions_RVJ, "% readmissions", "2014-05-01")
```
:::
:::
:::

### Cleaning costs

::: panel-tabset
#### No change

::: columns
::: {.column width="50%"}
Papworth (RGM)

```{r, fig.width=5, fig.height=6}

cleaning_costs_RGM<-tar_read(cleaning_costs_RGM)
  
#evaluating_model("RGM", "RGM22",cleaning_costs,"2019-05-01","cleaning_service_cost", 0.01, cleaning_costs_RGM, single_bedroom_matches_final)

cia_summary_plots( cleaning_costs_RGM, "Cost", "2019-05-01")
```
:::
:::

Black dotted line indicates the time of the last data point prior to the switch to single bedrooms

#### Increase

::: columns
::: {.column width="50%"}
Royal Liverpool (REM)

```{r, fig.width=5, fig.height=6}

cleaning_costs_REM<-tar_read(cleaning_costs_REM)
  
#evaluating_model("REM","REMRQ",cleaning_costs,"2022-10-01", "cleaning_service_cost", 0.01, cleaning_costs_REM, single_bedroom_matches_final)

cia_summary_plots( cleaning_costs_REM, "Cost", "2022-10-01")
```
:::

::: {.column width="50%"}
Clatterbridge (REN)

```{r,  fig.width=5, fig.height=6}

cleaning_costs_REN<-tar_read(cleaning_costs_REN)
  
#evaluating_model("REN", "REN22",cleaning_costs,"2020-06-01", "cleaning_service_cost", 0.01, cleaning_costs_REN, single_bedroom_matches_final)

cia_summary_plots( cleaning_costs_REN, "Cost", "2020-06-01")
```
:::
:::

Black dotted line indicates the time of the last data point prior to the switch to single bedrooms
:::

### Deaths in hospital

::: panel-tabset
#### Decrease

::: columns
::: {.column width="50%"}
Peterborough

```{r, fig.width=5, fig.height=6}

sus_deaths_RGN<-tar_read(sus_deaths_RGN)

#evaluating_model("RGN",  "RGN80", sus_deaths, "2010-11-01","hosp_rate_1000", 0.1, sus_deaths_RGN, single_bedroom_matches_final)

cia_summary_plots(sus_deaths_RGN, "No./per 1,000 discharges", "2010-11-01")
```
:::

::: {.column width="50%"}
:::
:::

#### No change

::: columns
::: {.column width="50%"}
Royal Liverpool

```{r,  fig.width=5, fig.height=6}

sus_deaths_REM<-tar_read(sus_deaths_REM)

#evaluating_model("REM", "REMRQ",  sus_deaths, "2022-10-01", "hosp_rate_1000", 0.05, sus_deaths_REM, single_bedroom_matches_final)

cia_summary_plots(sus_deaths_REM, "No./per 1,000 discharges", "2022-10-01")
```

```{r, include=FALSE}

sapply(file.path(tempdir(), list.files(tempdir())), unlink)
```

Tunbridge Wells

```{r, fig.width=5, fig.height=6}

sus_deaths_RWF<-tar_read(sus_deaths_RWF)

#evaluating_model("RWF",  "RWFTW", sus_deaths, "2011-01-01", "hosp_rate_1000", 0.01, sus_deaths_RWF, single_bedroom_matches_final)

cia_summary_plots(sus_deaths_RWF, "No./per 1,000 discharges", "2011-01-01")
```
:::

::: {.column width="50%"}
Southmead

```{r,  fig.width=5, fig.height=6}

sus_deaths_RVJ<-tar_read(sus_deaths_RVJ)

#evaluating_model("RVJ","RVJ01",  sus_deaths, "2014-05-01","hosp_rate_1000", 0.01, sus_deaths_RVJ, single_bedroom_matches_final)

cia_summary_plots(sus_deaths_RVJ,"No./per 1,000 discharges", "2014-05-01")
```

Clatterbridge

```{r,  fig.width=5, fig.height=6}

sus_deaths_REN<-tar_read(sus_deaths_REN)

#evaluating_model("REN", "REN22", sus_deaths, "2020-06-01","hosp_rate_1000", 0.05, sus_deaths_REN, single_bedroom_matches_final )

cia_summary_plots(sus_deaths_REN, "No./per 1,000 discharges", "2020-06-01")

```
:::
:::
:::

### Falls, Fractures and injuries in hospital

::: panel-tabset
#### Decrease

Peterborough

```{r, fig.width=5, fig.height=6}

falls_and_fractures_RGN<-tar_read(falls_and_fractures_RGN)

#evaluating_model("RGN",  "RGN80",falls_and_fractures, "2010-11-01","ff_rate", 0.01, falls_and_fractures_RGN, single_bedroom_matches_final)

cia_summary_plots(falls_and_fractures_RGN,"% of spells", "2010-11-01")
```

#### No change

::: columns
::: {.column width="50%"}
Royal Liverpool

```{r, fig.width=5, fig.height=6}

falls_and_fractures_REM<-tar_read(falls_and_fractures_REM)

#evaluating_model("REM", "REMRQ",  falls_and_fractures, "2022-10-01", "ff_rate", 0.05, falls_and_fractures_REM, single_bedroom_matches_final)

cia_summary_plots(falls_and_fractures_REM, "% of spells", "2022-10-01")
```

Southmead

```{r,  fig.width=5, fig.height=6}

falls_and_fractures_RVJ<-tar_read(falls_and_fractures_RVJ)

#evaluating_model("RVJ","RVJ01",  falls_and_fractures, "2014-05-01","ff_rate", 0.05, falls_and_fractures_RVJ, single_bedroom_matches_final)

cia_summary_plots(falls_and_fractures_RVJ,"% of spells", "2014-05-01")
```

Outcome period is cut short as the rate of falls and fractures at Southmead jumps suddenly in the second year of the outcome period (Nov 2015); this change does not appear to be associated with the change to single rooms as it occurs suddenly almost 18 months after the change to single rooms.
:::

::: {.column width="50%"}
Tunbridge Wells

```{r, fig.width=5, fig.height=6}

falls_and_fractures_RWF<-tar_read(falls_and_fractures_RWF)

#evaluating_model("RWF",  "RWFTW", falls_and_fractures, "2011-01-01", "ff_rate", 0.05, falls_and_fractures_RWF, single_bedroom_matches_final)

cia_summary_plots(falls_and_fractures_RWF, "% of spells", "2011-01-01")
```
:::
:::
:::

### Healthcare acquired infections

#### No change

Royal Liverpool

```{r, fig.width=5, fig.height=6}

hcai_REM<-tar_read(hcai_REM)

#evaluating_model("REM", NA, hcai, "2022-10-01", "combined_rate", 0.1, hcai_REM, single_bedroom_matches_final)

cia_summary_plots(hcai_REM, "Rate/10,000 beddays", "2022-10-01")
```

### Patient experience - Friends and Family scores

::: panel-tabset
#### Decrease

Clatterbridge (REN)

```{r, fig.width=5, fig.height=6}

friends_and_family_REN<-tar_read(friends_and_family_REN)

#evaluating_model("REN","REN22", friends_and_family,"2020-06-01", "friends_and_family_percent", 0.1, friends_and_family_REN, single_bedroom_matches_final )

cia_summary_plots(friends_and_family_REN,"Positive responses (%)", "2020-06-01")

#Last data point prior to switch was about 4 months prior then no data for 8 months after, as switch came during COVID

```

#### No Change

::: columns
::: {.column width="50%"}
Royal Liverpool (REMRQ)

```{r, fig.width=5,fig.height=6 }

friends_and_family_REM<-tar_read(friends_and_family_REM)

#evaluating_model("REM","REMRQ", friends_and_family,"2022-10-01", "friends_and_family_percent", 0.1, friends_and_family_REM, single_bedroom_matches_final)

cia_summary_plots(friends_and_family_REM, "Positive responses (%)", "2022-10-01")

# Large amount of data missing in the two years prior due to gap over covid. One of the control sites doesn't go back far enough for it is causing the data to be cut off. Think I need to have less matches for this one. But would still have a disturbed pre switch period due to COVID

```

Papworth (RGM)

```{r, fig.width=5, fig.height=6}

friends_and_family_RGM<-tar_read(friends_and_family_RGM)

#evaluating_model("RGM", "RGM22", friends_and_family,"2019-05-01", "friends_and_family_percent", 0.1, friends_and_family_RGM, single_bedroom_matches_final)

cia_summary_plots(friends_and_family_RGM, "Positive responses (%)", "2019-05-01")

```
:::

::: {.column width="50%"}
Chase Farm Hospital (RAL)

```{r, fig.width=5, fig.height=6}

friends_and_family_RAL<-tar_read(friends_and_family_RAL)

#evaluating_model("RAL","RALC7",  friends_and_family,"2018-09-01", "friends_and_family_percent", 0.01, friends_and_family_RAL, single_bedroom_matches_final)

cia_summary_plots(friends_and_family_RAL, "Positive responses (%)", "2018-09-01")
```
:::
:::
:::

### Staff sickness


::: panel-tabset
#### Increase

Southmead (RVJ)

```{r, fig.width=5, fig.height=6}

staff_sickness_RVJ<-tar_read(staff_sickness_RVJ)

#evaluating_model("RVJ", NA,staff_sickness,"2014-05-01", "staff_sickness_percent", 0.05, staff_sickness_RVJ, single_bedroom_matches_final)

cia_summary_plots(staff_sickness_RVJ, "Sickness Rate (%)", "2014-05-01")
```

#### No change

::: columns
::: {.column width="50%"}
Royal Liverpool (REM)

```{r, fig.height=6, fig.width=5}

staff_sickness_REM<-tar_read(staff_sickness_REM)

#evaluating_model("REM",NA, staff_sickness,"2022-10-01", "staff_sickness_percent", 0.05, staff_sickness_REM, single_bedroom_matches_final)

cia_summary_plots(staff_sickness_REM, "Sickness Rate (%)", "2022-10-01")

```

Clatterbridge (REN)

```{r, fig.width=5, fig.height=6}

staff_sickness_REN<-tar_read(staff_sickness_REN)

#evaluating_model("REN", NA,staff_sickness,"2020-06-01", "staff_sickness_percent", 0.05,staff_sickness_REN, single_bedroom_matches_final )

cia_summary_plots(staff_sickness_REN, "Sickness Rate (%)", "2020-06-01")

```
:::

::: {.column width="50%"}
Papworth (RGM)

```{r, fig.width=5, fig.height=6}

staff_sickness_RGM<-tar_read(staff_sickness_RGM)

#evaluating_model("RGM", NA,staff_sickness,"2019-05-01", "staff_sickness_percent", 0.05, staff_sickness_RGM, single_bedroom_matches_final)

cia_summary_plots(staff_sickness_RGM, "Sickness Rate (%)", "2019-05-01")
```

Chase Farm Hospital (RAL)

```{r,  fig.width=5, fig.height=6}

staff_sickness_RAL<-tar_read(staff_sickness_RAL)

#evaluating_model("RAL", NA, staff_sickness,"2018-09-01", "staff_sickness_percent", 0.05, staff_sickness_RAL, single_bedroom_matches_final)

cia_summary_plots(staff_sickness_RAL, "Sickness Rate (%)", "2018-09-01")
```
:::
:::
:::

### Staff turnover

#### No change

Royal Liverpool (REM)

```{r, fig.width=5, fig.height=6}

staff_turnover_REM<-tar_read(staff_turnover_REM)

#evaluating_model("REM", NA,staff_turnover,"2022-10-01", "leaving_rate", 0.1, staff_turnover_REM, single_bedroom_matches_final)

cia_summary_plots(staff_turnover_REM, "Staff leaving rate (%)", "2022-10-01")
```

### Staff survey


```{r, include=FALSE}

Peterborough_matches<-single_bedroom_matches_final|>
  filter(organisation_code=="RGN")|>
  filter(rank_of_ranks<=10)

Peterborough_analysis<-staff_survey|>
  filter(organisation_code=="RGN" | (organisation_code %in% (Peterborough_matches$matching_organisation_code)))

Peterborough_analysis|>
    filter(organisation_code=="RGN"|
         organisation_code=="RXH"|
        organisation_code=="RJR"|  
         organisation_code=="RXN"| 
         organisation_code=="RXK"|  
         organisation_code=="RPA"  )|>
  ggplot()+
  geom_line(aes(x=month, y=positive_responses, group=organisation_code, colour=organisation_code))+
   geom_vline(
      aes(xintercept = as.Date('2010-11-01')),
      linetype = "dotted",
      linewidth = 0.6,
      color = "#ec6555"
    )


Peterborough_analysis|>
   filter(organisation_code=="RGN"|
         organisation_code=="RXH"|
        organisation_code=="RJR"|  
         organisation_code=="RXN"| 
         organisation_code=="RXK"|  
         organisation_code=="RPA"  )|>
  filter(month=='2009-12-31'| month=='2012-12-31' )|>
  spread(key=month, value=positive_responses)|>
  mutate(change=(((`2012-12-31`-`2009-12-31`)/`2009-12-31`)*100))





Tunbridge_matches<-single_bedroom_matches_final|>
  filter(organisation_code=="RWF")|>
  filter(rank_of_ranks<=20)

Tunbridge_analysis<-staff_survey|>
  filter(organisation_code=="RWF" | (organisation_code %in% (Tunbridge_matches$matching_organisation_code)))

mm <- MarketMatching::best_matches(
      data = Tunbridge_analysis,
      id_variable = "organisation_code",
      date_variable = "month",
      matching_variable = "positive_responses",
      parallel = FALSE,
      warping_limit = 1,
      dtw_emphasis = 0,
      matches = 5,
      start_match_period = (as.Date('2011-01-01') %m-% months(120)),
      end_match_period = (as.Date('2011-01-01'))
    )

mm<-mm$BestMatches|>
  filter(organisation_code=="RWF")

Tunbridge_analysis|>
  filter(organisation_code=="RWF" | (organisation_code %in% mm$BestControl))|>
  ggplot()+
  geom_line(aes(x=month, y=positive_responses, group=organisation_code, colour=organisation_code))+
   geom_vline(
      aes(xintercept = as.Date('2011-01-01')),
      linetype = "dotted",
      linewidth = 0.6,
      color = "#ec6555"
    )


Tunbridge_analysis|>
   filter(organisation_code=="RWF" | (organisation_code %in% mm$BestControl))|>
  filter(month=='2009-12-31'| month=='2012-12-31' )|>
  spread(key=month, value=positive_responses)|>
  mutate(change=(((`2012-12-31`-`2009-12-31`)/`2009-12-31`)*100))


```



::: panel-tabset
#### Decrease

::: columns
::: {.column width="50%"}
Clatterbridge (REN)

```{r,  fig.width=5, fig.height=6}

staff_survey_REN<-tar_read(staff_survey_REN)
  
#evaluating_model("REN", NA,staff_survey,"2020-06-01", "positive_responses", 0.01, staff_survey_REN, single_bedroom_matches_final)

cia_summary_plots( staff_survey_REN, "Positive Responses (%)", "2020-06-01")
```
:::

::: {.column width="50%"}
Southmead (RVJ)

```{r, fig.width=5, fig.height=6}

staff_survey_RVJ<-tar_read(staff_survey_RVJ)
  
#evaluating_model("RVJ", NA,staff_survey,"2014-05-01", "positive_responses", 0.01, staff_survey_RVJ, single_bedroom_matches_final)

cia_summary_plots( staff_survey_RVJ, "Positive Responses (%)", "2014-05-01")
```
:::

Black dotted line indicates the time of the last data point prior to the switch to single bedrooms
:::

#### No change

::: columns
::: {.column width="50%"}
Royal Liverpool (REM)

```{r, fig.width=5, fig.height=6}

staff_survey_REM<-tar_read(staff_survey_REM)
  
#evaluating_model("REM", NA,staff_survey,"2022-10-01", "positive_responses", 0.01, staff_survey_REM, single_bedroom_matches_final)

cia_summary_plots( staff_survey_REM, "Positive Responses (%)", "2022-10-01")

```
:::

::: {.column width="50%"}
Chase Farm (RAL)

```{r,  fig.width=5, fig.height=6}

staff_survey_RAL<-tar_read(staff_survey_RAL)
  
#evaluating_model("RAL", NA,staff_survey,"2018-09-01", "positive_responses", 0.01, staff_survey_RAL, single_bedroom_matches_final)

cia_summary_plots( staff_survey_RAL, "Positive Responses (%)", "2018-09-01")
```
:::
:::

Black dotted line indicates the time of the last data point prior to the switch to single bedrooms

#### Increase

::: columns
::: {.column width="50%"}
Papworth (RGM)

```{r, fig.width=5, fig.height=6}

staff_survey_RGM<-tar_read(staff_survey_RGM)
  
#evaluating_model("RGM", NA,staff_survey,"2019-05-01", "positive_responses", 0.01, staff_survey_RGM, single_bedroom_matches_final)

cia_summary_plots( staff_survey_RGM, "Positive Responses (%)", "2019-05-01")

```
:::
:::

Black dotted line indicates the time of the last data point prior to the switch to single bedrooms
:::

## B.Notes on data quality and suitability (for CIA)

RTT waiting time data - Only available at trust level - Chase Farm was excluded as there was only 4 months of data available in the outcome period. - Southmead was excluded due to a period of missing data in the 2 years prior to the switch to single rooms.

Length of stay - Papworth was excluded as there were 2 large COVID-19 related spikes in length of stay in the outcome period that were significantly larger than the COVID-19 effects in the control sites, so it was not possible to determine if there would have been a change in length of stay without COVID-19.

Bed occupancy - Only available at trust level - This is a quarterly measure so there is more limited data and depending on the time point at which the switch to single bedrooms occurred the may be no data until 3 months after the switch or the last point of baseline may be 3 months prior to the switch.

Cleaning costs - This is an annual measure, so there are limited data points in the pre-switch period and only 1 or 2 points in the outcome period. - The limited data meant that for Chase Farm only 1 control site could be matched and there was insufficient data to fit a suitable model.

Healthcare acquired infections - Only available at trust level - Data is only available for Royal Liverpool - Clatterbridge was excluded as the rate was generally low, often zero, but there were also significant spikes, which meant it was not possible to fit a suitable model.

Falls, fractures and injuries in hospital - Clatterbridge, Papworth and Chase Farm were all excluded as the rates were very low, often zero, so it wasn't possible to fit suitable models to the data.

Deaths in hospital - Papworth was excluded due to a large COVID-19 spike in the outcome period that was greater than that seen in the control sites, so it was not possible to determine if there would have been a change had COVID-19 not occurred. - Chase Farm was excluded as the rate was very low, often zero, so it wasn't possible to fit a suitable model, this low rate is unsurprising given it is only conducting elective care.

Patient experience - There is around a year of missing Friends and Family Test data for all sites during the COVID-19 pandemic (March 2020 until late 2020/early 2021), this means that there is some missing data in the baseline period for Royal Liverpool and some missing data in the outcome periods for Clatterbridge, Papworth and Chase Farm.  

Staff sickness - Only available at trust level

Staff turnover - Only available at trust level - Data is only available for Royal Liverpool

Staff survey - Only available at trust level - This is an annual measure, so there are limited data points in the pre-switch period and only 1 or 2 points in the outcome period.

## C.List of control sites/providers by indicator

## D.Provider and site codes?

------------------------------------------------------------------------
