---
title: "NHP Royal Liverpool Length of Stay"
author: "Andrew Hood and Jacqueline Grout"
editor: visual
execute:
  echo: false
  message: false
  warning: false
lang: en-GB
date: last-modified
date-format: "YYYY-MM-DD"
title-block-banner: "#f9bf07"
title-block-banner-color: "#333739"
format:
  html:
    embed-resources: true
    smooth-scroll: true
    theme: cosmo
    fontcolor: black
    toc: true
    toc-location: left
    toc-title: Summary
    toc-depth: 3
    callout-icon: false
    
css: styles.css
---

## Introduction

dhfjshglsjlgjsndgsfgsgd

## Time-Series

Time-series analysis to compare the lengths of

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

## Control Group

Other hospitals analysis considering any variation in lengths of stay between Royal Liverpool and other hospitals in the region:

-   Aintree

-   Whiston

-   Warrington

-   Southport and Formby

-   Ormskirk and district

-   Countess of Chester

## Case-mix

Case mix analysis using main specialty
