---
title: "NHP Royal Liverpool Length of Stay"
author: "Andrew Hood and Jacqueline Grout"
editor: visual
execute:
  echo: false
  message: false
  warning: false
lang: en-GB
date: last-modified
date-format: "YYYY-MM-DD"
title-block-banner: "#f9bf07"
title-block-banner-color: "#333739"
format:
  html:
    embed-resources: true
    smooth-scroll: true
    theme: cosmo
    fontcolor: black
    toc: true
    toc-location: left
    toc-title: Summary
    toc-depth: 3
    callout-icon: false
    
css: styles.css
---

```{r load_packages}
#| include: false
#| 
library(tidyverse)
library(janitor)

```

```{r load_clean_data}
#| include: false

df <- read.csv("single_room_extract.csv") |> 
  clean_names() |>
  mutate(wk_2 = ifelse(wk<10, paste0(0,wk), wk)) |> 
  mutate(yyyy_wk = paste0(yr,"-",wk_2)) |> 
  mutate(avg_los = round(spell_los / spells,2))

# add table to get unique period number for year-wk
periods <- df |>
  group_by(yr,wk) |> 
  distinct(yyyy_wk) |>
  ungroup() |> 
  arrange(yr, wk) |> 
  mutate(n_period = row_number())

df <- df |> 
  left_join(periods |> select(yyyy_wk, n_period), by = "yyyy_wk") |> 
  mutate(yyyy_wk = fct_reorder(yyyy_wk, n_period))

rm(periods)

df_pre <- df |> 
  filter(between(n_period,72 ,136))

df_post <- df |> 
  filter(n_period > 136)

```

```{r site_plot_function}
#| include: false

fun_site_plot <- function(sitecode, sitename){
  
df |> 
  filter(der_provider_site_code == sitecode, adm_meth_desc != 'other', between(n_period, 72, 181)) |> 
  group_by(der_provider_site_code, yr, wk, yyyy_wk, n_period) |> 
  summarise(spells = sum(spells)
            ,spell_los = sum(spell_los)) |> 
  ungroup() |> 
  mutate(avg_los = round(spell_los / spells,2)) |>
  ggplot(aes(x=fct_reorder(yyyy_wk, n_period), y=avg_los, group = 1)) +
  geom_smooth(data = df_pre |> 
      filter(der_provider_site_code == sitecode, adm_meth_desc != 'other') |> 
      group_by(der_provider_site_code, yr, wk, yyyy_wk, n_period) |> 
      summarise(spells = sum(spells)
                ,spell_los = sum(spell_los)) |> 
      ungroup() |> 
      mutate(avg_los = round(spell_los / spells,2)), aes(x=fct_reorder(yyyy_wk, n_period), y=avg_los), method = "lm", fullrange = TRUE, color="#ec6555", linetype = "dashed", se = FALSE) +
  geom_smooth(data = df_post |> 
      filter(der_provider_site_code == sitecode, adm_meth_desc != 'other') |> 
      group_by(der_provider_site_code, yr, wk, yyyy_wk, n_period) |> 
      summarise(spells = sum(spells)
                ,spell_los = sum(spell_los)) |> 
      ungroup() |> 
      mutate(avg_los = round(spell_los / spells,2)), aes(x=fct_reorder(yyyy_wk, n_period), y=avg_los), method = "lm", color="#ABDDA4", linetype = "dashed", se = FALSE) +
  geom_line(colour = "#f9bf07") +
  geom_point(colour = "#686F73", alpha = 0.4) +
  geom_vline(xintercept = "2022-43", colour = "blue") +
  expand_limits(y=0) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size = 5)
        ,panel.grid = element_blank()) +
  labs(title = "Average length of stay (days) by week"
      ,subtitle = paste0(sitename, " hospital, Aug 2021 to Aug 2023")
      ,caption = "blue line indicates week of site switch"
      ,x = "Year and week"
      ,y = "LoS in days")
}
```

## Introduction

The New Hospitals Programme (NHP) team have asked the Strategy Unit to provide some insight as the potential effect on length of stay of single-bed rooms compared to multi-bed rooms or wards. The following is a brief exploratory analysis of length of stay patterns for admitted patients at Royal Liverpool hospital.

The Royal Liverpool is the only hospital in recent memory to have made this switch in bed composition and therefore makes a useful case study.

Through necessity, this analysis is crude and carries significant caveats and limitations. However; it may be indicative that the theory has some credit and that more robust in-depth work is required to quantify the potential impact on whole hospital or sub-hospital populations that may be considered in future bed modelling.

## Length of stay pattern over time

In order to observe the potential change in length of stay patterns in multi-bed wards and rooms in the old hospital compared to single-bed rooms in the new hospital, we plot the length of stay averages by week of all the patients admitted to Royal Liverpool (REMRQ) between August 2021 (end of legal covid restrictions) and August 2023.

The week of transition between the old and new hospital (officially the 20th October 2022) is indicated by a vertical blue line on the plots.

```{r overall_trends}

fun_site_plot("REMRQ","Royal Liverpool")

```

## Control Group

One limitation of considering only the activity at the Royal Liverpool hospital over the specified time period is that the effects might be similar elsewhere and therefore the single/multiple bedded rooms might not be a variable of influence. 

To test this, we have extracted and present the same set of activity for the 5 nearest other hospitals providing general acute services to (among others) patients from Liverpool:

-   Aintree

-   Whiston

-   Southport and Formby

-   Ormskirk and district

-   Countess of Chester

:::panel-tabset

### Aintree

```{r control_hospital_aintree}

fun_site_plot("REM21","Aintree University")

```

### Whiston

```{r control_hospital_whiston}

fun_site_plot("RBN01","Whiston")

```

### Southport & Formby

```{r control_hospital_southport}

fun_site_plot("RVY01","Southport & Formby")

```

### Ormskirk & District

```{r control_hospital_ormskirk}

fun_site_plot("RVY02","Ormskirk & District")

```

### Countess Chester

```{r control_hospital_chester}

fun_site_plot("RJR05","Countess of Chester")

```

:::

## Case-mix

Case mix analysis using main specialty

```{r}
df_top_10_elective <- df |>
  filter(der_provider_site_code == "REMRQ") |> 
  filter(adm_meth_desc == "elective") |>
  group_by(der_admit_treatment_function_code) |>
  summarise(spells_total = sum(spells))|>
  ungroup() |>
slice_max(spells_total, n = 10)

df_top_10_nonelective <- df |>
  filter(der_provider_site_code == "REMRQ") |> 
  filter(adm_meth_desc == "non_elective") |>
  group_by(der_admit_treatment_function_code) |>
  summarise(spells_total = sum(spells))|>
  ungroup() |>
  slice_max(spells_total, n = 10)

top_10_elective <- df_top_10_elective$der_admit_treatment_function_code
top_10_nonelective <- df_top_10_nonelective$der_admit_treatment_function_code





```

::: panel-tabset
## Elective

```{r}
df |> 
  filter(der_provider_site_code == "REMRQ", adm_meth_desc != 'other') |>
  filter(adm_meth_desc == "elective") |>
  filter(der_admit_treatment_function_code %in% top_10_elective)|>
  group_by(der_provider_site_code, der_admit_treatment_function_code, yr, wk, yyyy_wk, n_period) |> 
  summarise(spells = sum(spells)
            ,spell_los = sum(spell_los)) |> 
  ungroup() |> 
  mutate(avg_los = round(spell_los / spells,2)) |>
  ggplot(aes(x=fct_reorder(yyyy_wk, n_period), y=avg_los, group = 1)) +
  geom_line(colour = "#f9bf07") +
  geom_point(colour = "#686F73") +
  geom_vline(xintercept = "2022-43", colour = "blue") +
  facet_wrap(vars(der_admit_treatment_function_code), scales = "free") + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size = 5)) +
  labs(title = "Average length of stay (days) by week and top 10 elective main specialties"
       ,subtitle = "Royal Liverpool Hospital, Aug 2021 to Aug 2023"
       ,caption = "blue line indicates week of site switch") 
```

## Non-elective

```{r}
df |> 
  filter(der_provider_site_code == "REMRQ", adm_meth_desc != 'other') |>
  filter(adm_meth_desc == "non_elective") |>
  filter(der_admit_treatment_function_code %in% top_10_nonelective)|>
  group_by(der_provider_site_code, der_admit_treatment_function_code, yr, wk, yyyy_wk, n_period) |> 
  summarise(spells = sum(spells)
            ,spell_los = sum(spell_los)) |> 
  ungroup() |> 
  mutate(avg_los = round(spell_los / spells,2)) |>
  ggplot(aes(x=fct_reorder(yyyy_wk, n_period), y=avg_los, group = 1)) +
  geom_line(colour = "#f9bf07") +
  geom_point(colour = "#686F73") +
  geom_vline(xintercept = "2022-43", colour = "blue") +
  facet_wrap(vars(der_admit_treatment_function_code), scales = "free") + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size = 5)) +
  labs(title = "Average length of stay (days) by week and top 10 elective main specialties"
       ,subtitle = "Royal Liverpool Hospital, Aug 2021 to Aug 2023"
       ,caption = "blue line indicates week of site switch") 
```
:::
