---
title: "NHP Royal Liverpool Length of Stay"
author: "Andrew Hood and Jacqueline Grout"
editor: visual
execute:
  echo: false
  message: false
  warning: false
lang: en-GB
date: last-modified
date-format: "YYYY-MM-DD"
title-block-banner: "#f9bf07"
title-block-banner-color: "#333739"
format:
  html:
    embed-resources: true
    smooth-scroll: true
    theme: cosmo
    fontcolor: black
    toc: true
    toc-location: left
    toc-title: Summary
    toc-depth: 3
    callout-icon: false
    
css: styles.css
---

```{r load_packages, include = false}
library(tidyverse)
library(janitor)

```

```{r load_clean_data, include = false}

df <- read.csv("single_room_extract.csv") |> 
  clean_names() |>
  mutate(yyyy_wk = paste0(yr,"-",wk)) |> 
  mutate(avg_los = round(spell_los / spells,2))

# add table to get unique period number for year-wk
periods <- df |>
  group_by(yr,wk) |> 
  distinct(yyyy_wk) |>
  ungroup() |> 
  arrange(yr, wk) |> 
  mutate(n_period = row_number())

df <- df |> 
  left_join(periods |> select(yyyy_wk, n_period), by = "yyyy_wk")

rm(periods)

```


## Introduction

dhfjshglsjlgjsndgsfgsgd

## Time-Series

Time-series analysis to compare the lengths of

```{r}
df |> 
  filter(der_provider_site_code == "REMRQ", adm_meth_desc != 'other') |> 
  group_by(der_provider_site_code, yr, wk, yyyy_wk, n_period) |> 
  summarise(spells = sum(spells)
            ,spell_los = sum(spell_los)) |> 
  ungroup() |> 
  mutate(avg_los = round(spell_los / spells,2)) |>
  ggplot(aes(x=fct_reorder(yyyy_wk, n_period), y=avg_los, group = 1)) +
  geom_line(colour = "#f9bf07") +
  geom_point(colour = "#686F73") +
  geom_vline(xintercept = "2022-43", colour = "blue") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size = 5)) +
  labs(title = "Average length of stay (days) by week"
         ,subtitle = "Royal Liverpool Hospital, Aug 2021 to Aug 2023"
       ,caption = "blue line indicates week of site switch")
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

## Control Group

Other hospitals analysis considering any variation in lengths of stay between Royal Liverpool and other hospitals in the region:

-   Aintree

-   Whiston

-   Warrington

-   Southport and Formby

-   Ormskirk and district

-   Countess of Chester

## Case-mix

Case mix analysis using main specialty
