---
title: "Site by Indicator charts"
format: html
execute: 
  echo: false
  warning: false
embed-resources: true
---

```{r}
library(targets)
library(plotly)
```


For all the charts below:

-   The black line is the trend for the hospital of interest
-   The grey lines are the trends for each control for the hospital of interest
-   The blue line is for the onset of COVID-19
-   The purple line is for the month where the hospital of interest introduced 
single bedrooms

::: panel-tabset
## Bed occupancy

These are the charts for bed occupancy percentage, taken from the quarterly [KH03 collection](https://www.england.nhs.uk/statistics/statistical-work-areas/bed-availability-and-occupancy/bed-availability-and-occupancy-kh03/).

### Royal Liverpool

```{r}
tar_read(plot_bed_occupancy_royal_liverpool) |> 
  ggplotly()
```

### Clatterbridge

```{r}
tar_read(plot_bed_occupancy_clatterbridge) |> 
  ggplotly()
```

### Royal Papworth

```{r}
tar_read(plot_bed_occupancy_royal_papworth) |> 
  ggplotly()
```

### Peterborough

```{r}
tar_read(plot_bed_occupancy_peterborough) |> 
  ggplotly()
```

### Chase Farm

```{r}
tar_read(plot_bed_occupancy_chase_farm) |> 
  ggplotly()
```

### Southmead

```{r}
tar_read(plot_bed_occupancy_southmead) |> 
  ggplotly()
```

### Tunbridge Wells

```{r}
tar_read(plot_bed_occupancy_tunbridge_wells) |> 
  ggplotly()
```

## Cleaning staff

These are the charts for cleaning staff WTE, taken from the annual [Estates 
Returns Information Collection](https://digital.nhs.uk/data-and-information/publications/statistical/estates-returns-information-collection).

### Royal Liverpool

```{r}
tar_read(plot_cleaning_staff_royal_liverpool) |> 
  ggplotly()
```

### Clatterbridge

```{r}
tar_read(plot_cleaning_staff_clatterbridge) |> 
  ggplotly()
```

### Royal Papworth

```{r}
tar_read(plot_cleaning_staff_royal_papworth) |> 
  ggplotly()
```

### Peterborough

```{r}
tar_read(plot_cleaning_staff_peterborough) |> 
  ggplotly()
```

### Chase Farm

```{r}
tar_read(plot_cleaning_staff_chase_farm) |> 
  ggplotly()
```

### Southmead

```{r}
tar_read(plot_cleaning_staff_southmead) |> 
  ggplotly()
```

### Tunbridge Wells

```{r}
tar_read(plot_cleaning_staff_tunbridge_wells) |> 
  ggplotly()
```

## Falls and Fractures

These are the charts for the number of falls and fractures per 10000 beddays.

### Royal Liverpool

```{r}
tar_read(plot_falls_and_fractures_royal_liverpool) |> 
  ggplotly()
```

### Clatterbridge

```{r}
tar_read(plot_falls_and_fractures_clatterbridge) |> 
  ggplotly()
```

### Royal Papworth

```{r}
tar_read(plot_falls_and_fractures_royal_papworth) |> 
  ggplotly()
```

### Peterborough

```{r}
tar_read(plot_falls_and_fractures_peterborough) |> 
  ggplotly()
```

### Chase Farm

```{r}
tar_read(plot_falls_and_fractures_chase_farm) |> 
  ggplotly()
```

### Southmead

```{r}
tar_read(plot_falls_and_fractures_southmead) |> 
  ggplotly()
```

### Tunbridge Wells

```{r}
tar_read(plot_falls_and_fractures_tunbridge_wells) |> 
  ggplotly()
```

## HCAI

These are the charts for the contributed rate of Healthcare associated 
Infections (HCAI) over time. For each of the bacteria below a rate of the number
of cases divided by the number of 10000 beddays was calculated:

-   Clostridium difficile
-   Klebsiella
-   Ecoli
-   MSSA
-   MRSA
-   Pseudomonas Aeruginosa

The combined rate of HCAI was calculated as the sum of the above rates.

### Royal Liverpool

```{r}
tar_read(plot_hcai_royal_liverpool) |> 
  ggplotly()
```

### Clatterbridge

```{r}
tar_read(plot_hcai_clatterbridge) |> 
  ggplotly()
```

### Royal Papworth

```{r}
tar_read(plot_hcai_royal_papworth) |> 
  ggplotly()
```

### Peterborough

```{r}
tar_read(plot_hcai_peterborough) |> 
  ggplotly()
```

### Chase Farm

```{r}
tar_read(plot_hcai_chase_farm) |> 
  ggplotly()
```

### Southmead

```{r}
tar_read(plot_hcai_southmead) |> 
  ggplotly()
```

### Tunbridge Wells

```{r}
tar_read(plot_hcai_tunbridge_wells) |> 
  ggplotly()
```

## Length of Stay

These are the charts for the average length of stay of all admissions in that 
month.

### Royal Liverpool

```{r}
tar_read(plot_length_of_stay_royal_liverpool) |> 
  ggplotly()
```

### Clatterbridge

```{r}
tar_read(plot_length_of_stay_clatterbridge) |> 
  ggplotly()
```

### Royal Papworth

```{r}
tar_read(plot_length_of_stay_royal_papworth) |> 
  ggplotly()
```

### Peterborough

```{r}
tar_read(plot_length_of_stay_peterborough) |> 
  ggplotly()
```

### Chase Farm

```{r}
tar_read(plot_length_of_stay_chase_farm) |> 
  ggplotly()
```

### Southmead

```{r}
tar_read(plot_length_of_stay_southmead) |> 
  ggplotly()
```

### Tunbridge Wells

```{r}
tar_read(plot_length_of_stay_tunbridge_wells) |> 
  ggplotly()
```

## Mortality

These are the charts for the number of deaths in hospital per 1000 admissions.

### Royal Liverpool

```{r}
tar_read(plot_sus_deaths_royal_liverpool) |> 
  ggplotly()
```

### Clatterbridge

```{r}
tar_read(plot_sus_deaths_clatterbridge) |> 
  ggplotly()
```

### Royal Papworth

```{r}
tar_read(plot_sus_deaths_royal_papworth) |> 
  ggplotly()
```

### Peterborough

```{r}
tar_read(plot_sus_deaths_peterborough) |> 
  ggplotly()
```

### Chase Farm

```{r}
tar_read(plot_sus_deaths_chase_farm) |> 
  ggplotly()
```

### Southmead

```{r}
tar_read(plot_sus_deaths_southmead) |> 
  ggplotly()
```

### Tunbridge Wells

```{r}
tar_read(plot_sus_deaths_tunbridge_wells) |> 
  ggplotly()
```

## Patient experience

These are the charts for the percentage of positive responses in the friends and
family test.

### Royal Liverpool

```{r}
tar_read(plot_friends_and_family_royal_liverpool) |> 
  ggplotly()
```

### Clatterbridge

```{r}
tar_read(plot_friends_and_family_clatterbridge) |> 
  ggplotly()
```

### Royal Papworth

```{r}
tar_read(plot_friends_and_family_royal_papworth) |> 
  ggplotly()
```

### Peterborough

```{r}
tar_read(plot_friends_and_family_peterborough) |> 
  ggplotly()
```

### Chase Farm

```{r}
tar_read(plot_friends_and_family_chase_farm) |> 
  ggplotly()
```

### Southmead

```{r}
tar_read(plot_friends_and_family_southmead) |> 
  ggplotly()
```

### Tunbridge Wells

```{r}
tar_read(plot_friends_and_family_tunbridge_wells) |> 
  ggplotly()
```

## Staff turnover

These are the charts for the number of staff leavers over the number of staff.

### Royal Liverpool

```{r}
tar_read(plot_staff_turnover_royal_liverpool) |> 
  ggplotly()
```

### Clatterbridge

```{r}
tar_read(plot_staff_turnover_clatterbridge) |> 
  ggplotly()
```

### Royal Papworth

```{r}
tar_read(plot_staff_turnover_royal_papworth) |> 
  ggplotly()
```

### Peterborough

```{r}
tar_read(plot_staff_turnover_peterborough) |> 
  ggplotly()
```

### Chase Farm

```{r}
tar_read(plot_staff_turnover_chase_farm) |> 
  ggplotly()
```

### Southmead

```{r}
tar_read(plot_staff_turnover_southmead) |> 
  ggplotly()
```

### Tunbridge Wells

```{r}
tar_read(plot_staff_turnover_tunbridge_wells) |> 
  ggplotly()
```

## Staff sickness absence

These are the charts for the percentage of staff absences due to sickness.

### Royal Liverpool

```{r}
tar_read(plot_staff_sickness_royal_liverpool) |> 
  ggplotly()
```

### Clatterbridge

```{r}
tar_read(plot_staff_sickness_clatterbridge) |> 
  ggplotly()
```

### Royal Papworth

```{r}
tar_read(plot_staff_sickness_royal_papworth) |> 
  ggplotly()
```

### Peterborough

```{r}
tar_read(plot_staff_sickness_peterborough) |> 
  ggplotly()
```

### Chase Farm

```{r}
tar_read(plot_staff_sickness_chase_farm) |> 
  ggplotly()
```

### Southmead

```{r}
tar_read(plot_staff_sickness_southmead) |>
  ggplotly()
```

### Tunbridge Wells

```{r}
tar_read(plot_staff_sickness_tunbridge_wells) |> 
  ggplotly()
```

## Waiting time

These are the charts for the median RTT waiting time in weeks.

### Royal Liverpool

```{r}
tar_read(plot_rtt_waiting_time_royal_liverpool) |> 
  ggplotly()
```

### Clatterbridge

```{r}
tar_read(plot_rtt_waiting_time_clatterbridge) |> 
  ggplotly()
```

### Royal Papworth

```{r}
tar_read(plot_rtt_waiting_time_royal_papworth) |> 
  ggplotly()
```

### Peterborough

```{r}
tar_read(plot_rtt_waiting_time_peterborough) |> 
  ggplotly()
```

### Chase Farm

```{r}
tar_read(plot_rtt_waiting_time_chase_farm) |> 
  ggplotly()
```

### Southmead

```{r}
tar_read(plot_rtt_waiting_time_southmead) |> 
  ggplotly()
```

### Tunbridge Wells

```{r}
tar_read(plot_rtt_waiting_time_tunbridge_wells) |> 
  ggplotly()
```
:::

## Overall Notes

-   COVID-19 has affected all measures
-   We do not have enough/any data pre SBR for some sites
-   Code for bed occupancy excludes the annual groups
-   For turnover, should we look at joiners as well as leavers?
-   Friends and family and falls and fractures have NaN, probably because of 
zero denominators
-   Missing Readmissions
