---
title: "Site by Indicator charts"
format: html
execute: 
  echo: false
  warning: false
embed-resources: true
editor: 
  markdown: 
    wrap: 72
---

```{r}
library(targets)
library(plotly)
```

# The intervention sites and their control matches

The following maps demonstrate the location of the intervention sites
across England and then, for each one individually, show where the
current set of control sites are.

Currently, the controls are matched according to whether they are part
of a sub-set of specialty providers e.g. cancer or cardiothoracic and
then having a similar % of single-bed inpatient rooms prior to the
switch.

The next iteration of this matching of control sites will include
factors on hospital size and patient case-mix to improve the suitability
of comparisons fed into the Causal Impact Analysis.

```{r overview_map}
tar_read(map_all_sites)
```

\

::: panel-tabset
## Royal Liverpool

```{r royal_liverpool_map}
tar_read(map_REM)
```

## Clatterbridge

```{r clatterbridge_map}
tar_read(map_REN)
```

## Royal Papworth

```{r royal_papworth_map}
tar_read(map_RGM)
```

## Peterborough

```{r peterborough_map}
tar_read(map_RGN)
```

## Chase Farm

```{r chase_farm_map}
tar_read(map_RAL)
```

## Southmead

```{r southmead_map}
tar_read(map_RVJ)
```

## Tunbridge Wells

```{r tunbridge_wells_map}
tar_read(map_RWF)
```
:::

# The trends for each impact measure

For all the indicator charts below:

-   The black line is the trend for the hospital of interest
-   The grey lines are the trends for each control for the hospital of
    interest
-   The blue line is for the onset of COVID-19
-   The orange line is for the month where the hospital of interest
    introduced single bedrooms

::: panel-tabset
## Bed occupancy

These are the charts for bed occupancy percentage, taken from the
quarterly [KH03
collection](https://www.england.nhs.uk/statistics/statistical-work-areas/bed-availability-and-occupancy/bed-availability-and-occupancy-kh03/).

### Royal Liverpool

```{r royal_liverpool_bed_occupancy}
tar_read(plot_bed_occupancy_REM) |> 
  ggplotly()
```

### Clatterbridge

```{r clatterbridge_bed_occupancy}
tar_read(plot_bed_occupancy_REN) |> 
  ggplotly()
```

### Royal Papworth

```{r royal_papworth_bed_occupancy}
tar_read(plot_bed_occupancy_RGM) |> 
  ggplotly()
```

### Peterborough

```{r peterborough_bed_occupancy}
tar_read(plot_bed_occupancy_RGN) |> 
  ggplotly()
```

### Chase Farm

```{r chase_farm_bed_occupancy}
tar_read(plot_bed_occupancy_RAL) |> 
  ggplotly()
```

### Southmead

```{r southmead_bed_occupancy}
tar_read(plot_bed_occupancy_RVJ) |> 
  ggplotly()
```

### Tunbridge Wells

```{r tunbridge_wells_bed_occupancy}
tar_read(plot_bed_occupancy_RWF) |> 
  ggplotly()
```

## Cleaning service costs

These are the charts for cleaning service costs, taken from the annual
[Estates Returns Information
Collection](https://digital.nhs.uk/data-and-information/publications/statistical/estates-returns-information-collection).

### Royal Liverpool

```{r royal_liverpool_cleaning_costs}
tar_read(plot_cleaning_costs_REM) |> 
  ggplotly()
```

### Clatterbridge

```{r clatterbridge_cleaning_costs}
tar_read(plot_cleaning_costs_REN) |> 
  ggplotly()
```

### Royal Papworth

```{r royal_papworth_cleaning_costs}
tar_read(plot_cleaning_costs_RGM) |> 
  ggplotly()
```

### Peterborough

```{r peterborough_cleaning_costs}
tar_read(plot_cleaning_costs_RGN) |> 
  ggplotly()
```

### Chase Farm

```{r chase_farm_cleaning_costs}
tar_read(plot_cleaning_costs_RAL) |> 
  ggplotly()
```

### Southmead

```{r southmead_cleaning_costs}
tar_read(plot_cleaning_costs_RVJ) |> 
  ggplotly()
```

### Tunbridge Wells

```{r tunbridge_cleaning_costs}
tar_read(plot_cleaning_costs_RWF) |> 
  ggplotly()
```

## Cleaning staff

These are the charts for cleaning staff WTE, taken from the annual
[Estates Returns Information
Collection](https://digital.nhs.uk/data-and-information/publications/statistical/estates-returns-information-collection).

### Royal Liverpool

```{r royal_liverpool_cleaning_staff}
tar_read(plot_cleaning_staff_REM) |> 
  ggplotly()
```

### Clatterbridge

```{r clatterbridge_cleaning_staff}
tar_read(plot_cleaning_staff_REN) |> 
  ggplotly()
```

### Royal Papworth

```{r royal_papworth_cleaning_staff}
tar_read(plot_cleaning_staff_RGM) |> 
  ggplotly()
```

### Peterborough

```{r peterborough_cleaning_staff}
tar_read(plot_cleaning_staff_RGN) |> 
  ggplotly()
```

### Chase Farm

```{r chase_farm_cleaning_staff}
tar_read(plot_cleaning_staff_RAL) |> 
  ggplotly()
```

### Southmead

```{r southmead_cleaning_staff}
tar_read(plot_cleaning_staff_RVJ) |> 
  ggplotly()
```

### Tunbridge Wells

```{r tunbridge_wells_cleaning_staff}
tar_read(plot_cleaning_staff_RWF) |> 
  ggplotly()
```

## Falls and Fractures

These are the charts for the number of falls and fractures per 10000
beddays.

### Royal Liverpool

```{r royal_liverpool_falls_and_fractures}
tar_read(plot_falls_and_fractures_REM) |> 
  ggplotly()
```

### Clatterbridge

```{r clatterbridge_falls_and_fractures}
tar_read(plot_falls_and_fractures_REN) |> 
  ggplotly()
```

### Royal Papworth

```{r royal_papworth_falls_and_fractures}
tar_read(plot_falls_and_fractures_RGM) |> 
  ggplotly()
```

### Peterborough

```{r peterborough_falls_and_fractures}
tar_read(plot_falls_and_fractures_RGN) |> 
  ggplotly()
```

### Chase Farm

```{r chase_farm_falls_and_fractures}
tar_read(plot_falls_and_fractures_RAL) |> 
  ggplotly()
```

### Southmead

```{r southmead_falls_and_fractures}
tar_read(plot_falls_and_fractures_RVJ) |> 
  ggplotly()
```

### Tunbridge Wells

```{r tunbridge_wells_falls_and_fractures}
tar_read(plot_falls_and_fractures_RWF) |> 
  ggplotly()
```

## HCAI

These are the charts for the contributed rate of Healthcare associated
Infections (HCAI) over time. For each of the bacteria below a rate of
the number of cases divided by the number of 10000 beddays was
calculated:

-   Clostridium difficile
-   Klebsiella
-   Ecoli
-   MSSA
-   MRSA
-   Pseudomonas Aeruginosa

The combined rate of HCAI was calculated as the sum of the above rates.

### Royal Liverpool

```{r royal_liverpool_hcai}
tar_read(plot_hcai_REM) |> 
  ggplotly()
```

### Clatterbridge

```{r clatterbridge_hcai}
tar_read(plot_hcai_REN) |> 
  ggplotly()
```

### Royal Papworth

```{r royal_papworth_hcai}
tar_read(plot_hcai_RGM) |> 
  ggplotly()
```

### Peterborough

```{r peterborough_hcai}
tar_read(plot_hcai_RGN) |> 
  ggplotly()
```

### Chase Farm

```{r chase_farm_hcai}
tar_read(plot_hcai_RAL) |> 
  ggplotly()
```

### Southmead

```{r southmead_hcai}
tar_read(plot_hcai_RVJ) |> 
  ggplotly()
```

### Tunbridge Wells

```{r tunbridge_wells_hcai}
tar_read(plot_hcai_RWF) |> 
  ggplotly()
```

## Length of Stay

These are the charts for the average length of stay of all admissions in
that month.

### Royal Liverpool

```{r royal_liverpool_length_of_stay}
tar_read(plot_length_of_stay_REM) |> 
  ggplotly()
```

### Clatterbridge

```{r clatterbridge_length_of_stay}
tar_read(plot_length_of_stay_REN) |> 
  ggplotly()
```

### Royal Papworth

```{r royal_papworth_length_of_stay}
tar_read(plot_length_of_stay_RGM) |> 
  ggplotly()
```

### Peterborough

```{r peterborough_length_of_stay}
tar_read(plot_length_of_stay_RGN) |> 
  ggplotly()
```

### Chase Farm

```{r chase_farm_length_of_stay}
tar_read(plot_length_of_stay_RAL) |> 
  ggplotly()
```

### Southmead

```{r southmead_length_of_stay}
tar_read(plot_length_of_stay_RVJ) |> 
  ggplotly()
```

### Tunbridge Wells

```{r tunbridge_wells_length_of_stay}
tar_read(plot_length_of_stay_RWF) |> 
  ggplotly()
```

## Mortality

These are the charts for the number of deaths in hospital per 1000
admissions.

### Royal Liverpool

```{r royal_liverpool_sus_deaths}
tar_read(plot_sus_deaths_REM) |> 
  ggplotly()
```

### Clatterbridge

```{r clatterbridge_sus_deaths}
tar_read(plot_sus_deaths_REN) |> 
  ggplotly()
```

### Royal Papworth

```{r royal_papworth_sus_deaths}
tar_read(plot_sus_deaths_RGM) |> 
  ggplotly()
```

### Peterborough

```{r peterborough_sus_deaths}
tar_read(plot_sus_deaths_RGN) |> 
  ggplotly()
```

### Chase Farm

```{r chase_farm_sus_deaths}
tar_read(plot_sus_deaths_RAL) |> 
  ggplotly()
```

### Southmead

```{r southmead_sus_deaths}
tar_read(plot_sus_deaths_RVJ) |> 
  ggplotly()
```

### Tunbridge Wells

```{r tunbridge_wells_sus_deaths}
tar_read(plot_sus_deaths_RWF) |> 
  ggplotly()
```

## Patient experience

These are the charts for the percentage of positive responses in the
friends and family test.

### Royal Liverpool

```{r royal_liverpool_friends_and_family}
tar_read(plot_friends_and_family_REM) |> 
  ggplotly()
```

### Clatterbridge

```{r clatterbridge_friends_and_family}
tar_read(plot_friends_and_family_REN) |> 
  ggplotly()
```

### Royal Papworth

```{r royal_papworth_friends_and_family}
tar_read(plot_friends_and_family_RGM) |> 
  ggplotly()
```

### Peterborough

```{r peterborough_friends_and_family}
tar_read(plot_friends_and_family_RGN) |> 
  ggplotly()
```

### Chase Farm

```{r chase_farm_friends_and_family}
tar_read(plot_friends_and_family_RAL) |> 
  ggplotly()
```

### Southmead

```{r southmead_friends_and_family}
tar_read(plot_friends_and_family_RVJ) |> 
  ggplotly()
```

### Tunbridge Wells

```{r tunbridge_wells_friends_and_family}
tar_read(plot_friends_and_family_RWF) |> 
  ggplotly()
```

## Readmissions

These are the charts for the percentage of emergency readmissions.

### Royal Liverpool

```{r royal_liverpool_emergency_readmissions}
tar_read(plot_emergency_readmissions_REM) |> 
  ggplotly()
```

### Clatterbridge

```{r clatterbridge_emergency_readmissions}
tar_read(plot_emergency_readmissions_REN) |> 
  ggplotly()
```

### Royal Papworth

```{r royal_papworth_emergency_readmissions}
tar_read(plot_emergency_readmissions_RGM) |> 
  ggplotly()
```

### Peterborough

```{r peterborough_emergency_readmissions}
tar_read(plot_emergency_readmissions_RGN) |> 
  ggplotly()
```

### Chase Farm

```{r chase_farm_emergency_readmissions}
tar_read(plot_emergency_readmissions_RAL) |> 
  ggplotly()
```

### Southmead

```{r southmead_emergency_readmissions}
tar_read(plot_emergency_readmissions_RVJ) |> 
  ggplotly()
```

### Tunbridge Wells

```{r tunbridge_wells_emergency_readmissions}
tar_read(plot_emergency_readmissions_RWF) |> 
  ggplotly()
```

## Staff turnover

These are the charts for the number of staff leavers over the number of
staff.

### Royal Liverpool

```{r royal_liverpool_staff_turnover}
tar_read(plot_staff_turnover_REM) |> 
  ggplotly()
```

### Clatterbridge

```{r clatterbridge_staff_turnover}
tar_read(plot_staff_turnover_REN) |> 
  ggplotly()
```

### Royal Papworth

```{r royal_papworth_staff_turnover}
tar_read(plot_staff_turnover_RGM) |> 
  ggplotly()
```

### Peterborough

```{r peterborough_staff_turnover}
tar_read(plot_staff_turnover_RGN) |> 
  ggplotly()
```

### Chase Farm

```{r chase_farm_staff_turnover}
tar_read(plot_staff_turnover_RAL) |> 
  ggplotly()
```

### Southmead

```{r southmead_staff_turnover}
tar_read(plot_staff_turnover_RVJ) |> 
  ggplotly()
```

### Tunbridge Wells

```{r tunbridge_wells_staff_turnover}
tar_read(plot_staff_turnover_RWF) |> 
  ggplotly()
```

## Staff sickness absence

These are the charts for the percentage of staff absences due to
sickness.

### Royal Liverpool

```{r royal_liverpool_staff_sickness}
tar_read(plot_staff_sickness_REM) |> 
  ggplotly()
```

### Clatterbridge

```{r clatterbridge_staff_sickness}
tar_read(plot_staff_sickness_REN) |> 
  ggplotly()
```

### Royal Papworth

```{r royal_papworth_staff_sickness}
tar_read(plot_staff_sickness_RGM) |> 
  ggplotly()
```

### Peterborough

```{r peterborough_staff_sickness}
tar_read(plot_staff_sickness_RGN) |> 
  ggplotly()
```

### Chase Farm

```{r chase_farm_staff_sickness}
tar_read(plot_staff_sickness_RAL) |> 
  ggplotly()
```

### Southmead

```{r southmead_staff_sickness}
tar_read(plot_staff_sickness_RVJ) |>
  ggplotly()
```

### Tunbridge Wells

```{r tunbridge_wells_staff_sickness}
tar_read(plot_staff_sickness_RWF) |> 
  ggplotly()
```

## Staff survey

These are the charts for the percentage of positive responses to the staff 
survey.

### Royal Liverpool

```{r royal_liverpool_staff_survey}
tar_read(plot_staff_survey_REM) |> 
  ggplotly()
```

### Clatterbridge

```{r clatterbridge_staff_survey}
tar_read(plot_staff_survey_REN) |> 
  ggplotly()
```

### Royal Papworth

```{r royal_papworth_staff_survey}
tar_read(plot_staff_survey_RGM) |> 
  ggplotly()
```

### Peterborough

```{r peterborough_staff_survey}
tar_read(plot_staff_survey_RGN) |> 
  ggplotly()
```

### Chase Farm

```{r chase_farm_staff_survey}
tar_read(plot_staff_survey_RAL) |> 
  ggplotly()
```

### Southmead

```{r southmead_staff_survey}
tar_read(plot_staff_survey_RVJ) |>
  ggplotly()
```

### Tunbridge Wells

```{r tunbridge_wells_staff_survey}
tar_read(plot_staff_survey_RWF) |> 
  ggplotly()
```

## Waiting time

These are the charts for the median RTT waiting time in weeks.

### Royal Liverpool

```{r royal_liverpool_rtt_waiting_time}
tar_read(plot_rtt_waiting_time_REM) |> 
  ggplotly()
```

### Clatterbridge

```{r clatterbridge_rtt_waiting_time}
tar_read(plot_rtt_waiting_time_REN) |> 
  ggplotly()
```

### Royal Papworth

```{r royal_papworth_rtt_waiting_time}
tar_read(plot_rtt_waiting_time_RGM) |> 
  ggplotly()
```

### Peterborough

```{r peterborough_rtt_waiting_time}
tar_read(plot_rtt_waiting_time_RGN) |> 
  ggplotly()
```

### Chase Farm

```{r chase_farm_rtt_waiting_time}
tar_read(plot_rtt_waiting_time_RAL) |> 
  ggplotly()
```

### Southmead

```{r southmead_rtt_waiting_time}
tar_read(plot_rtt_waiting_time_RVJ) |> 
  ggplotly()
```

### Tunbridge Wells

```{r tunbridge_wells_rtt_waiting_time}
tar_read(plot_rtt_waiting_time_RWF) |> 
  ggplotly()
```

## Single Bed Rooms

These are the charts for the percentage of total beds being single room
beds by year. Please note that these are at provider level due to having
to use KH03 as denominator for total bed numbers in some periods (not
reported in ERIC).

### Royal Liverpool

```{r royal_liverpool_sbr_percent}
tar_read(plot_sbr_percent_REM) |> 
  ggplotly()
```

### Clatterbridge

```{r clatterbridge_sbr_percent}
tar_read(plot_sbr_percent_REN) |> 
  ggplotly()
```

### Royal Papworth

```{r royal_papworth_sbr_percent}
tar_read(plot_sbr_percent_RGM) |> 
  ggplotly()
```

### Peterborough

```{r peterborough_sbr_percent}
tar_read(plot_sbr_percent_RGN) |> 
  ggplotly()
```

### Chase Farm

```{r chase_farm_sbr_percent}
tar_read(plot_sbr_percent_RAL) |> 
  ggplotly()
```

### Southmead

```{r southmead_sbr_percent}
tar_read(plot_sbr_percent_RVJ) |> 
  ggplotly()
```

### Tunbridge Wells

```{r tunbridge_wells_sbr_percent}
tar_read(plot_sbr_percent_RWF) |> 
  ggplotly()
```
:::

## Overall Notes

-   COVID-19 has affected all measures
-   We do not have enough/any data pre SBR for some sites
-   Clatterbridge not in eric data before 2021
-   For turnover, should we look at joiners as well as leavers?
-   Friends and family and falls and fractures have NaN, probably
    because of zero denominators
-   Missing Readmissions
-   SBR available at provider only due to KH03 not being at site level
    for the denominator
